### 2014-03-05 paper/tex/Paper.tex
tex stuff

% LaTeX template for MICS papers
% To Run:  pdflatex Sample.tex

\documentclass[12pt]{article}

\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\setlength{\parindent}{0in}

\usepackage{graphicx} %For jpg figure inclusion
\usepackage{times} %For typeface

\begin{document}
\pagestyle{plain}

\title{Sample MICS Paper Title}

\author{
Mary Smith\\
Name of Department\\
Name of Institution\\
City, State Zip\\
Contact email
\and
Joe Jones\\
Name of Department\\
Name of Institution\\
City, State Zip\\
Contact email
}
\date{}

\maketitle
\thispagestyle{empty}

\section*{\centering Abstract}

This is the abstract of the paper.  Note that the title and the abstract are the only things on the title page.  This example shows two authors at different institutions.  If information is the same for multiple authors, the authors can be listed as:

\begin{center}
{\large
Mary Smith and Joe Jones\\
Name of Department\\
Name of Institution\\
City, State Zip\\
Contact email
}
\end{center}

\newpage
\setcounter{page}{1}

\section{Level 1 Header}

This is the first section of the paper.  It starts on a new page.  Note how the left/right justification appears: text is justified on the left as well as on the right.  This section cites a paper by Author A.  It then cites a paper by Author B \cite{Pigeonhole}.  The citations are clearly described in the reference section.  Note that citation format can be determined by the author.  This is only one example.

\subsection{Level 2 Header}

This is a subsection of Section 1.   The figure in Figure~\ref{stars} is of four stars.\\

This is the second paragraph of the subsection.  Note that there is a blank line between the paragraphs and
no indentation at the beginning of the second paragraph.

% the following includes an image
% \begin{figure}[h]
% \centerline{
% \includegraphics[height=1.5in]{FigureName.jpg}			
% }
% \caption{Figure Caption.}
% \label{stars}
% \end{figure}

This paragraph starts after the figure.

\subsubsection{Level 3 Header}

This is a sub-subsection of Section 1.  Table~\ref{table1} contains data.

\begin{table}[hbt]
\begin{center}
\begin{tabular}{|c|c|} \hline
Field 1 & Field 2\\ \hline
data 1a   & data 2a\\ \hline
data 1b &  data 2b \\ \hline
\end{tabular}
\end{center}
\caption{Table Caption.}
\label{table1} 
\end{table}

This paragraph starts after the table.

\bibliographystyle{amc}
\bibliography{Paper}

\end{document}

### 2014-03-06 search_project/test_code.py
Added 20 data point test

@@ -551,6 +551,37 @@ class TestSequenceFunctions(unittest.TestCase):
         
         self.assertTrue(output == expected_output)
 
+    def test_data20_txt(self):
+        expected_output = \
+"""[54.796, 41.361, 51.848, 19.414]
+[55.396, 30.413, 54.749, 41.328]
+[54.501, 43.445, 55.437, 30.396]
+[60.419, 71.281, 54.235, 43.447]
+[60.125, 29.214, 60.125, 71.214]
+[60.111, 29.007, 60.111, 29.007]
+[58.758, 29.074, 60.087, 28.961]
+[66.77, 38.056, 58.701, 29.07]
+[55.393, 17.975, 66.743, 38.1]
+[59.244, 29.006, 55.335, 17.953]
+[58.303, 36.926, -1.0, 29.058]
+[59.743, 32.044, 58.227, 36.987]
+[59.526, 29.241, 59.526, 31.965]
+[55.105, 19.238, 59.403, 29.239]
+[61.947, 40.83, 55.079, 19.304]
+[61.69, 63.222, 61.69, 41.111]
+[57.045, 41.72, -1.0, -1.0]
+[58.428, 39.852, 57.023, 41.822]
+[52.631, 39.919, 58.441, 39.915]
+[58.427, 32.55, 52.597, 39.994]
+"""
+        p = subprocess.Popen(["python", "search_project.py", "./Data/data20.txt"], stdout=subprocess.PIPE)
+        out = p.communicate()
+
+        outputList = out[0].split("\n")
+        output = "\n".join(outputList[3 : len(outputList) - 3])
+
+        self.assertTrue(output == expected_output)
+
 #     def test_largedata_txt(self):
 #         expected_output = \
 # """[54.796, 41.361, 51.848, 19.414]

### 2014-03-06 search_project/Tile.py
testing new error

@@ -11,8 +11,8 @@ class Tile(object):
         self.c = float(c)
         self.d = float(d)
         self.place_holder = place_holder
-        self.char_weight = .4
-        self.order_weight = .4
+        self.char_weight = .1
+        self.order_weight = 1
         if(self.b == -1.0 and 0<self.a and self.a<50.0):
             self.amino_type = 1 #gly
         elif(0.0<self.b and self.b<20.0 and self.a > 52 and self.a < 56):
@@ -49,7 +49,7 @@ class Tile(object):
         
     def get_error(self, char):
         if(self.place_holder == True or self.a == -1 and self.b == -1):
-            return self.char_weight * .5 
+            return 0
         elif(self.a == -1):
             return (math.fabs(char[0]-self.a)*self.char_weight*2)
         elif(self.b == -1):
@@ -66,7 +66,7 @@ class Tile(object):
              t.get_c() == -1 and t.get_d() ==-1 or \
               t.get_d() == -1 and self.a == -1 or \
                t.get_c() == -1 and self.b == -1):
-            return self.order_weight * .3 
+            return self.order_weight  * 1.9
         elif(self.a == -1 or t.get_c() == -1):
             return math.fabs((self.b-t.get_d()))*self.order_weight
         elif(self.b == -1 or t.get_d() == -1):

### 2014-03-06 search_project/search_strategies.py

@@ -111,7 +111,7 @@ def uniform_cost(file_name):
 	root = Node(tile_set, [], 0.0, characteristic,0,0)
 
 	frontier = [root] #list of nodes
-
+	node_count = 1
 	best_solution = None
 	best_cost = float("inf") #set to infinity
 	keep_running = True
@@ -133,7 +133,6 @@ def uniform_cost(file_name):
 	# 	print str(sum) + "\t" + str(i)
 	# for i in tile_set:
 	# 	print i.get_amino_type()
-	
 	#runs while frontier is not empty
 	while keep_running:
 	        current_cost = float("inf")
@@ -154,9 +153,11 @@ def uniform_cost(file_name):
 		#creates child_nodes to search 
 		#adds child_nodes to frontier
 		child_nodes = current_node.expand()
+		node_count = node_count + len(child_nodes)
 		for c_n in child_nodes:
 			frontier.insert(0, c_n)
 		
+		print len(frontier)
 		keep_running = False
 		for i in range(len(frontier)):
 		    if (keep_running==False and frontier[i].get_cost() < best_cost):
@@ -170,3 +171,4 @@ def uniform_cost(file_name):
 	print best_solution
 	print "Char cost:  " + str(best_solution.get_char_cost())
 	print "Order Cost:  " + str(best_solution.get_order_cost())
+	print "Nodes: " + str(node_count)

### 2014-03-06 search_project/search_strategies.py
Added data30 to unit test, tested, and commented it out

@@ -157,7 +157,7 @@ def uniform_cost(file_name):
 		for c_n in child_nodes:
 			frontier.insert(0, c_n)
 		
-		print len(frontier)
+		#print len(frontier)
 		keep_running = False
 		for i in range(len(frontier)):
 		    if (keep_running==False and frontier[i].get_cost() < best_cost):
@@ -171,4 +171,4 @@ def uniform_cost(file_name):
 	print best_solution
 	print "Char cost:  " + str(best_solution.get_char_cost())
 	print "Order Cost:  " + str(best_solution.get_order_cost())
-	print "Nodes: " + str(node_count)
+	#print "Nodes: " + str(node_count)

### 2014-03-06 search_project/test_code.py

@@ -530,6 +530,48 @@ class TestSequenceFunctions(unittest.TestCase):
         
         self.assertTrue(output == expected_output)
 
+#     def test_data30_txt(self):
+#         expected_output = \
+# """[54.796, 41.361, 51.848, 19.414]
+# [55.396, 30.413, 54.749, 41.328]
+# [54.501, 43.445, 55.437, 30.396]
+# [60.419, 71.281, 54.235, 43.447]
+# [60.125, 29.214, 60.125, 71.214]
+# [60.111, 29.007, 60.111, 29.007]
+# [58.758, 29.074, 60.087, 28.961]
+# [66.77, 38.056, 58.701, 29.07]
+# [55.393, 17.975, 66.743, 38.1]
+# [59.244, 29.006, 55.335, 17.953]
+# [58.303, 36.926, -1.0, 29.058]
+# [59.743, 32.044, 58.227, 36.987]
+# [59.526, 29.241, 59.526, 31.965]
+# [55.105, 19.238, 59.403, 29.239]
+# [61.947, 40.83, 55.079, 19.304]
+# [61.69, 63.222, 61.69, 41.111]
+# [57.045, 41.72, -1.0, -1.0]
+# [58.428, 39.852, 57.023, 41.822]
+# [52.631, 39.919, 58.441, 39.915]
+# [58.427, 32.55, 52.597, 39.994]
+# [54.411, 41.198, 58.337, 32.591]
+# [46.83, -1.0, 54.39, 41.141]
+# [53.766, 41.319, 46.814, -1.0]
+# [45.945, -1.0, 53.714, 41.339]
+# [59.853, 73.245, 46.122, -1.0]
+# [59.346, 41.36, -1.0, -1.0]
+# [60.573, 70.772, 59.309, 41.478]
+# [65.249, 67.535, 60.553, 70.685]
+# [58.394, 32.309, 65.271, 67.334]
+# [56.12, 29.678, 58.467, 32.38]
+# [58.654, 41.811, 56.159, 29.866]
+# """
+#         p = subprocess.Popen(["python", "search_project.py", "./Data/data30.txt"], stdout=subprocess.PIPE)
+#         out = p.communicate()
+
+#         outputList = out[0].split("\n")
+#         output = "\n".join(outputList[3 : len(outputList) - 3])
+
+#         self.assertTrue(output == expected_output)
+
     def test_test18_txt(self):
         expected_output = \
 """[55.299, 42.945, 54.696, 39.212]

### 2014-03-09 search_project/Node.py
comment correction

@@ -50,6 +50,4 @@ class Node(object):
 				c = temp_order_cost + temp_char_cost
 
 				new_nodes.append(Node(temp_ut, temp_pt, self.cost + c, self.characteristic,self.char_cost+temp_char_cost, self.order_cost+temp_order_cost))
-			
-		
 		return new_nodes

### 2014-03-09 search_project/Tile.py

@@ -39,11 +39,11 @@ class Tile(object):
     def get_place_holder(self):
         return self.place_holder
 
-    #returns a
+    #returns c
     def get_c(self):
         return self.c
 
-    #returns b
+    #returns d
     def get_d(self):
         return self.d
         

### 2014-03-09 search_project/search_strategies.py

@@ -156,8 +156,6 @@ def uniform_cost(file_name):
 		node_count = node_count + len(child_nodes)
 		for c_n in child_nodes:
 			frontier.insert(0, c_n)
-		
-		#print len(frontier)
 		keep_running = False
 		for i in xrange(len(frontier)):
 		    if (keep_running==False and frontier[i].get_cost() < best_cost):

### 2014-03-11 search_project/dataformatscript.pl
Added script to make formatting data for unit test module easier

@@ -1,0 +1,37 @@
+#!/usr/bin/perl
+
+# DataFormatScript.pl
+# Author: David Mascharka
+# Takes input formatted for reading as input into the assignment program and formats it for use in
+# unit testing. 
+
+use strict;
+
+open (FILE, '>', 'out.txt') or die;
+my $firstline = 1;
+while (<>)
+{
+    if ($firstline) {
+        $firstline = 0;
+        next;
+    }
+
+    chomp $_;
+    $_ = "[$_";
+    while ($_ =~ /(\t+.+$)|([ ]{2,}.+$)/) {
+        s/(\t+)|([ ]{2})/, /g;
+    }
+    
+    while ($_ =~ /0[^\d.]/) {
+        s/0[^\d.]/ /g;
+    }
+
+    while ($_ =~ /na/) {
+        s/na/-1.0/g;
+    }
+    
+    $_ =  "$_]\n";
+    print FILE $_;
+}
+
+close FILE;

### 2014-03-11 search_project/dataformatscript.pl
Fix script

@@ -18,17 +18,20 @@ while (<>)
 
     chomp $_;
     $_ = "[$_";
-    while ($_ =~ /(\t+.+$)|([ ]{2,}.+$)/) {
-        s/(\t+)|([ ]{2})/, /g;
+    while ($_ =~ /\t+| {2,}/) {
+        s/\t+|( {2,})/, /g;
     }
     
-    while ($_ =~ /0[^\d.]/) {
+    while ($_ =~ /0[^\d.]|0$/) {
+        s/0$//g;
         s/0[^\d.]/ /g;
     }
 
     while ($_ =~ /na/) {
         s/na/-1.0/g;
     }
+
+    s/ /, /g;
     
     $_ =  "$_]\n";
     print FILE $_;

### 2014-03-11 search_project/dataformatscript.pl
Fix script

@@ -19,7 +19,7 @@ while (<>)
     chomp $_;
     $_ = "[$_";
     while ($_ =~ /\t+| {2,}/) {
-        s/\t+|( {2,})/, /g;
+        s/\t+|( {2,})/ /g;
     }
     
     while ($_ =~ /0[^\d.]|0$/) {

### 2014-03-12 paper/tex/Paper.tex
Paper update
algorithm section of paper

@@
 \setlength{\textheight}{9in}
-\setlength{\parindent}{0in}
+\usepackage[parfill]{parskip}
 
@@
 
-\section{Level 1 Header}
+\section{Method} % (fold)
+\label{sec:method}
 
-This is the first section of the paper.
-It starts on a new page.
-Note how the left/right justification appears: text is justified on the left as well as on the right.
-This section cites a paper by Author A.
-It then cites a paper by Author B \cite{Pigeonhole}.
-The citations are clearly described in the reference section.
-Note that citation format can be determined by the author.
-This is only one example.
+\subsection{Algorithm} % (fold)
+\label{sub:algorithm}
+Our algorithm begins by reading in and expected amino acid order and the NMR carbon shift data from a data file.
+It then changes the amino acids to there expected $C_\alpha$ and $C_{\beta}$ values and stores them in an list that represents the protein chain.
+Next, the carbon shift values for a single amino acid is placed in a tile.
+A tile contains the $C_\alpha$ and $C_{\beta}$ values for the amino acid residue $i$ and residue $i-1$.
+Next, missing data is accounted for.
+If there are less tiles than the number of amino acids in the protein chain, place holder tiles are generated to make up the difference.
+Before the search for the best solution begins, the tiles are grouped by the type of amino acids they could represent to accelerate the assignment process.
+Tiles that do not match a group are grouped with the place holder tiles
 
-\subsection{Level 2 Header}
+To start the search, tiles in the place holder group and tiles in the same amino acid group as the first amino acid in the protein chain are placed in the first position in a node.
+The tile is then compared to the first amino acid in the protein chain, and a cost is generated.
 
-This is a subsection of Section 1.   The figure in Figure~\ref{stars} is of four stars.\\
+%continue assignment
 
-This is the second paragraph of the subsection.  Note that there is a blank line between the paragraphs and
-no indentation at the beginning of the second paragraph.
+%goal state
 
-% the following includes an image
-% \begin{figure}[h]
-% \centerline{
-% \includegraphics[height=1.5in]{FigureName.jpg}			
-% }
-% \caption{Figure Caption.}
-% \label{stars}
-% \end{figure}
+%solution found
 
-This paragraph starts after the figure.
-
-\subsubsection{Level 3 Header}
-
-This is a sub-subsection of Section 1.  Table~\ref{table1} contains data.
-
-\begin{table}[hbt]
-\begin{center}
-\begin{tabular}{|c|c|} \hline
-Field 1 & Field 2\\ \hline
-data 1a   & data 2a\\ \hline
-data 1b &  data 2b \\ \hline
-\end{tabular}
-\end{center}
-\caption{Table Caption.}
-\label{table1} 
-\end{table}
-
-This paragraph starts after the table.
-
+% subsection algorithm (end)
+% section method (end)
 \bibliographystyle{amc}

### 2014-03-12 search_project/dataformatscript.pl
Improve script

@@ -17,24 +17,30 @@ while (<>)
     }
 
     chomp $_;
+
+    s/^\s+|\s+$//g;
+
     $_ = "[$_";
-    while ($_ =~ /\t+| {2,}/) {
-        s/\t+|( {2,})/ /g;
-    }
+
+    #while ($_ =~ /\s+/) {
+        s/\s+/ /g;
+    #}
     
     while ($_ =~ /0[^\d.]|0$/) {
         s/0$//g;
         s/0[^\d.]/ /g;
     }
 
-    while ($_ =~ /na/) {
+    s/\.[^\d]/\.0 /g;
+
+    #while ($_ =~ /na/) {
         s/na/-1.0/g;
-    }
+    #}
 
     s/ /, /g;
     
     $_ =  "$_]\n";
-    print FILE $_;
+    print $_;
 }
 
 close FILE;

### 2014-03-12 paper/tex/Paper.tex

@@
 \label{sub:algorithm}
+%read file
 Our algorithm begins by reading in and expected amino acid order and the NMR carbon shift data from a data file.
@@
 
+%start search
 To start the search, tiles in the place holder group and tiles in the same amino acid group as the first amino acid in the protein chain are placed in the first position in a node.
 The tile is then compared to the first amino acid in the protein chain, and a cost is generated.
+All of the generated nodes are place in a frontier array.
 
 %continue assignment
+The node in the frontier with the lowest cost is removed from the frontier and used to generate child nodes.
+To generate a child node, a tile is added to the end of the node.
+A child node is generated for all unplaced tiles that are either in the place holder group or in the group matching the corresponding amino acid in the protein chain.
+A cost of placing the tile is then generated.
+The cost is a sum of the cost of placing the previous tiles in the node, how well the tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
+The child nodes are then added to the frontier, and the process of generating child nodes is repeated.
 
 %goal state
+Once a node has every tile placed, it is said to be in the goal state.
+The first node that reaches goal state is stored as the current best solution.
+Every node that hits goal state is compared to the current best solution.
+The node with the lower cost is saved as the current best solution.
 
 %solution found
+A solution has been found once the current best solution's cost is lower than the cost of any nodes in the frontier.
+The search is then ended.
+The algorithm then outputs the cost of the best solution followed by the assigned carbon shift values.
 

### 2014-03-12 search_project/dataformatscript.pl
Improve script

@@ -22,10 +22,8 @@ while (<>)
 
     $_ = "[$_";
 
-    #while ($_ =~ /\s+/) {
-        s/\s+/ /g;
-    #}
-    
+    s/\s+/ /g;
+        
     while ($_ =~ /0[^\d.]|0$/) {
         s/0$//g;
         s/0[^\d.]/ /g;
@@ -33,10 +31,8 @@ while (<>)
 
     s/\.[^\d]/\.0 /g;
 
-    #while ($_ =~ /na/) {
-        s/na/-1.0/g;
-    #}
-
+    s/na/-1.0/g;
+    
     s/ /, /g;
     
     $_ =  "$_]\n";

### 2014-03-13 search_project/dataformatscript.pl
Improve script

@@ -19,10 +19,6 @@ while (<>)
     chomp $_;
 
     s/^\s+|\s+$//g;
-
-    $_ = "[$_";
-
-    s/\s+/ /g;
         
     while ($_ =~ /0[^\d.]|0$/) {
         s/0$//g;
@@ -33,9 +29,9 @@ while (<>)
 
     s/na/-1.0/g;
     
-    s/ /, /g;
+    s/\s+/, /g;
     
-    $_ =  "$_]\n";
+    $_ =  "[$_]\n";
     print $_;
 }
 

### 2014-03-13 search_project/test_code.py
Rewrote test code to use the perl script. Added subroutines to boilerplate code.

@@ -2,731 +2,107 @@ import unittest
 import subprocess
 import re
 
+def getExpectedOutput(filename):
+    p = subprocess.Popen(["perl", "dataformatscript.pl", "./Data/"+filename], stdout=subprocess.PIPE)
+    out = p.communicate()
+    expected_output = "\n".join(out[0].split("\n"))
+    return expected_output
+
+def getOutput(filename):
+    p = subprocess.Popen(["python", "search_project.py", "./Data/"+filename], stdout=subprocess.PIPE)
+    out = p.communicate()
+    outputList = out[0].split("\n")
+    output = "\n".join(outputList[3 : len(outputList) - 4])
+    return output
+
 class TestSequenceFunctions(unittest.TestCase):
 
     def test_testdata_txt(self):
-        expected_output = \
-"""[54.796, 41.361, 51.848, 19.414]
-[55.396, 30.413, 54.749, 41.328]
-[54.501, 43.445, 55.437, 30.396]
-[60.419, 71.281, 54.235, 43.447]
-[60.125, 29.214, 60.125, 71.214]
-[60.111, 29.007, 60.111, 29.007]
-[58.758, 29.074, 60.087, 28.961]
-[66.77, 38.056, 58.701, 29.07]
-[55.393, 17.975, 66.743, 38.1]
-[59.244, 29.006, 55.335, 17.953]
-"""
-        p = subprocess.Popen(["python", "search_project.py", "./Data/testdata.txt"], stdout=subprocess.PIPE)
-        out = p.communicate()
-
-        outputList = out[0].split("\n")
-        output = "\n".join(outputList[3 : len(outputList) - 4])
-        
-        self.assertTrue(output == expected_output)
+        self.assertTrue(getOutput("testdata.txt") == getExpectedOutput("testdata.txt"))
 
     def test_mdata_txt(self):
-        expected_output = \
-"""[54.796, 41.361, 51.848, 19.414]
-[55.396, 30.413, 54.749, 41.328]
-[54.501, 43.445, 55.437, 30.396]
-[60.419, 71.281, 54.235, 43.447]
-[60.125, 29.214, 60.125, 71.214]
-[60.111, 29.007, 60.111, 29.007]
-[58.758, 29.074, 60.087, 28.961]
-[66.77, 38.056, 58.701, 29.07]
-[55.393, 17.975, 66.743, 38.1]
[…]

### 2014-03-13 search_project/dataformatscript.pl
Remove out.txt creation

@@ -7,7 +7,6 @@
 
 use strict;
 
-open (FILE, '>', 'out.txt') or die;
 my $firstline = 1;
 while (<>)
 {

### 2014-03-13 search_project/old_test_code.py

@@ -1,0 +1,732 @@
+import unittest
+import subprocess
+import re
+
+class TestSequenceFunctions(unittest.TestCase):
+
+    def test_testdata_txt(self):
+        expected_output = \
+"""[54.796, 41.361, 51.848, 19.414]
+[55.396, 30.413, 54.749, 41.328]
+[54.501, 43.445, 55.437, 30.396]
+[60.419, 71.281, 54.235, 43.447]
+[60.125, 29.214, 60.125, 71.214]
+[60.111, 29.007, 60.111, 29.007]
+[58.758, 29.074, 60.087, 28.961]
+[66.77, 38.056, 58.701, 29.07]
+[55.393, 17.975, 66.743, 38.1]
+[59.244, 29.006, 55.335, 17.953]
+"""     
+        p = subprocess.Popen(["python", "search_project.py", "./Data/testdata.txt"], stdout=subprocess.PIPE)
+        out = p.communicate()
+
+        outputList = out[0].split("\n")
+        output = "\n".join(outputList[3 : len(outputList) - 4])
+        
+        self.assertTrue(output == expected_output)
+
+    def test_mdata_txt(self):
+        expected_output = \
+"""[54.796, 41.361, 51.848, 19.414]
+[55.396, 30.413, 54.749, 41.328]
+[54.501, 43.445, 55.437, 30.396]
+[60.419, 71.281, 54.235, 43.447]
+[60.125, 29.214, 60.125, 71.214]
+[60.111, 29.007, 60.111, 29.007]
+[58.758, 29.074, 60.087, 28.961]
+[66.77, 38.056, 58.701, 29.07]
+[55.393, 17.975, 66.743, 38.1]
+[59.244, 29.006, 55.335, 17.953]
+[58.303, 36.926, -1.0, 29.058]
+"""
+        p = subprocess.Popen(["python", "search_project.py", "./Data/mdata.txt"], stdout=subprocess.PIPE)
+        out = p.communicate()
+
+        outputList = out[0].split("\n")
+        output = "\n".join(outputList[3 : len(outputList) - 4])
+
+        self.assertTrue(output == expected_output)
+
+    def test_tiny_test_txt(self):
+        expected_output = \
+"""[54.796, 41.361, 51.848, 19.414]
+[55.396, 30.413, 54.749, 41.328]
+[54.501, 43.445, 55.437, 30.396]
+[-1.0, -1.0, -1.0, -1.0]
[…]

### 2014-03-13 paper/tex/Paper.tex
typo

@@
 A cost of placing the tile is then generated.
-The cost is a sum of the cost of placing the previous tiles in the node, how well the tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
+The cost is a sum of the cost of placing the previous tiles in the node, how well the current tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
 The child nodes are then added to the frontier, and the process of generating child nodes is repeated.

### 2014-03-26 paper/tex/Paper.tex
citation
update to paper

@@
 \author{
-Mary Smith\\
-Name of Department\\
-Name of Institution\\
-City, State Zip\\
-Contact email
-\and
-Joe Jones\\
+Mary Smith and Joe Jones\\
 Name of Department\\
@@
 
-This is the abstract of the paper.
-Note that the title and the abstract are the only things on the title page.
-This example shows two authors at different institutions.
-If information is the same for multiple authors, the authors can be listed as:
+Nuclear magnetic resonance (NMR) spectroscopy is a powerful method for studying the three-dimensional structure of molecules such as proteins.
+The post-genomic era has created the need to gather functional and structural information of unknown proteins encoded by newly discovered genes.
+Unfortunately, current manual techniques for analyzing NMR datasets can take days to months to assign, and are prone to error.
+The current goal of this research is to develop an algorithm to automate the process of assigning nontrivial NMR datasets, in an attempt to minimize human error and accelerate a time consuming task.
 
-\begin{center}
-{\large
-Mary Smith and Joe Jones\\
-Name of Department\\
-Name of Institution\\
-City, State Zip\\
-Contact email
-}
-\end{center}
+NMR images yield structural information that needs to be analyzed rapidly and accurately.
+Accurate assignment of nontrivial NMR datasets will provide the necessary framework for continued advancement in the fields of structural biology and proteomics.
+
+The algorithm utilizes A* search to sequence amino acids produced from NMR datasets of proteins.
+The program is given a set of nodes, each corresponding to a single amino acid in the protein chain, from an input file.
+Each node is placed in the initial node position of the protein chain.
+The node that most correctly fits the reference protein chain is used to generate child nodes.
+Unplaced nodes are sequentially added to the end of a list to create child node lists.
+The node list with the smallest error is then expanded further.
+The error is a running total of how well the nodes fit the reference protein chain, coupled with the accuracy of the match of the placed child.
+This process of assigning the child nodes and calculating costs repeats until every node is placed and the best node list contains the lowest cost of all generated lists.
+
+Assignments of test sets have shown this method can be used to assign NMR datasets, but there remains need for improvement.
+Research is ongoing as we continue to refine our algorithm.
+Future goals include adjusting for potentially missing data, sorting nodes into amino acid groups, and testing with larger datasets.
+Upon completion, this algorithm will allow for great advancements in the areas of structural biology and proteomics.
 
@@
 \setcounter{page}{1}
+
+example cite\cite{Alipanahi09ipass:error}
 

### 2014-03-26 paper/tex/Paper.tex
paper update

@@
 
-\title{Sample MICS Paper Title}
+\title{Accelerating Biomolecular Nuclear Magnetic Resonance Assignment with A*}
 
 \author{
-Mary Smith and Joe Jones\\
-Name of Department\\
-Name of Institution\\
-City, State Zip\\
-Contact email
+Joel Venzke, Paxten Johnson, Rachel Davis, John Emmons, Katherine Roth,\\ David Mascharka, Leah Robison, Timothy Urness and Adina Kilpatrick\\
+Department of Mathematics and Computer Science\\
+Drake University\\
+Des Moines, IA\\
+email %TODO
 }
@@
 
-\newpage
 \setcounter{page}{1}
 
-example cite\cite{Alipanahi09ipass:error}
+\section{Introduction}
+Several types of NMR variables can be used in the analysis of protein structures.
+In particular, essential information is provided by the chemical shifts of NMR-active nuclei present in proteins, including hydrogen and isotopes of carbon and nitrogen.
+The chemical shift is a quantifier for the deviation in the resonant frequency of a nucleus from its value in a structure-free environment, and therefore provides information on the local conformation.
+Determining the chemical shifts of all or most of the nuclei in a biomolecule is the first step in determining its structure.
+An important set of chemical shifts in a protein are those corresponding to the nuclei in the backbone of the protein polypeptide chain, including the nitrogen, attached hydrogen, and the alpha and beta carbon atoms ($C_\alpha$ and $C_{\beta}$) of each residue.
+These chemical shifts are measured using various three-dimensional NMR experiments, and then matched to the individual residues in the protein in a process called sequential assignment.
 
+A prerequisite of the assignment process is data collection using experiments that can provide connectivities between neighboring residues.
+For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_\alpha$ and $C_{\beta}$ nuclei of one residue (residue i), as well as the $C_\alpha$ and $C_{\beta}$ chemical shifts of the immediately preceding residue (residue $i – 1$).
+In this experiment, the values corresponding to residue i can usually be distinguished from the ($i -1$) values by their higher intensity.
+However, ambiguities can arise if the intensities are comparable or if the chemical shift values are overlapping.
+These ambiguities can be resolved by using additional experiments, such as CBCA(CO) NH, which yields the chemical shifts of the preceding residue only.
+Using all inter-residue connectivities, a chain of correlations through the protein backbone chemical shifts can be established.
+This pattern of sequentially linked chemical shift values reflects the sequential linear arrangement of the individual residues in the protein sequence.
+The pattern is then matched with the protein sequence, by using the fact that certain residues have characteristic $C_\alpha$ and $C_{\beta}$ chemical shift ranges which uniquely identify them.
+Thus, each measured chemical shift is assigned to a protein residue, and this information can then be used to infer structural information about the biomolecule.
 \section{Method} % (fold)

### 2014-03-26 paper/tex/Paper.tex
image for paper

@@
 \section{Introduction}
+\label{sub:introduction}
 Several types of NMR variables can be used in the analysis of protein structures.
@@
 \label{sub:algorithm}
-%read file
-Our algorithm begins by reading in and expected amino acid order and the NMR carbon shift data from a data file.
-It then changes the amino acids to there expected $C_\alpha$ and $C_{\beta}$ values and stores them in an list that represents the protein chain.
+Our algorithm begins by reading in an expected amino acid order and the NMR carbon shift data from a data file.
+It then changes the amino acids to their expected $C_\alpha$ and $C_{\beta}$ values and stores them in an list that represents the protein chain.
 Next, the carbon shift values for a single amino acid is placed in a tile.
@@
 Next, missing data is accounted for.
-If there are less tiles than the number of amino acids in the protein chain, place holder tiles are generated to make up the difference.
+If there are less tiles than the number of amino acids in the protein chain, placeholder tiles are generated to make up the difference.
 Before the search for the best solution begins, the tiles are grouped by the type of amino acids they could represent to accelerate the assignment process.
-Tiles that do not match a group are grouped with the place holder tiles
+Tiles that do not match a group are grouped with the placeholder tiles
 
 %start search
-To start the search, tiles in the place holder group and tiles in the same amino acid group as the first amino acid in the protein chain are placed in the first position in a node.
+To start the search, tiles in the placeholder group and tiles in the same amino acid group as the first amino acid in the protein chain are placed in the first position in a node.
 The tile is then compared to the first amino acid in the protein chain, and a cost is generated.
@@
 To generate a child node, a tile is added to the end of the node.
-A child node is generated for all unplaced tiles that are either in the place holder group or in the group matching the corresponding amino acid in the protein chain.
+A child node is generated for all unplaced tiles that are either in the placeholder group or in the group matching the corresponding amino acid in the protein chain.
 A cost of placing the tile is then generated.
@@
 Every node that hits goal state is compared to the current best solution.
-The node with the lower cost is saved as the current best solution.
+The node with the lower cost is then saved as the current best solution.
 

### 2014-03-26 paper/tex/Paper.tex
update paper
bibtex stuff
bibtex

@@
 The current goal of this research is to develop an algorithm to automate the process of assigning nontrivial NMR datasets, in an attempt to minimize human error and accelerate a time consuming task.
-
+%
 NMR images yield structural information that needs to be analyzed rapidly and accurately.
 Accurate assignment of nontrivial NMR datasets will provide the necessary framework for continued advancement in the fields of structural biology and proteomics.
-
+%
 The algorithm utilizes A* search to sequence amino acids produced from NMR datasets of proteins.
@@
 This process of assigning the child nodes and calculating costs repeats until every node is placed and the best node list contains the lowest cost of all generated lists.
-
+%
 Assignments of test sets have shown this method can be used to assign NMR datasets, but there remains need for improvement.
@@
 Upon completion, this algorithm will allow for great advancements in the areas of structural biology and proteomics.
-
+\newpage
 \setcounter{page}{1}
@@
 \label{sub:introduction}
+
+\subsection{NMR} % (fold)
+\label{sub:nmr}
 Several types of NMR variables can be used in the analysis of protein structures.
@@
 Thus, each measured chemical shift is assigned to a protein residue, and this information can then be used to infer structural information about the biomolecule.
+
 \section{Method} % (fold)
@@
 The algorithm then outputs the cost of the best solution followed by the assigned carbon shift values.
+\cite{guntert_automated_2009} \cite{babak_alipanahi_error_2011} \cite{brief_introduction_Poulsen}
 

### 2014-03-26 paper/tex/Paper.tex
alskdjf

@@
 It then changes the amino acids to their expected $C_\alpha$ and $C_{\beta}$ values and stores them in an list that represents the protein chain.
-Next, the carbon shift values for a single amino acid is placed in a tile.
+Next, the carbon shift values for a single amino acid are placed in a tile.
 A tile contains the $C_\alpha$ and $C_{\beta}$ values for the amino acid residue $i$ and residue $i-1$.
@@
 Before the search for the best solution begins, the tiles are grouped by the type of amino acids they could represent to accelerate the assignment process.
-Tiles that do not match a group are grouped with the placeholder tiles
+Tiles that do not match a group are grouped with the placeholder tiles.
 
 %start search
-To start the search, tiles in the placeholder group and tiles in the same amino acid group as the first amino acid in the protein chain are placed in the first position in a node.
-The tile is then compared to the first amino acid in the protein chain, and a cost is generated.
+To start the search, tiles in the placeholder group and tiles of the same amino acid group as the first amino acid in the protein chain are placed in the first position in a node.
+The tile is then compared to the first amino acid in the protein chain and an cost is generated.
+The cost is the sum of the cost of placing the previous tiles in the node, how well the current tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
 All of the generated nodes are place in a frontier array.
@@
 A cost of placing the tile is then generated.
-The cost is a sum of the cost of placing the previous tiles in the node, how well the current tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
 The child nodes are then added to the frontier, and the process of generating child nodes is repeated.
@@
 The first node that reaches goal state is stored as the current best solution.
-Every node that hits goal state is compared to the current best solution.
-The node with the lower cost is then saved as the current best solution.
+Every node that achieves goal state is compared to the current best solution.
+The node with the lowest cost is then saved as the current best solution.
 
@@
 The algorithm then outputs the cost of the best solution followed by the assigned carbon shift values.
-\cite{guntert_automated_2009} \cite{babak_alipanahi_error_2011} \cite{brief_introduction_Poulsen}
+\cite{guntert_automated_2009} \cite{Alipanahi09ipass:error} \cite{babak_alipanahi_error_2011}
 

### 2014-03-26 paper/tex/Paper.tex
edit

@@
 The tile is then compared to the first amino acid in the protein chain and an cost is generated.
-The cost is the sum of the cost of placing the previous tiles in the node, how well the current tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
+The cost is the sum of the cost of placing any previous tiles in the node, how well the current tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
 All of the generated nodes are place in a frontier array.
@@
 The algorithm then outputs the cost of the best solution followed by the assigned carbon shift values.
-\cite{guntert_automated_2009} \cite{Alipanahi09ipass:error} \cite{babak_alipanahi_error_2011}
+\cite{guntert_automated_2009} \cite{babak_alipanahi_error_2011} \cite{brief_introduction_Poulsen}
 

### 2014-03-26 paper/tex/Paper.tex
lkdsj

@@
 Des Moines, IA\\
-email %TODO
+email % TODO
 }

### 2014-03-26 paper/tex/Paper.tex
Added results section to paper

@@
 A prerequisite of the assignment process is data collection using experiments that can provide connectivities between neighboring residues.
-For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_\alpha$ and $C_{\beta}$ nuclei of one residue (residue i), as well as the $C_\alpha$ and $C_{\beta}$ chemical shifts of the immediately preceding residue (residue $i – 1$).
-In this experiment, the values corresponding to residue i can usually be distinguished from the ($i -1$) values by their higher intensity.
+For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_\alpha$ and $C_{\beta}$ nuclei of one residue (residue $i$), as well as the $C_\alpha$ and $C_{\beta}$ chemical shifts of the immediately preceding residue (residue $i – 1$).
+In this experiment, the values corresponding to residue $i$ can usually be distinguished from the ($i -1$) values by their higher intensity.
 However, ambiguities can arise if the intensities are comparable or if the chemical shift values are overlapping.
@@
 Our algorithm begins by reading in an expected amino acid order and the NMR carbon shift data from a data file.
-It then changes the amino acids to their expected $C_\alpha$ and $C_{\beta}$ values and stores them in an list that represents the protein chain.
+It then changes the amino acids to their expected $C_\alpha$ and $C_{\beta}$ values and stores them in a list that represents the protein chain.
 Next, the carbon shift values for a single amino acid are placed in a tile.
@@
 Next, missing data is accounted for.
-If there are less tiles than the number of amino acids in the protein chain, placeholder tiles are generated to make up the difference.
-Before the search for the best solution begins, the tiles are grouped by the type of amino acids they could represent to accelerate the assignment process.
+If there are fewer tiles than the number of amino acids in the protein chain, placeholder tiles are generated to make up the difference.
+Before the search for the best solution begins, the tiles are grouped by the types of amino acids they could represent to accelerate the assignment process.
 Tiles that do not match a group are grouped with the placeholder tiles.
@@
 To start the search, tiles in the placeholder group and tiles of the same amino acid group as the first amino acid in the protein chain are placed in the first position in a node.
-The tile is then compared to the first amino acid in the protein chain and an cost is generated.
+The tile is then compared to the first amino acid in the protein chain and a cost is generated.
 The cost is the sum of the cost of placing any previous tiles in the node, how well the current tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
-All of the generated nodes are place in a frontier array.
+All of the generated nodes are placed in a frontier array.
 
@@
 A child node is generated for all unplaced tiles that are either in the placeholder group or in the group matching the corresponding amino acid in the protein chain.
-A cost of placing the tile is then generated.
+The cost of placing the tile is then generated.
 The child nodes are then added to the frontier, and the process of generating child nodes is repeated.
@@
 
+\section{Conclusions}
+\label{sec:conclusions}
+
+\subsection{Results}
+\label{sub:results}
+Our algorithm has been tested with real NMR datasets of varying size.
+When compared to hand-ordered data, the algorithm produces the same, optimal ordering of amino acids.
+Initially, we focused our research on accurate assignment at the cost of speed.
+Thus, at the start of our research we could assign only smaller datasets up to ten to fifteen amino acids long.
+As we shifted our focus to optimizing the algorithm's speed while maintaining the accuracy we managed to achieve we improved runtime to correctly assign up to forty to fifty amino acids.
+In future research, we plan to test with larger datasets, maximizing speed and efficiency to the point that our algorithm can assign full protein sequences.
+We also plan to look into testing datasets with more than a few missing datapoints to verify that our algorithm correctly places amino acids when given less-perfect data.
+
 % subsection algorithm (end)

### 2014-03-26 paper/tex/Paper.tex
paper stuff

@@
 \usepackage{graphicx} %For jpg figure inclusion
+\usepackage{float}
 \usepackage{times} %For typeface
@@
 \label{sub:introduction}
+Knowledge of a protein’s structure allows for further understanding of the function of a protein and alterations to its function that can lead to disease.
+The post-genomic era has brought the need to gather functional and structural information of unknown proteins that are encoded by newly discovered genes.
+Through the implementation of Nuclear magnetic resonance (NMR) spectroscopy, the structure of molecules, such as proteins, can be studied.
+However, NMR spectroscopy generates large amounts of data that needs to be assigned.
+The assignment process can take months to complete and is prone to error.
+To allow for major advances in structural biology, a faster and more accurate method needs to be developed.
+Our research focuses on developing an algorithm to automate the assignment process, in an attempt to minimize human error and accelerate the time consuming task.
 
@@
 A prerequisite of the assignment process is data collection using experiments that can provide connectivities between neighboring residues.
-For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_\alpha$ and $C_{\beta}$ nuclei of one residue (residue $i$), as well as the $C_\alpha$ and $C_{\beta}$ chemical shifts of the immediately preceding residue (residue $i – 1$).
+For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_\alpha$ and $C_{\beta}$ nuclei of one residue (residue $i$), as well as the $C_\alpha$ and $C_{\beta}$ chemical shifts of the immediately preceding residue (residue $i -1$).
 In this experiment, the values corresponding to residue $i$ can usually be distinguished from the ($i -1$) values by their higher intensity.
@@
 Tiles that do not match a group are grouped with the placeholder tiles.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics{carbon}
+\end{center}
+\caption{aslkfjlkd}
+\label{fig:carbon}
+\end{figure}
 
@@
 The algorithm then outputs the cost of the best solution followed by the assigned carbon shift values.
-\cite{guntert_automated_2009} \cite{babak_alipanahi_error_2011} \cite{brief_introduction_Poulsen}
 
@@
 
+\subsection{Future Goals} % (fold)
+\label{sub:future_goals}
+We are currently looking into the possibility of parallelizing our algorithm.
+If possible, our algorithm will be able to handle full NMR datasets.
+We are also looking to use machine learning in order to optimize the cost calculation.
+% subsection future_goals (end)
+
 % subsection algorithm (end)

### 2014-03-26 paper/tex/Paper.tex
paper

@@
 If there are fewer tiles than the number of amino acids in the protein chain, placeholder tiles are generated to make up the difference.
-Before the search for the best solution begins, the tiles are grouped by the types of amino acids they could represent to accelerate the assignment process.
+Before the search for the best solution begins, the tiles are grouped by the types of amino acids they could represent.
+The groups were created using the expected $C_\alpha$ and $C_{\beta}$ values shown in Figure~\ref{fig:carbon}.
+Grouping is done in an attempted to accelerate the assignment process.
 Tiles that do not match a group are grouped with the placeholder tiles.
@@
 \end{center}
-\caption{aslkfjlkd}
+\caption{Expected Carbon Shift Values}
 \label{fig:carbon}

### 2014-03-27 paper/tex/Paper.tex
paper
Paper Revision

@@
 Knowledge of a protein’s structure allows for further understanding of the function of a protein and alterations to its function that can lead to disease.
-The post-genomic era has brought the need to gather functional and structural information of unknown proteins that are encoded by newly discovered genes.
 Through the implementation of Nuclear magnetic resonance (NMR) spectroscopy, the structure of molecules, such as proteins, can be studied.
-However, NMR spectroscopy generates large amounts of data that needs to be assigned.
-The assignment process can take months to complete and is prone to error.
+However, assigning NMR spectroscopy generates large amounts of data that needs to be assigned.
+This process can take months to complete and is prone to error.
 To allow for major advances in structural biology, a faster and more accurate method needs to be developed.
-Our research focuses on developing an algorithm to automate the assignment process, in an attempt to minimize human error and accelerate the time consuming task.
+Our research focuses on developing an algorithm to automate the assignment process.
+We hope our attempts can minimize the human error and decrease the time consumption associated with manual assignment , increasing the overall effectiveness of the operation.
 
-\subsection{NMR} % (fold)
+\subsection{Nuclear Magnetic Resonance Spectroscopy} % (fold)
 \label{sub:nmr}
@@
 
-\section{Method} % (fold)
+\section{Assignment Methods} % (fold)
 \label{sec:method}
 
-\subsection{Algorithm} % (fold)
+\subsection{Manual Assignment} % (fold)
+\label{sub:manual_assignment}
+% TODO
+add this part
+cite our sources
+
+% subsection manual_assignment (end)
+
+\subsection{Our Algorithm} % (fold)
 \label{sub:algorithm}
@@
 \end{center}
-\caption{Expected Carbon Shift Values}
+\caption{Expected Carbon Shift Values} % TODO citation
 \label{fig:carbon}
@@
 \label{sub:results}
-Our algorithm has been tested with real NMR datasets of varying size.
-When compared to hand-ordered data, the algorithm produces the same, optimal ordering of amino acids.
+Our algorithm has been tested with NMR datasets of varying size from experiments conducted by Dr.
+Kilpatrick.
+When compared to manually assigned data, the algorithm produces the same, optimal ordering of amino acids.
 Initially, we focused our research on accurate assignment at the cost of speed.
-Thus, at the start of our research we could assign only smaller datasets up to ten to fifteen amino acids long.
-As we shifted our focus to optimizing the algorithm's speed while maintaining the accuracy we managed to achieve we improved runtime to correctly assign up to forty to fifty amino acids.
-In future research, we plan to test with larger datasets, maximizing speed and efficiency to the point that our algorithm can assign full protein sequences.
-We also plan to look into testing datasets with more than a few missing datapoints to verify that our algorithm correctly places amino acids when given less-perfect data.
+Thus, at the start of our research our algorithm was only able to assign smaller datasets with a chain of ten to fifteen amino acids.
+Shifting our focus to optimizing the algorithm's speed while maintaining the accuracy we had managed to achieve, we were able to improve runtime.
+With the increased runtime, we were able to correctly assign forty to fifty amino acids.
+In future research, we plan to test with larger datasets, maximizing speed and efficiency to the point that our algorithm can assign full protein(amino acid?) sequences.
+We also plan to look into testing datasets with more than a few missing data points to verify that our algorithm correctly places amino acids when given less perfect data.
+- TIME FOR DATASETS?
 
@@
 \label{sub:future_goals}
-We are currently looking into the possibility of parallelizing our algorithm.
-If possible, our algorithm will be able to handle full NMR datasets.
-We are also looking to use machine learning in order to optimize the cost calculation.
+In future research, we will look into maximizing speed and efficiency to the point that our algorithm can assign full amino acid sequences.
+In order to achieve this, we will experiment with  both parallelization (techniques) and machine learning.
+The latter of these two will assist in optimizing the cost calculation while the former will increase the speed of assignment.
+We believe these implementations will help our algorithm handle datasets with numerous missing data points, validating our results even when given incomplete data.
 % subsection future_goals (end)

### 2014-03-27 paper/tex/Paper.tex
paper update

@@
 
-\section{Assignment Methods} % (fold)
+\section{Assignment} % (fold)
 \label{sec:method}
+
+\subsection{Data Collection} % (fold)
+\label{sub:data_collection}
+Determining the structure of a protein requires many highly involved steps.
+The first, which can take at least five days, is protein production.
+NMR experiments are then performed using the produced proteins in order to gather the data necessary for the assignment process.
+This process usually takes another one to two days for every spectrum involved.
+The most time consuming process is assignment of the structure.
+\cite{babak_alipanahi_error_2011}
 
@@
 % TODO
-add this part
-cite our sources
+In most cases, backbone NMR data is assigned manually.
+However, with hundreds of values for the chemical shift values of C(a) and C(b), this process can take anywhere from 20 days to 9 months with perfect data.
+To complicate matters even more, experience has shown most data sets to have missing or false peaks, requiring whomever is doing the actual assignment to either skip large portions of the protein sequence or to guess where a certain chain is located in the sequence, making this method extremely error prone.
+\cite{babak_alipanahi_error_2011}
 
@@
 % subsection future_goals (end)
-
-% subsection algorithm (end)
+\nocite{guntert_automated_2009}
+\nocite{brief_introduction_Poulsen}
 % section method (end)

### 2014-03-27 paper/tex/Paper.tex
paper update

@@
 Shifting our focus to optimizing the algorithm's speed while maintaining the accuracy we had managed to achieve, we were able to improve runtime.
-With the increased runtime, we were able to correctly assign forty to fifty amino acids.
-In future research, we plan to test with larger datasets, maximizing speed and efficiency to the point that our algorithm can assign full protein(amino acid?) sequences.
+With the increased runtime, we were able to correctly assign forty amino acids in less than a minute.
+In future research, we plan to test with larger datasets, maximizing speed and efficiency to the point that our algorithm can assign full protein sequences.
 We also plan to look into testing datasets with more than a few missing data points to verify that our algorithm correctly places amino acids when given less perfect data.
-- TIME FOR DATASETS?
 

### 2014-03-27 paper/tex/Paper.tex
image cite
bibtex stuff
We didn't increase runtime. We increased performance/decreased runtime.

@@
 \end{center}
-\caption{Expected Carbon Shift Values} % TODO citation
+\caption{Expected Carbon Shift Values \cite{carbon}} % TODO citation
 \label{fig:carbon}
@@
 Shifting our focus to optimizing the algorithm's speed while maintaining the accuracy we had managed to achieve, we were able to improve runtime.
-With the increased runtime, we were able to correctly assign forty amino acids in less than a minute.
+With the increased performance, we were able to correctly assign forty amino acids in less than a minute.
 In future research, we plan to test with larger datasets, maximizing speed and efficiency to the point that our algorithm can assign full protein sequences.
@@
 % subsection future_goals (end)
-\nocite{guntert_automated_2009}
-\nocite{brief_introduction_Poulsen}
+\nocite{*}
 % section method (end)

### 2014-03-27 paper/tex/Paper.tex
small changes

@@
 With the increased performance, we were able to correctly assign forty amino acids in less than a minute.
-In future research, we plan to test with larger datasets, maximizing speed and efficiency to the point that our algorithm can assign full protein sequences.
-We also plan to look into testing datasets with more than a few missing data points to verify that our algorithm correctly places amino acids when given less perfect data.
 

### 2014-03-27 paper/tex/Paper.tex
margin fix
ALMOST DONE

@@
 Des Moines, IA\\
-email % TODO
+joel.venzke@drake.edu
 }
@@
 \label{sub:introduction}
-Knowledge of a protein’s structure allows for further understanding of the function of a protein and alterations to its function that can lead to disease.
-Through the implementation of Nuclear magnetic resonance (NMR) spectroscopy, the structure of molecules, such as proteins, can be studied.
-However, assigning NMR spectroscopy generates large amounts of data that needs to be assigned.
+Knowledge of a protein's structure can explain the function of a protein and how alterations to its function can lead to disease.
+With the use of nuclear magnetic resonance (NMR) spectroscopy, the structure of molecules, such as proteins, can be studied.
+However, NMR spectroscopy generates large amounts of data that needs to be analyzed.
 This process can take months to complete and is prone to error.
-To allow for major advances in structural biology, a faster and more accurate method needs to be developed.
+To allow for major advances in structural biology, a faster and more accurate method of analysis needs to be developed.
 Our research focuses on developing an algorithm to automate the assignment process.
-We hope our attempts can minimize the human error and decrease the time consumption associated with manual assignment , increasing the overall effectiveness of the operation.
+We hope our attempts can minimize the human error and decrease the time consumption associated with manual assignment, increasing the overall effectiveness of the operation.
 
@@
 \label{sub:nmr}
-Several types of NMR variables can be used in the analysis of protein structures.
+Several types of NMR variables can be used in the analysis of proteins' structures.
 In particular, essential information is provided by the chemical shifts of NMR-active nuclei present in proteins, including hydrogen and isotopes of carbon and nitrogen.
@@
 This process usually takes another one to two days for every spectrum involved.
-The most time consuming process is assignment of the structure.
+After all the data has been gathered, the assigning of the protein's structure, the most lengthy of the steps, will then begin.
 \cite{babak_alipanahi_error_2011}
@@
 In most cases, backbone NMR data is assigned manually.
-However, with hundreds of values for the chemical shift values of C(a) and C(b), this process can take anywhere from 20 days to 9 months with perfect data.
-To complicate matters even more, experience has shown most data sets to have missing or false peaks, requiring whomever is doing the actual assignment to either skip large portions of the protein sequence or to guess where a certain chain is located in the sequence, making this method extremely error prone.
+However, with hundreds of chemical shift values, this process can take anywhere from 20 days to 9 months with perfect data.
+To complicate matters even more, experience has shown most data sets to have missing or false peaks, requiring whomever is doing the actual assignment to either skip large portions of the protein sequence or to guess where a certain chain is located in the sequence.
+As a result, this method is extremely error prone.
 \cite{babak_alipanahi_error_2011}
@@
 
-\subsection{Our Algorithm} % (fold)
+\subsection{Algorithm Design} % (fold)
 \label{sub:algorithm}
-Our algorithm begins by reading in an expected amino acid order and the NMR carbon shift data from a data file.
+Our algorithm begins by reading in an expected amino acid sequence and the NMR chemical shift data.
 It then changes the amino acids to their expected $C_\alpha$ and $C_{\beta}$ values and stores them in a list that represents the protein chain.
@@
 Before the search for the best solution begins, the tiles are grouped by the types of amino acids they could represent.
-The groups were created using the expected $C_\alpha$ and $C_{\beta}$ values shown in Figure~\ref{fig:carbon}.
-Grouping is done in an attempted to accelerate the assignment process.
-Tiles that do not match a group are grouped with the placeholder tiles.
+The groups are created using the expected $C_\alpha$ and $C_{\beta}$ values shown in Figure~\ref{fig:carbon}.
+Grouping is done in an attempt to accelerate the assignment process.
+Tiles that do not match are grouped with the placeholder tiles.
 
@@
 %start search
-To start the search, tiles in the placeholder group and tiles of the same amino acid group as the first amino acid in the protein chain are placed in the first position in a node.
-The tile is then compared to the first amino acid in the protein chain and a cost is generated.
-The cost is the sum of the cost of placing any previous tiles in the node, how well the current tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
-All of the generated nodes are placed in a frontier array.
+To start the search,  all the tiles matching the first amino acid in the reference protein chain are placed in the first position in a node.
+All placeholder tiles are also added to this position.
+The tile is then compared to the first amino acid in the protein chain to generate a cost.
+The cost is the sum of the differences generated by placing any previous tiles in the node, how well the current tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
+All of the generated nodes are placed in an array of possible solutions, also called the frontier.
 
 %continue assignment
-The node in the frontier with the lowest cost is removed from the frontier and used to generate child nodes.
-To generate a child node, a tile is added to the end of the node.
+The node in the frontier with the lowest cost is removed from the array and used to generate child nodes.
+To create a child node, a tile is added to the end of the node.
 A child node is generated for all unplaced tiles that are either in the placeholder group or in the group matching the corresponding amino acid in the protein chain.
-The cost of placing the tile is then generated.
-The child nodes are then added to the frontier, and the process of generating child nodes is repeated.
+The cost of placing the tile is then calculated.
+Next, the child nodes are added to the frontier, and the process of generating child nodes is repeated until a goal state is reached.
 
@@
 Once a node has every tile placed, it is said to be in the goal state.
-The first node that reaches goal state is stored as the current best solution.
+The first node that reaches this state is stored as the current best solution.
 Every node that achieves goal state is compared to the current best solution.
-The node with the lowest cost is then saved as the current best solution.
+The node with the lowest cost is then replaces the previously stored best solution.
 
 %solution found
-A solution has been found once the current best solution's cost is lower than the cost of any nodes in the frontier.
-The search is then ended.
-The algorithm then outputs the cost of the best solution followed by the assigned carbon shift values.
+A solution has been found once the current best solution's cost is lower than the cost of any other nodes in the frontier.
+The search is completed.
+The algorithm then outputs the cost of the best solution followed by the assigned chemical shift values.
 
@@
 Initially, we focused our research on accurate assignment at the cost of speed.
-Thus, at the start of our research our algorithm was only able to assign smaller datasets with a chain of ten to fifteen amino acids.
+Thus, at the start of our research, our algorithm was only able to assign smaller datasets with a chain of ten to fifteen amino acids.
 Shifting our focus to optimizing the algorithm's speed while maintaining the accuracy we had managed to achieve, we were able to improve runtime.
-With the increased performance, we were able to correctly assign forty amino acids in less than a minute.
+With the increased performance, we were able to correctly assign forty amino acids in approximately seventy seconds.
 
@@
 \label{sub:future_goals}
-In future research, we will look into maximizing speed and efficiency to the point that our algorithm can assign full amino acid sequences.
-In order to achieve this, we will experiment with  both parallelization (techniques) and machine learning.
+In future research, we will look into maximizing speed and efficiency with the goal of assigning  full amino acid sequences.
+In order to achieve this, we will experiment with both parallelization  and machine learning.
 The latter of these two will assist in optimizing the cost calculation while the former will increase the speed of assignment.

### 2014-03-27 paper/tex/Paper.tex
bibtex

@@
 
-\documentclass[12pt]{article}
+\documentclass[12pt, letter]{article}
 
@@
 \usepackage{times} %For typeface
-
+\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
 \begin{document}
@@
 In most cases, backbone NMR data is assigned manually.
-However, with hundreds of chemical shift values, this process can take anywhere from 20 days to 9 months with perfect data.
+However, with hundreds of chemical shift values, this process can take anywhere from 20 days to 9 months with perfect data\cite{guntert_automated_2009}.
 To complicate matters even more, experience has shown most data sets to have missing or false peaks, requiring whomever is doing the actual assignment to either skip large portions of the protein sequence or to guess where a certain chain is located in the sequence.
-As a result, this method is extremely error prone.
-\cite{babak_alipanahi_error_2011}
+As a result, this method is extremely error prone \cite{babak_alipanahi_error_2011}.
 
@@
 % subsection future_goals (end)
-\nocite{*}
 % section method (end)

### 2014-03-27 search_project/search_project.py
add runtime and updated test code

@@ -20,5 +20,5 @@ start = time.clock()
 search_strategies.uniform_cost(file_name)
 end = time.clock()
 
-# print "Run Time:  " + str(end-start)
+print "Run Time:  " + str(end-start)
 

### 2014-03-27 paper/tex/Paper.tex
added figures to paper

@@
 Determining the chemical shifts of all or most of the nuclei in a biomolecule is the first step in determining its structure.
-An important set of chemical shifts in a protein are those corresponding to the nuclei in the backbone of the protein polypeptide chain, including the nitrogen, attached hydrogen, and the alpha and beta carbon atoms ($C_\alpha$ and $C_{\beta}$) of each residue.
+An important set of chemical shifts in a protein are those corresponding to the nuclei in the backbone of the protein polypeptide chain, including the nitrogen, attached hydrogen, and the alpha and beta carbon atoms ($C_\alpha$ and $C_{\beta}$) of each residue shown in Figure~\ref{fig:nmr}.
 These chemical shifts are measured using various three-dimensional NMR experiments, and then matched to the individual residues in the protein in a process called sequential assignment.
 
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=.6\textwidth]{diagram}
+\end{center}
+\caption{NMR} % TODO
+\label{fig:nmr}
+\end{figure}
 A prerequisite of the assignment process is data collection using experiments that can provide connectivities between neighboring residues.
@@
 Shifting our focus to optimizing the algorithm's speed while maintaining the accuracy we had managed to achieve, we were able to improve runtime.
-With the increased performance, we were able to correctly assign forty amino acids in approximately seventy seconds.
+With the increased performance, we were able to correctly assign forty amino acids in less than 30 seconds.
+The results of our testing are shown in Figure~\ref{fig:plot}.
+
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=.65\textwidth]{plot}
+\end{center}
+\caption{Time of Assignment} 
+\label{fig:plot}
+\end{figure}
+
+Since we are using real data to test the algorithm, some data points are missing.
+Missing data can leads to dramatic increases assignment time.
+The jump in runtime between 37 and 38 residues, seen in Figure~\ref{fig:plot}, is one such example.
+Residue 38 is missing the $C_\alpha$ and $C_{\beta}$ values for residue $i-1$.
+The missing data forces the algorithm to explore a greater number of possibilities to ensure accurate assignment.
 

### 2014-04-06 paper/tex/Paper.tex

@@
 With the use of nuclear magnetic resonance (NMR) spectroscopy, the structure of molecules, such as proteins, can be studied.
-However, NMR spectroscopy generates large amounts of data that needs to be analyzed.
+However, NMR spectroscopy generates large amounts of data that need to be analyzed.
 This process can take months to complete and is prone to error.
@@
 This pattern of sequentially linked chemical shift values reflects the sequential linear arrangement of the individual residues in the protein sequence.
-The pattern is then matched with the protein sequence, by using the fact that certain residues have characteristic $C_\alpha$ and $C_{\beta}$ chemical shift ranges which uniquely identify them.
+The pattern is then matched with the protein sequence by using the fact that certain residues have characteristic $C_\alpha$ and $C_{\beta}$ chemical shift ranges to uniquely identify them.
 Thus, each measured chemical shift is assigned to a protein residue, and this information can then be used to infer structural information about the biomolecule.
@@
 This process usually takes another one to two days for every spectrum involved.
-After all the data has been gathered, the assigning of the protein's structure, the most lengthy of the steps, will then begin.
-\cite{babak_alipanahi_error_2011}
+After all the data has been gathered, the assigning of the protein's structure, the most lengthy of the steps, will begin \cite{babak_alipanahi_error_2011}.
 
@@
 In most cases, backbone NMR data is assigned manually.
-However, with hundreds of chemical shift values, this process can take anywhere from 20 days to 9 months with perfect data\cite{guntert_automated_2009}.
+However, with hundreds of chemical shift values, this process can take anywhere from 20 days to 9 months with perfect data \cite{guntert_automated_2009}.
 To complicate matters even more, experience has shown most data sets to have missing or false peaks, requiring whomever is doing the actual assignment to either skip large portions of the protein sequence or to guess where a certain chain is located in the sequence.
@@
 \label{sub:algorithm}
-Our algorithm begins by reading in an expected amino acid sequence and the NMR chemical shift data.
+Our algorithm, which is designed to decrease the error and time consumption associated with manual assignment, begins by reading in an expected amino acid sequence and the NMR chemical shift data.
 It then changes the amino acids to their expected $C_\alpha$ and $C_{\beta}$ values and stores them in a list that represents the protein chain.
-Next, the carbon shift values for a single amino acid are placed in a tile.
-A tile contains the $C_\alpha$ and $C_{\beta}$ values for the amino acid residue $i$ and residue $i-1$.
+A tile containing the $C_\alpha$ and $C_{\beta}$ values for the amino acid residue $i$ and residue ($i-1$) is then created.
 Next, missing data is accounted for.
 If there are fewer tiles than the number of amino acids in the protein chain, placeholder tiles are generated to make up the difference.
-Before the search for the best solution begins, the tiles are grouped by the types of amino acids they could represent.
-The groups are created using the expected $C_\alpha$ and $C_{\beta}$ values shown in Figure~\ref{fig:carbon}.
-Grouping is done in an attempt to accelerate the assignment process.
+Before the search for the best solution begins, the tiles are grouped by the types of amino acids they most likely represent in an attempt to accelerate the assignment process.
+These groups are created using the expected $C_\alpha$ and $C_{\beta}$ values shown in Figure~\ref{fig:carbon}.
 Tiles that do not match are grouped with the placeholder tiles.
@@
 %start search
-To start the search,  all the tiles matching the first amino acid in the reference protein chain are placed in the first position in a node.
+To start the search,  all the tiles matching the first amino acid in the reference protein chain are placed in the first position of a node.
 All placeholder tiles are also added to this position.
 The tile is then compared to the first amino acid in the protein chain to generate a cost.
-The cost is the sum of the differences generated by placing any previous tiles in the node, how well the current tile matched the corresponding amino acid in the protein chain and how well the tile's residue $i-1$ values match the residue $i$ values of the tile placed before it.
+The cost is the sum of the differences generated by placing any previous tiles in the node, how well the current tile matches the corresponding amino acid in the protein chain, and the disparity between the tile's residue ($i-1$) values and the residue $i$ values of the tile placed before it.
 All of the generated nodes are placed in an array of possible solutions, also called the frontier.
@@
 %continue assignment
-The node in the frontier with the lowest cost is removed from the array and used to generate child nodes.
-To create a child node, a tile is added to the end of the node.
+The node in the frontier with the lowest cost is removed from the array and used to generate child nodes, which is accomplished simply by adding a tile to the end of the node.
 A child node is generated for all unplaced tiles that are either in the placeholder group or in the group matching the corresponding amino acid in the protein chain.
 The cost of placing the tile is then calculated.
-Next, the child nodes are added to the frontier, and the process of generating child nodes is repeated until a goal state is reached.
+Next, the child nodes are added to the frontier.
+This process of generating child nodes is repeated until a goal state is reached.
 
@@
 The first node that reaches this state is stored as the current best solution.
-Every node that achieves goal state is compared to the current best solution.
-The node with the lowest cost is then replaces the previously stored best solution.
+Every node that achieves the goal state is compared to the current best solution.
+The node with the lowest cost then replaces the previously stored best solution.
 
 %solution found
-A solution has been found once the current best solution's cost is lower than the cost of any other nodes in the frontier.
+The final solution has been found once the current best solution's cost is lower than the cost of any other nodes in the frontier.
 The search is completed.
@@
 \begin{center}
-\includegraphics[width=.65\textwidth]{plot}
+\includegraphics[width=.6\textwidth]{plot}
 \end{center}
@@
 Since we are using real data to test the algorithm, some data points are missing.
-Missing data can leads to dramatic increases assignment time.
+Missing data can lead to dramatic increases in assignment time.
 The jump in runtime between 37 and 38 residues, seen in Figure~\ref{fig:plot}, is one such example.
-Residue 38 is missing the $C_\alpha$ and $C_{\beta}$ values for residue $i-1$.
-The missing data forces the algorithm to explore a greater number of possibilities to ensure accurate assignment.
+Residue 38 is missing the $C_\alpha$ and $C_{\beta}$ values for residue ($i-1$).
+This missing data forces the algorithm to explore a greater number of possibilities to ensure accurate assignment, incidentally increasing the time it takes for the best solution to be found.
 

### 2014-04-07 presentation/graphic/time_line.tex
Presentation finished up

\documentclass[10pt, varwidth]{standalone}

%
% compile using: pdflatex -shell-escape reu_paper.tex
%

\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{shapes,arrows}

\usepackage{pgfplots}

\usepackage{caption}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{mdwlist}
\usepackage{mathtools}
\usepackage{url}

\date{}

\begin{document}
\maketitle
\vspace{-3cm}

\begin{tikzpicture} [scale=.5]
		\draw [thick] (1.5,6.5) -- (13.5,6.5) -- (13.5,3.5) -- (1.5,3.5) -- (1.5,6.5);
		\node[align=center] at (4.5,5) {\textbf{Tiles to assign:}};
		\node[align=center, box, draw] at (8.5,5) {13\\9};
		\node[align=center, box, draw] at (10.5,5) {11\\13};
		\node[align=center, box, draw] at (12.5,5) {9\\12};		
		\draw [thick] (-4,2) -- (18,2);

		\node[align=right] at (11,2.5) {\textbf{Tiles}};

		\node[align=center, box, draw] at (5,0) {13\\9};
		\node[align=center] at (6.5,0) {1.5};
		\node[align=center, box, draw, fill = green] at (11,0) {11\\13};
		\node[align=center] at (12.5,0) {0.5};
		\node[align=center, box, draw, fill = orange] at (16.5,0) {9\\12};
		\node[align=center] at (18,0) {2.5};

		\draw (11,-1) -- (9.5,-1.5);
		\draw (11,-1) -- (13,-1.5);

		\node[align=center, box, draw, fill = green] at (9.5,-2.5) {13\\9};
		\node[align=center] at (11,-2.5) {1.0};
		\node[align=center, box, draw, fill = orange] at (12.5,-2.5) {9\\12};
		\node[align=center] at (14,-2.5) {8.0};

		\draw (5,-1) -- (3.5,-1.5);
		\draw (5,-1) -- (6.5,-1.5);

		\node[align=center, box, draw, fill = orange] at (3.5,-2.5) {13\\9};
		\node[align=center] at (5,-2.5) {6.0};
		\node[align=center, box, draw, fill = orange] at (6.5,-2.5) {9\\12};
		\node[align=center] at (8,-2.5) {5.0};

		\draw (9.5,-4) -- (9.5,-3.5);

		\node[align=center, box, draw, fill = green] at (9.5,-5) {9\\12};
		\node[align=center] at (11,-5) {1.6};

		\draw [thick] (2,3) -- (2,-6);

		\node[align=right] at (-1,2.5) {\textbf{Protein Chain}};
		\node[align=right] at (-1,0) {11.5};
		\node[align=right] at (-1,-2.5) {12.5};
		\node[align=right] at (-1,-5) {9.6};

	\end{tikzpicture}
\end{document}

### 2014-04-08 presentation/graphic/time_line.tex
added test files, made new graph, fixed typo, fix figure

@@
 	\begin{tikzpicture} [scale=.5]
-		\draw [thick] (1.5,6.5) -- (13.5,6.5) -- (13.5,3.5) -- (1.5,3.5) -- (1.5,6.5);
-		\node[align=center] at (4.5,5) {\textbf{Tiles to assign:}};
-		\node[align=center, box, draw] at (8.5,5) {13\\9};
-		\node[align=center, box, draw] at (10.5,5) {11\\13};
-		\node[align=center, box, draw] at (12.5,5) {9\\12};		
+		\draw [thick] (6,6) -- (10,6) -- (10,3.5) -- (6,3.5) -- (6,6);
+		\draw [thick] (14.5,6) -- (10.5,6) -- (10.5,3.5) -- (14.5,3.5) -- (14.5,6);
+		\node[align=center] at (2.5,4.75) {\textbf{Tiles to assign:}};
+		\node[align=center, above] at (8,6) {Group 1};
+		\node[align=center, above] at (12.5,6) {Group 2};
+		\node[align=center, box, draw] at (7,4.75) {13\\9};
+		\node[align=center, box, draw] at (9,4.75) {11\\13};
+		\node[align=center, box, draw] at (12.5,4.75) {9\\12};		
 		\draw [thick] (-4,2) -- (18,2);
 
-		\node[align=right] at (11,2.5) {\textbf{Tiles}};
+		\node[align=right] at (10.5,2.8) {\scriptsize \textbf{Nodes}};
 
-		\node[align=center, box, draw] at (5,0) {13\\9};
-		\node[align=center] at (6.5,0) {1.5};
-		\node[align=center, box, draw, fill = green] at (11,0) {11\\13};
-		\node[align=center] at (12.5,0) {0.5};
-		\node[align=center, box, draw, fill = orange] at (16.5,0) {9\\12};
-		\node[align=center] at (18,0) {2.5};
+		\node[align=center, box, draw] at (7,.5) {13\\9};
+		\node[align=center] at (8.5,.5) {1.5};
+		\node[align=center, box, draw, fill = green] at (14,.5) {11\\13};
+		\node[align=center] at (15.5,.5) {0.5};
 
-		\draw (11,-1) -- (9.5,-1.5);
-		\draw (11,-1) -- (13,-1.5);
+		\draw (10.5,2) -- (7,1.5);
+		\draw (10.5,2) -- (14,1.5);
 
-		\node[align=center, box, draw, fill = green] at (9.5,-2.5) {13\\9};
-		\node[align=center] at (11,-2.5) {1.0};
-		\node[align=center, box, draw, fill = orange] at (12.5,-2.5) {9\\12};
-		\node[align=center] at (14,-2.5) {8.0};
+		\node[align=center, box, draw, fill = green] at (14,-2) {13\\9};
+		\node[align=center] at (15.5,-2) {1.0};
 
-		\draw (5,-1) -- (3.5,-1.5);
-		\draw (5,-1) -- (6.5,-1.5);
+		\draw (7,-.5) -- (7,-1);
+		\draw (14,-.5) -- (14,-1);
 
-		\node[align=center, box, draw, fill = orange] at (3.5,-2.5) {13\\9};
-		\node[align=center] at (5,-2.5) {6.0};
-		\node[align=center, box, draw, fill = orange] at (6.5,-2.5) {9\\12};
-		\node[align=center] at (8,-2.5) {5.0};
+		\node[align=center, box, draw, fill = orange] at (7,-2) {11\\13};
+		\node[align=center] at (8.5,-2) {5.0};
 
-		\draw (9.5,-4) -- (9.5,-3.5);
+		\draw (14,-3) -- (14,-3.5);
 
-		\node[align=center, box, draw, fill = green] at (9.5,-5) {9\\12};
-		\node[align=center] at (11,-5) {1.6};
+		\node[align=center, box, draw, fill = green] at (14,-4.5) {9\\12};
+		\node[align=center] at (15.5,-4.5) {1.6};
 
-		\draw [thick] (2,3) -- (2,-6);
+		\draw [thick] (2,3.5) -- (2,-5.5);
 
-		\node[align=right] at (-1,2.5) {\textbf{Protein Chain}};
-		\node[align=right] at (-1,0) {11.5};
-		\node[align=right] at (-1,-2.5) {12.5};
-		\node[align=right] at (-1,-5) {9.6};
+		\draw  (-.75,1.75) -- (-.75,-5.5);
+		\draw  (-4,1.125) -- (1.25,1.125);
+
+		\node[align=right] at (-1,3.2) {\scriptsize \textbf{Reference}};
+		\node[align=right] at (-1,2.5) {\scriptsize \textbf{Protein Chain}};
+		\node[align=right] at (-2.5,1.5) {\tiny Chemical Shift};
+		\node[align=right] at (.25,1.5) {\tiny Group};
+		\node[align=right] at (-2.5,.5) {11.5};
+		\node[align=right] at (-2.5,-2) {12.5};
+		\node[align=right] at (-2.5,-4.5) {9.6};
+		\node[align=right] at (.25,.5) {1};
+		\node[align=right] at (.25,-2) {1};
+		\node[align=right] at (.25,-4.5) {2};
 

### 2014-04-08 presentation/percent_graph/test.tex
added test files, made new graph, fixed typo, fix figure

% to run use
% $ pdflatex -shell-escape plot.tex

\documentclass[varwidth]{standalone}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{graphics}
\usepackage{graphicx}

\begin{document}
\begin{figure}
\begin{center}
\begin{tikzpicture}

\begin{axis}[width = \columnwidth, grid=major, xlabel={Number of Residues}, ylabel={Time to Completion (seconds)}]
\addplot[no markers, red] gnuplot [raw gnuplot] { 
fac(x) = (int(x)==0) ? 1.0 : int(x) * fac(int(x)-1.0);
g(x) = (a*x**2+b*x+c)/(d*x+e);
fit g(x) 'percent.dat' using 1:(log10($2/fac($1))) via a,b,c,d,e;
plot 'percent.dat' using 1:(log10($2/fac($1))) title 'Data', g(x);
};

\end{axis}
\end{tikzpicture}
% \caption{Time to completion for analysis of a uniform filesystem with uniform branching factor two plotted with entry counts.}
% \label{fig:radix_2_line}
\end{center}
\end{figure}
\end{document}

### 2014-04-08 presentation/graphic/time_line.tex
fixed graphic
more presentation stuff

@@
 		\draw [thick] (14.5,6) -- (10.5,6) -- (10.5,3.5) -- (14.5,3.5) -- (14.5,6);
-		\node[align=center] at (2.5,4.75) {\textbf{Tiles to assign:}};
+		\node[align=center] at (0,4.75) {\textbf{Tiles to assign:}};
+		\node[align=center] at (4.25,4.75) {$i-1$\\$i$};
+		\draw [thick] (5.5,6) -- (3,6) -- (3,3.5) -- (5.5,3.5) -- (5.5,6);
 		\node[align=center, above] at (8,6) {Group 1};
 		\node[align=center, above] at (12.5,6) {Group 2};
-		\node[align=center, box, draw] at (7,4.75) {13\\9};
-		\node[align=center, box, draw] at (9,4.75) {11\\13};
-		\node[align=center, box, draw] at (12.5,4.75) {9\\12};		
+		\node[align=center, rounded corners, box, draw] at (7,4.75) {9\\12};
+		\node[align=center, rounded corners, box, draw] at (9,4.75) {11\\13};
+		\node[align=center, rounded corners, box, draw] at (12.5,4.75) {13\\9};		
 		\draw [thick] (-4,2) -- (18,2);
@@
 
-		\node[align=center, box, draw] at (7,.5) {13\\9};
+		\node[align=center, rounded corners, box, draw] at (7,.5) {9\\12};
 		\node[align=center] at (8.5,.5) {1.5};
-		\node[align=center, box, draw, fill = green] at (14,.5) {11\\13};
+		\node[align=center, rounded corners, box, draw, fill = green] at (14,.5) {11\\13};
 		\node[align=center] at (15.5,.5) {0.5};
@@
 
-		\node[align=center, box, draw, fill = green] at (14,-2) {13\\9};
+		\node[align=center, rounded corners, box, draw, fill = green] at (14,-2) {13\\9};
 		\node[align=center] at (15.5,-2) {1.0};
@@
 
-		\node[align=center, box, draw, fill = orange] at (7,-2) {11\\13};
-		\node[align=center] at (8.5,-2) {5.0};
+		\node[align=center, rounded corners, box, draw, fill = orange] at (7,-2) {13\\9};
+		\node[align=center] at (8.5,-2) {3.0};
 
@@
 
-		\node[align=center, box, draw, fill = green] at (14,-4.5) {9\\12};
+		\node[align=center, rounded corners, box, draw, fill = green] at (14,-4.5) {9\\12};
 		\node[align=center] at (15.5,-4.5) {1.6};
@@
 		\node[align=right] at (.25,1.5) {\tiny Group};
-		\node[align=right] at (-2.5,.5) {11.5};
-		\node[align=right] at (-2.5,-2) {12.5};
-		\node[align=right] at (-2.5,-4.5) {9.6};
+		\node[align=right] at (-2.5,.5) {13.5};
+		\node[align=right] at (-2.5,-2) {9.5};
+		\node[align=right] at (-2.5,-4.5) {11.4};
 		\node[align=right] at (.25,.5) {1};
-		\node[align=right] at (.25,-2) {1};
-		\node[align=right] at (.25,-4.5) {2};
+		\node[align=right] at (.25,-2) {2};
+		\node[align=right] at (.25,-4.5) {1};
 

### 2014-04-22 presentation/tilePlacement/step10.tex
updated graphics

--- 2014-04-08 presentation/graphic/time_line.tex
@@
 	\begin{tikzpicture} [scale=.5]
+
+		% Tile groups 
 		\draw [thick] (6,6) -- (10,6) -- (10,3.5) -- (6,3.5) -- (6,6);
@@
 		\node[align=center, above] at (12.5,6) {Group 2};
+
+		% tiles
 		\node[align=center, rounded corners, box, draw] at (7,4.75) {9\\12};
 		\node[align=center, rounded corners, box, draw] at (9,4.75) {11\\13};
-		\node[align=center, rounded corners, box, draw] at (12.5,4.75) {13\\9};		
+		\node[align=center, rounded corners, box, draw] at (11.5,4.75) {13\\9};
+		\node[align=center, rounded corners, box, draw] at (13.5,4.75) {12\\9.2};		
 		\draw [thick] (-4,2) -- (18,2);
 
+		% title
 		\node[align=right] at (10.5,2.8) {\scriptsize \textbf{Nodes}};
 
+		%first 
 		\node[align=center, rounded corners, box, draw] at (7,.5) {9\\12};
-		\node[align=center] at (8.5,.5) {1.5};
+		% \node[align=center] at (8.5,.5) {1.5};
 		\node[align=center, rounded corners, box, draw, fill = green] at (14,.5) {11\\13};
-		\node[align=center] at (15.5,.5) {0.5};
-
+		% \node[align=center] at (15.5,.5) {0.5};
 		\draw (10.5,2) -- (7,1.5);
@@
 
-		\node[align=center, rounded corners, box, draw, fill = green] at (14,-2) {13\\9};
-		\node[align=center] at (15.5,-2) {1.0};
+		%right side row 2
+		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-2) {13\\9};
+		% \node[align=center] at (14,-2) {1.0};
+		\draw (14,-.5) -- (12.5,-1);
+		\node[align=center, rounded corners, box, draw] at (15.5,-2) {12\\9.2};
+		% \node[align=center] at (17,-2) {1.8};
+		\draw (14,-.5) -- (15.5,-1);
 
-		\draw (7,-.5) -- (7,-1);
-		\draw (14,-.5) -- (14,-1);
+		% left side row 2
+		\draw (7,-.5) -- (5.5,-1);
+		\draw (7,-.5) -- (8.5,-1);
+		\node[align=center, rounded corners, box, draw, fill = orange] at (5.5,-2) {13\\9};
+		\node[align=center] at (7,-2) {3.0};
+		\node[align=center, rounded corners, box, draw] at (8.5,-2) {12\\9.2};
+		% \node[align=center] at (10,-2) {1.8};
 
-		\node[align=center, rounded corners, box, draw, fill = orange] at (7,-2) {13\\9};
-		\node[align=center] at (8.5,-2) {3.0};
+		% left side row 3
+		\node[align=center, rounded corners, box, draw, fill = orange] at (8.5,-4.5) {11\\13};
+		\node[align=center] at (10,-4.5) {5.2};
+		\draw (8.5,-3) -- (8.5,-3.5);
 
-		\draw (14,-3) -- (14,-3.5);
+		% right side row 3
+		\draw (12.5,-3) -- (12.5,-3.5);
+		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-4.5) {9\\12};
+		% \node[align=center] at (14,-4.5) {1.6};
+		\draw (15.5,-3) -- (15.5,-3.5);
+		\node[align=center, rounded corners, box, draw, fill = orange] at (15.5,-4.5) {9\\12};
+		\node[align=center] at (17,-4.5) {2.6};
 
-		\node[align=center, rounded corners, box, draw, fill = green] at (14,-4.5) {9\\12};
-		\node[align=center] at (15.5,-4.5) {1.6};
+		% right side row 4
+		\draw (12.5,-5.5) -- (12.5,-6);
+		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-7) {12\\9.2};
+		\node[align=center] at (14,-7) {2.0};
 
-		\draw [thick] (2,3.5) -- (2,-5.5);
-
-		\draw  (-.75,1.75) -- (-.75,-5.5);
+		% grid
+		\draw [thick] (2,3.5) -- (2,-8);
+		\draw  (-.75,1.75) -- (-.75,-8);
 		\draw  (-4,1.125) -- (1.25,1.125);
@@
 		\node[align=right] at (-2.5,-4.5) {11.4};
+		\node[align=right] at (-2.5,-7) {8.8};
 		\node[align=right] at (.25,.5) {1};
@@
 		\node[align=right] at (.25,-4.5) {1};
+		\node[align=right] at (.25,-7) {2};
 

### 2014-04-22 presentation/tilePlacement/step4.tex
updated graphics

--- 2014-04-08 presentation/graphic/time_line.tex
@@
 		\node[align=center, above] at (12.5,6) {Group 2};
+
+		% tiles
 		\node[align=center, rounded corners, box, draw] at (7,4.75) {9\\12};
 		\node[align=center, rounded corners, box, draw] at (9,4.75) {11\\13};
-		\node[align=center, rounded corners, box, draw] at (12.5,4.75) {13\\9};		
+		\node[align=center, rounded corners, box, draw] at (11.5,4.75) {13\\9};
+		\node[align=center, rounded corners, box, draw] at (13.5,4.75) {12\\9.2};		
 		\draw [thick] (-4,2) -- (18,2);
 
+		% title
 		\node[align=right] at (10.5,2.8) {\scriptsize \textbf{Nodes}};
 
-		\node[align=center, rounded corners, box, draw] at (7,.5) {9\\12};
+		%first 
+		\node[align=center, rounded corners, box, draw, fill = orange] at (7,.5) {9\\12};
 		\node[align=center] at (8.5,.5) {1.5};
@@
 		\node[align=center] at (15.5,.5) {0.5};
-
 		\draw (10.5,2) -- (7,1.5);
@@
 
-		\node[align=center, rounded corners, box, draw, fill = green] at (14,-2) {13\\9};
-		\node[align=center] at (15.5,-2) {1.0};
+		%right side row 2
+		\node[align=center, rounded corners, box, draw, fill = orange] at (12.5,-2) {13\\9};
+		\node[align=center] at (14,-2) {1.0};
+		\draw (14,-.5) -- (12.5,-1);
+		\node[align=center, rounded corners, box, draw, fill = orange] at (15.5,-2) {12\\9.2};
+		\node[align=center] at (17,-2) {1.8};
+		\draw (14,-.5) -- (15.5,-1);
 
-		\draw (7,-.5) -- (7,-1);
-		\draw (14,-.5) -- (14,-1);
-
-		\node[align=center, rounded corners, box, draw, fill = orange] at (7,-2) {13\\9};
-		\node[align=center] at (8.5,-2) {3.0};
-
-		\draw (14,-3) -- (14,-3.5);
-
-		\node[align=center, rounded corners, box, draw, fill = green] at (14,-4.5) {9\\12};
-		\node[align=center] at (15.5,-4.5) {1.6};
-
-		\draw [thick] (2,3.5) -- (2,-5.5);
-
-		\draw  (-.75,1.75) -- (-.75,-5.5);
+		% grid
+		\draw [thick] (2,3.5) -- (2,-8);
+		\draw  (-.75,1.75) -- (-.75,-8);
 		\draw  (-4,1.125) -- (1.25,1.125);

### 2014-04-22 presentation/tilePlacement/step5.tex
updated graphics

--- 2014-04-22 presentation/tilePlacement/step4.tex
@@
 		\node[align=center] at (8.5,.5) {1.5};
-		\node[align=center, rounded corners, box, draw, fill = green] at (14,.5) {11\\13};
-		\node[align=center] at (15.5,.5) {0.5};
+		\node[align=center, rounded corners, box, draw] at (14,.5) {11\\13};
+		%\node[align=center] at (15.5,.5) {0.5};
 		\draw (10.5,2) -- (7,1.5);
@@
 		%right side row 2
-		\node[align=center, rounded corners, box, draw, fill = orange] at (12.5,-2) {13\\9};
+		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-2) {13\\9};
 		\node[align=center] at (14,-2) {1.0};
@@
 		\draw (14,-.5) -- (15.5,-1);
+
+		% right side row 3
+		\draw (12.5,-3) -- (12.5,-3.5);
+		\node[align=center, rounded corners, box, draw, fill = orange] at (12.5,-4.5) {9\\12};
+		\node[align=center] at (14,-4.5) {1.6};
 

### 2014-04-22 presentation/tilePlacement/step6.tex
updated graphics

--- 2014-04-22 presentation/tilePlacement/step5.tex
@@
 		%first 
-		\node[align=center, rounded corners, box, draw, fill = orange] at (7,.5) {9\\12};
+		\node[align=center, rounded corners, box, draw, fill = green] at (7,.5) {9\\12};
 		\node[align=center] at (8.5,.5) {1.5};
@@
 		%right side row 2
-		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-2) {13\\9};
-		\node[align=center] at (14,-2) {1.0};
+		\node[align=center, rounded corners, box, draw] at (12.5,-2) {13\\9};
+		%\node[align=center] at (14,-2) {1.0};
 		\draw (14,-.5) -- (12.5,-1);
@@
 		\draw (14,-.5) -- (15.5,-1);
+
+		% left side row 2
+		\draw (7,-.5) -- (5.5,-1);
+		\draw (7,-.5) -- (8.5,-1);
+		\node[align=center, rounded corners, box, draw, fill = orange] at (5.5,-2) {13\\9};
+		\node[align=center] at (7,-2) {3.0};
+		\node[align=center, rounded corners, box, draw, fill = orange] at (8.5,-2) {12\\9.2};
+		\node[align=center] at (10,-2) {1.8};
 

### 2014-04-22 presentation/tilePlacement/step7.tex
updated graphics

--- 2014-04-22 presentation/tilePlacement/step6.tex
@@
 		%first 
-		\node[align=center, rounded corners, box, draw, fill = green] at (7,.5) {9\\12};
-		\node[align=center] at (8.5,.5) {1.5};
+		\node[align=center, rounded corners, box, draw] at (7,.5) {9\\12};
+		% \node[align=center] at (8.5,.5) {1.5};
 		\node[align=center, rounded corners, box, draw] at (14,.5) {11\\13};
-		%\node[align=center] at (15.5,.5) {0.5};
+		% \node[align=center] at (15.5,.5) {0.5};
 		\draw (10.5,2) -- (7,1.5);
@@
 		\node[align=center, rounded corners, box, draw] at (12.5,-2) {13\\9};
-		%\node[align=center] at (14,-2) {1.0};
+		% \node[align=center] at (14,-2) {1.0};
 		\draw (14,-.5) -- (12.5,-1);
@@
 		\draw (12.5,-3) -- (12.5,-3.5);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (12.5,-4.5) {9\\12};
+		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-4.5) {9\\12};
 		\node[align=center] at (14,-4.5) {1.6};
+
+		% right side row 4
+		\draw (12.5,-5.5) -- (12.5,-6);
+		\node[align=center, rounded corners, box, draw, fill = orange] at (12.5,-7) {12\\9.2};
+		\node[align=center] at (14,-7) {2.0};
 

### 2014-04-22 presentation/tilePlacement/step8.tex
updated graphics

--- 2014-04-22 presentation/tilePlacement/step7.tex
@@
 		\node[align=center] at (7,-2) {3.0};
-		\node[align=center, rounded corners, box, draw, fill = orange] at (8.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, box, draw, fill = green] at (8.5,-2) {12\\9.2};
 		\node[align=center] at (10,-2) {1.8};
+
+		% left side row 3
+		\node[align=center, rounded corners, box, draw, fill = orange] at (8.5,-4.5) {11\\13};
+		\node[align=center] at (10,-4.5) {5.2};
+		\draw (8.5,-3) -- (8.5,-3.5);
 
@@
 		\draw (12.5,-3) -- (12.5,-3.5);
-		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-4.5) {9\\12};
-		\node[align=center] at (14,-4.5) {1.6};
+		\node[align=center, rounded corners, box, draw] at (12.5,-4.5) {9\\12};
+		% \node[align=center] at (14,-4.5) {1.6};
 

### 2014-04-22 presentation/tilePlacement/step9.tex
updated graphics

--- 2014-04-22 presentation/tilePlacement/step8.tex
@@
 		\draw (14,-.5) -- (12.5,-1);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (15.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, box, draw, fill = green] at (15.5,-2) {12\\9.2};
 		\node[align=center] at (17,-2) {1.8};
@@
 		\node[align=center] at (7,-2) {3.0};
-		\node[align=center, rounded corners, box, draw, fill = green] at (8.5,-2) {12\\9.2};
-		\node[align=center] at (10,-2) {1.8};
+		\node[align=center, rounded corners, box, draw] at (8.5,-2) {12\\9.2};
+		% \node[align=center] at (10,-2) {1.8};
 
@@
 		% \node[align=center] at (14,-4.5) {1.6};
+		\draw (15.5,-3) -- (15.5,-3.5);
+		\node[align=center, rounded corners, box, draw, fill = orange] at (15.5,-4.5) {9\\12};
+		\node[align=center] at (17,-4.5) {2.6};
 

### 2014-04-22 presentation/tilePlacement/step10.tex
added naive graphic and fixed errors

@@
 \begin{document}
-\maketitle
 \vspace{-3cm}
@@
 		% tiles
-		\node[align=center, rounded corners, box, draw] at (7,4.75) {9\\12};
-		\node[align=center, rounded corners, box, draw] at (9,4.75) {11\\13};
-		\node[align=center, rounded corners, box, draw] at (11.5,4.75) {13\\9};
-		\node[align=center, rounded corners, box, draw] at (13.5,4.75) {12\\9.2};		
+		\node[align=center, rounded corners, draw] at (7,4.75) {9\\12};
+		\node[align=center, rounded corners, draw] at (9,4.75) {11\\13};
+		\node[align=center, rounded corners, draw] at (11.5,4.75) {13\\9};
+		\node[align=center, rounded corners, draw] at (13.5,4.75) {12\\9.2};		
 		\draw [thick] (-4,2) -- (18,2);
@@
 		%first 
-		\node[align=center, rounded corners, box, draw] at (7,.5) {9\\12};
+		\node[align=center, rounded corners, draw] at (7,.5) {9\\12};
 		% \node[align=center] at (8.5,.5) {1.5};
-		\node[align=center, rounded corners, box, draw, fill = green] at (14,.5) {11\\13};
+		\node[align=center, rounded corners, draw, fill = green] at (14,.5) {11\\13};
 		% \node[align=center] at (15.5,.5) {0.5};
@@
 		%right side row 2
-		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-2) {13\\9};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-2) {13\\9};
 		% \node[align=center] at (14,-2) {1.0};
 		\draw (14,-.5) -- (12.5,-1);
-		\node[align=center, rounded corners, box, draw] at (15.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw] at (15.5,-2) {12\\9.2};
 		% \node[align=center] at (17,-2) {1.8};
@@
 		\draw (7,-.5) -- (8.5,-1);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (5.5,-2) {13\\9};
+		\node[align=center, rounded corners, draw, fill = orange] at (5.5,-2) {13\\9};
 		\node[align=center] at (7,-2) {3.0};
-		\node[align=center, rounded corners, box, draw] at (8.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw] at (8.5,-2) {12\\9.2};
 		% \node[align=center] at (10,-2) {1.8};
@@
 		% left side row 3
-		\node[align=center, rounded corners, box, draw, fill = orange] at (8.5,-4.5) {11\\13};
+		\node[align=center, rounded corners, draw, fill = orange] at (8.5,-4.5) {11\\13};
 		\node[align=center] at (10,-4.5) {5.2};
@@
 		\draw (12.5,-3) -- (12.5,-3.5);
-		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-4.5) {9\\12};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-4.5) {9\\12};
 		% \node[align=center] at (14,-4.5) {1.6};
 		\draw (15.5,-3) -- (15.5,-3.5);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (15.5,-4.5) {9\\12};
+		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
 		\node[align=center] at (17,-4.5) {2.6};
@@
 		\draw (12.5,-5.5) -- (12.5,-6);
-		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-7) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-7) {12\\9.2};
 		\node[align=center] at (14,-7) {2.0};

### 2014-04-22 presentation/tilePlacement/step4.tex
added naive graphic and fixed errors

@@
 		%first 
-		\node[align=center, rounded corners, box, draw, fill = orange] at (7,.5) {9\\12};
+		\node[align=center, rounded corners, draw, fill = orange] at (7,.5) {9\\12};
 		\node[align=center] at (8.5,.5) {1.5};
-		\node[align=center, rounded corners, box, draw, fill = green] at (14,.5) {11\\13};
+		\node[align=center, rounded corners, draw, fill = green] at (14,.5) {11\\13};
 		\node[align=center] at (15.5,.5) {0.5};
@@
 		%right side row 2
-		\node[align=center, rounded corners, box, draw, fill = orange] at (12.5,-2) {13\\9};
+		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-2) {13\\9};
 		\node[align=center] at (14,-2) {1.0};
 		\draw (14,-.5) -- (12.5,-1);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (15.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-2) {12\\9.2};
 		\node[align=center] at (17,-2) {1.8};

### 2014-04-22 presentation/tilePlacement/step5.tex
added naive graphic and fixed errors

@@
 		%first 
-		\node[align=center, rounded corners, box, draw, fill = orange] at (7,.5) {9\\12};
+		\node[align=center, rounded corners, draw, fill = orange] at (7,.5) {9\\12};
 		\node[align=center] at (8.5,.5) {1.5};
-		\node[align=center, rounded corners, box, draw] at (14,.5) {11\\13};
+		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
 		%\node[align=center] at (15.5,.5) {0.5};
@@
 		%right side row 2
-		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-2) {13\\9};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-2) {13\\9};
 		\node[align=center] at (14,-2) {1.0};
 		\draw (14,-.5) -- (12.5,-1);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (15.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-2) {12\\9.2};
 		\node[align=center] at (17,-2) {1.8};
@@
 		\draw (12.5,-3) -- (12.5,-3.5);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (12.5,-4.5) {9\\12};
+		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-4.5) {9\\12};
 		\node[align=center] at (14,-4.5) {1.6};

### 2014-04-22 presentation/tilePlacement/step6.tex
added naive graphic and fixed errors

@@
 		%first 
-		\node[align=center, rounded corners, box, draw, fill = green] at (7,.5) {9\\12};
+		\node[align=center, rounded corners, draw, fill = green] at (7,.5) {9\\12};
 		\node[align=center] at (8.5,.5) {1.5};
-		\node[align=center, rounded corners, box, draw] at (14,.5) {11\\13};
+		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
 		%\node[align=center] at (15.5,.5) {0.5};
@@
 		%right side row 2
-		\node[align=center, rounded corners, box, draw] at (12.5,-2) {13\\9};
+		\node[align=center, rounded corners, draw] at (12.5,-2) {13\\9};
 		%\node[align=center] at (14,-2) {1.0};
 		\draw (14,-.5) -- (12.5,-1);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (15.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-2) {12\\9.2};
 		\node[align=center] at (17,-2) {1.8};
@@
 		\draw (7,-.5) -- (8.5,-1);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (5.5,-2) {13\\9};
+		\node[align=center, rounded corners, draw, fill = orange] at (5.5,-2) {13\\9};
 		\node[align=center] at (7,-2) {3.0};
-		\node[align=center, rounded corners, box, draw, fill = orange] at (8.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = orange] at (8.5,-2) {12\\9.2};
 		\node[align=center] at (10,-2) {1.8};

### 2014-04-24 presentation/tilePlacement/step8.tex

@@
 		%first 
-		\node[align=center, rounded corners, box, draw] at (7,.5) {9\\12};
+		\node[align=center, rounded corners, draw] at (7,.5) {9\\12};
 		% \node[align=center] at (8.5,.5) {1.5};
-		\node[align=center, rounded corners, box, draw] at (14,.5) {11\\13};
+		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
 		% \node[align=center] at (15.5,.5) {0.5};
@@
 		%right side row 2
-		\node[align=center, rounded corners, box, draw] at (12.5,-2) {13\\9};
+		\node[align=center, rounded corners, draw] at (12.5,-2) {13\\9};
 		% \node[align=center] at (14,-2) {1.0};
 		\draw (14,-.5) -- (12.5,-1);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (15.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-2) {12\\9.2};
 		\node[align=center] at (17,-2) {1.8};
@@
 		\draw (7,-.5) -- (8.5,-1);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (5.5,-2) {13\\9};
+		\node[align=center, rounded corners, draw, fill = orange] at (5.5,-2) {13\\9};
 		\node[align=center] at (7,-2) {3.0};
-		\node[align=center, rounded corners, box, draw, fill = green] at (8.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = green] at (8.5,-2) {12\\9.2};
 		\node[align=center] at (10,-2) {1.8};
@@
 		\draw (12.5,-3) -- (12.5,-3.5);
-		\node[align=center, rounded corners, box, draw] at (12.5,-4.5) {9\\12};
+		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
 		% \node[align=center] at (14,-4.5) {1.6};
@@
 		\draw (12.5,-5.5) -- (12.5,-6);
-		\node[align=center, rounded corners, box, draw, fill = orange] at (12.5,-7) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {12\\9.2};
 		\node[align=center] at (14,-7) {2.0};

### 2014-09-16 search_project/Node.py
first run at grouping i-1 tiles

@@ -37,19 +37,31 @@ class Node(object):
 		char_num = len(self.placed_tiles) 
 		for i in range(len(self.unplaced_tiles)):
 			if(self.unplaced_tiles[i].get_amino_type() == self.characteristic[char_num][2] or self.unplaced_tiles[i].get_amino_type()==0):
-				temp_ut = list(self.unplaced_tiles)
-				placed_tile = temp_ut.pop(i)
-				temp_pt = list(self.placed_tiles)
-				temp_pt.append(placed_tile)
-				if(self.placed_tiles):
-					temp_char_cost = placed_tile.get_error(self.characteristic[char_num])
-					temp_order_cost = self.placed_tiles[-1].compare_above(placed_tile)
-				else:
-					temp_char_cost = placed_tile.get_error(self.characteristic[char_num])
-					temp_order_cost = 0
-				c = temp_order_cost + temp_char_cost
-
-				new_nodes.append(Node(temp_ut, temp_pt, self.cost + c, self.characteristic,self.char_cost+temp_char_cost, self.order_cost+temp_order_cost))
-			
+				if(char_num>0):
+					temp_ut = list(self.unplaced_tiles)
+					placed_tile = temp_ut.pop(i)
+					temp_pt = list(self.placed_tiles)
+					temp_pt.append(placed_tile)
+					if(self.placed_tiles):
+						temp_char_cost = placed_tile.get_error(self.characteristic[char_num])
+						temp_order_cost = self.placed_tiles[-1].compare_above(placed_tile)
+					else:
+						temp_char_cost = placed_tile.get_error(self.characteristic[char_num])
+						temp_order_cost = 0
+					c = temp_order_cost + temp_char_cost
+					new_nodes.append(Node(temp_ut, temp_pt, self.cost + c, self.characteristic,self.char_cost+temp_char_cost, self.order_cost+temp_order_cost))
+				elif(self.unplaced_tiles[i].get_amino_type_before() == self.characteristic[char_num-1][2] or self.unplaced_tiles[i].get_amino_type_before()==0):
+					temp_ut = list(self.unplaced_tiles)
+					placed_tile = temp_ut.pop(i)
+					temp_pt = list(self.placed_tiles)
+					temp_pt.append(placed_tile)
+					if(self.placed_tiles):
+						temp_char_cost = placed_tile.get_error(self.characteristic[char_num])
+						temp_order_cost = self.placed_tiles[-1].compare_above(placed_tile)
[…]

### 2014-09-16 search_project/Tile.py

@@ -27,10 +27,30 @@ class Tile(object):
             self.amino_type = 6 #pro, val
         else:
             self.amino_type = 0 # no appropriate match found
+        if(self.c == -1.0 and 0<self.d and self.d<50.0):
+            self.amino_type_before = 1 #gly
+        elif(0.0<self.c and self.c<20.0 and self.d > 52 and self.d < 56):
+            self.amino_type_before = 2 #ala
+        elif(36.0<self.c and self.c < 45.0 and 50.0 < self.a):
+            self.amino_type_before = 3 #asn, asp, leu, cyso
+        elif(27.0<self.c and self.c < 35.0 and 54.0 < self.d and self.d <62.0):
+            self.amino_type_before = 4 # met, gln, lys, arg, his, glu, trp, cysr
+        elif(61.0<self.c and self.c < 74.0 and 59.0 < self.d and self.d <67.0):
+            self.amino_type_before = 5 # ser, thr
+        elif(30.0<self.c and self.c < 35.0 and 62.0 < self.d):
+            self.amino_type_before = 6 #pro, val
+        else:
+            self.amino_type_before = 0 # no appropriate match found
+
 
     #return amino acid type
     def get_amino_type(self):
         return self.amino_type
+
+    #return amino acid type for i-1
+    def get_amino_type_before(self):
+        return self.amino_type_before
+
     #returns a list of tile values
     def get_tile(self):
         return [self.a, self.b, self.c, self.d]

### 2014-09-16 presentation/tilePlacement/step7.tex

@@
 		\draw (12.5,-3) -- (12.5,-3.5);
-		\node[align=center, rounded corners, box, draw, fill = green] at (12.5,-4.5) {9\\12};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-4.5) {9\\12};
 		\node[align=center] at (14,-4.5) {1.6};

### 2014-09-16 search_project/Node.py
more work on i-1 values

@@ -37,7 +37,7 @@ class Node(object):
 		char_num = len(self.placed_tiles) 
 		for i in range(len(self.unplaced_tiles)):
 			if(self.unplaced_tiles[i].get_amino_type() == self.characteristic[char_num][2] or self.unplaced_tiles[i].get_amino_type()==0):
-				if(char_num>0):
+				if(char_num<1):
 					temp_ut = list(self.unplaced_tiles)
 					placed_tile = temp_ut.pop(i)
 					temp_pt = list(self.placed_tiles)

### 2014-09-16 search_project/Tile.py

@@ -13,6 +13,8 @@ class Tile(object):
         self.place_holder = place_holder
         self.char_weight = .1
         self.order_weight = 1
+
+        # Group I 
         if(self.b == -1.0 and 0<self.a and self.a<50.0):
             self.amino_type = 1 #gly
         elif(0.0<self.b and self.b<20.0 and self.a > 52 and self.a < 56):
@@ -27,17 +29,19 @@ class Tile(object):
             self.amino_type = 6 #pro, val
         else:
             self.amino_type = 0 # no appropriate match found
-        if(self.c == -1.0 and 0<self.d and self.d<50.0):
+
+        # Group I-1
+        if(self.d == -1.0 and 0<self.c and self.c<50.0):
             self.amino_type_before = 1 #gly
-        elif(0.0<self.c and self.c<20.0 and self.d > 52 and self.d < 56):
+        elif(0.0<self.d and self.d<20.0 and self.c > 52 and self.c < 56):
             self.amino_type_before = 2 #ala
-        elif(36.0<self.c and self.c < 45.0 and 50.0 < self.a):
+        elif(36.0<self.d and self.d < 45.0 and 50.0 < self.c):
             self.amino_type_before = 3 #asn, asp, leu, cyso
-        elif(27.0<self.c and self.c < 35.0 and 54.0 < self.d and self.d <62.0):
+        elif(27.0<self.d and self.d < 35.0 and 54.0 < self.c and self.c <62.0):
             self.amino_type_before = 4 # met, gln, lys, arg, his, glu, trp, cysr
-        elif(61.0<self.c and self.c < 74.0 and 59.0 < self.d and self.d <67.0):
+        elif(61.0<self.d and self.d < 74.0 and 59.0 < self.c and self.c <67.0):
             self.amino_type_before = 5 # ser, thr
-        elif(30.0<self.c and self.c < 35.0 and 62.0 < self.d):
+        elif(30.0<self.d and self.d < 35.0 and 62.0 < self.c):
             self.amino_type_before = 6 #pro, val
         else:
             self.amino_type_before = 0 # no appropriate match found

### 2014-09-16 search_project/Data_pars/pars.sh
pras edit

@@ -1,5 +1,5 @@
 END=61;
 for i in $(seq 1 $END); do
-	echo ../Data/Data_Fall_2014_$i.txt;
-	python pars.py ../Data/Data_Fall_2014.txt $i > ../Data/Data_Fall_2014_$i.txt; 
+	echo ../Data/Data$i.txt;
+	python pars.py ../Data/data50.txt $i > data$i.txt; 
 done

### 2014-09-16 search_project/test_code.py

@@ -185,8 +185,8 @@ class TestSequenceFunctions(unittest.TestCase):
     # def test_data40_txt(self):
     #     self.assertTrue(getOutput("data40.txt") == getExpectedOutput("data40.txt"))
 
-    # def test_data41_txt(self):
-    #     self.assertTrue(getOutput("data41.txt") == getExpectedOutput("data41.txt"))
+    def test_data41_txt(self):
+        self.assertTrue(getOutput("data41.txt") == getExpectedOutput("data41.txt"))
 
 suite = unittest.TestLoader().loadTestsFromTestCase(TestSequenceFunctions)
 unittest.TextTestRunner(verbosity=2).run(suite)

### 2014-09-17 search_project/convert_letters.py
Converts strings to a three letter characteristic.

@@ -1,0 +1,56 @@
+
+print"Copy string here:  "
+backbone = raw_input()
+#print backbone
+backbone.split()
+#print backbone
+characteristic = []
+for let in backbone:
+	if let == "A":
+		characteristic.append("Ala");
+	if let == "R":
+		characteristic.append("Arg");
+	if let == "N":
+		characteristic.append("Asn");
+	if let == "D":
+		characteristic.append("Asp");
+	if let == "B":
+		characteristic.append("Asx");
+	if let == "C":
+		characteristic.append("Cys");
+	if let == "Q":
+		characteristic.append("Gln");
+	if let == "E":
+		characteristic.append("Glu");
+	if let == "G":
+		characteristic.append("Gly");
+	if let == "H":
+		characteristic.append("His");
+	if let == "I":
+		characteristic.append("Ile");
+	if let == "L":
+		characteristic.append("Leu");
+	if let == "K":
+		characteristic.append("Lys");
+	if let == "M":
+		characteristic.append("Met");
+	if let == "F":
+		characteristic.append("Phe");
+	if let == "P":
+		characteristic.append("Pro");
+	if let == "S":
+		characteristic.append("Ser");
+	if let == "T":
+		characteristic.append("Thr");
+	if let == "W":
+		characteristic.append("Trp");
+	if let == "Y":
+		characteristic.append("Tyr");
+	if let == "V":
+		characteristic.append("Val");
+
+print "Your characteristic is:  "
+line = ""
+for item in characteristic:
+	line = line+item+" "
+print str(line)

### 2015-02-08 search_project/Node1.py
proline fix and Astar

@@ -1,0 +1,130 @@
+#!/usr/bin/python
+
+"""
+A node contains a state in the search tree
+It contains the list of placed and unplaced tiles 
+It also holds the characteristic protein sequence if we have one
+It also has the cost of the search state
+"""
+
+class Node(object):
+
+	""" 
+	Initializes a node
+	ut: list of unplaced tiles in this node
+	pt: list of placed tiles in this node
+	cost: current cost associated with this node 
+	characteristic: list containing the characteristic backbone protein chain
+	char_cost: cost from comparing with the characteristic
+	order_cost: cost from comparing tiles with the one before it
+	"""
+	def __init__(self, ut, pt, cost, characteristic, char_cost, order_cost):
+		self.unplaced_tiles = ut
+		self.placed_tiles = pt
+		self.cost = cost
+		self.characteristic = characteristic
+		self.char_cost = char_cost
+		self.order_cost = order_cost
+
+	"""
+	prints the node to the console
+	"""
+	def __str__(self):
+		for tile in self.placed_tiles:
+			print tile.get_tile()
+		return ""
+
+	"""
+	Creates children nodes of the current node
+	returns a list of child nodes
+	"""
+	def expand(self):
+		new_nodes = []
+		char_num = len(self.placed_tiles) # location in the protein sequence
+
+		# If this Node contains a characteristic protein sequence we will use it
+		if(self.characteristic):
+
+			# loop through all tiles that have not been placed
+			for i in range(len(self.unplaced_tiles)):
+
+				# check to see if current tile can be placed in this location
+				amino_type_list = self.unplaced_tiles[i].get_amino_type()
+				amino_Idx = self.characteristic[char_num][2]
+				if(amino_type_list[amino_Idx]==2.0):
+					temp_ut = list(self.unplaced_tiles) 
+					placed_tile = temp_ut.pop(i) 
+					temp_pt = list(self.placed_tiles) 
+					temp_pt.append(placed_tile)
+
+					# add child node to list of new_nodes
+					new_nodes.append(Node(temp_ut, temp_pt, self.cost, self.characteristic, self.char_cost, self.order_cost))
+
+				elif(amino_type_list[amino_Idx] > 0.004):
+
+					# copy unplaced and placed tile lists, remove tile from list and add it to the placed tile list
+					temp_ut = list(self.unplaced_tiles) 
+					placed_tile = temp_ut.pop(i) 
+					temp_pt = list(self.placed_tiles) 
[…]

### 2015-02-08 search_project/Node_aStar.py

@@ -1,0 +1,131 @@
+#!/usr/bin/python
+
+"""
+A node contains a state in the search tree
+It contains the list of placed and unplaced tiles 
+It also holds the characteristic protein sequence if we have one
+It also has the cost of the search state
+"""
+
+class Node(object):
+
+	""" 
+	Initializes a node
+	ut: list of unplaced tiles in this node
+	pt: list of placed tiles in this node
+	cost: current cost associated with this node 
+	characteristic: list containing the characteristic backbone protein chain
+	char_cost: cost from comparing with the characteristic
+	order_cost: cost from comparing tiles with the one before it
+	"""
+	def __init__(self, ut, pt, cost, characteristic, char_cost, order_cost, heuristic=0):
+		self.unplaced_tiles = ut
+		self.placed_tiles = pt
+		self.cost = cost
+		self.characteristic = characteristic
+		self.char_cost = char_cost
+		self.order_cost = order_cost
+		self.heuristic_cost = heuristic
+
+	"""
+	prints the node to the console
+	"""
+	def __str__(self):
+		for tile in self.placed_tiles:
+			print tile.get_tile()
+		return ""
+
+	"""
+	Creates children nodes of the current node
+	returns a list of child nodes
+	"""
+	def expand(self):
+		new_nodes = []
+		char_num = len(self.placed_tiles) # location in the protein sequence
+
+		# If this Node contains a characteristic protein sequence we will use it
+		if(self.characteristic):
+
+			# loop through all tiles that have not been placed
+			for i in range(len(self.unplaced_tiles)):
+
+				# check to see if current tile can be placed in this location
+				amino_type_list = self.unplaced_tiles[i].get_amino_type()
+				amino_Idx = self.characteristic[char_num][2]
+				if(amino_type_list[amino_Idx]==2.0):
+					temp_ut = list(self.unplaced_tiles) 
+					placed_tile = temp_ut.pop(i) 
+					temp_pt = list(self.placed_tiles) 
+					temp_pt.append(placed_tile)
+
+					# add child node to list of new_nodes
+					new_nodes.append(Node(temp_ut, temp_pt, self.cost, self.characteristic, self.char_cost, self.order_cost, heuristic=self.heuristic_cost))
+
+				elif(amino_type_list[amino_Idx] > 0.004):
+
+					# copy unplaced and placed tile lists, remove tile from list and add it to the placed tile list
[…]

### 2015-02-08 search_project/Scripts/get_data1.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+cd ..
+
+for i  in $(seq 61 62); 
+do 
+	echo | tee -a Scripts/aStar_profix_lmt_3sd.log
+	echo ================================== | tee -a Scripts/aStar_profix_lmt_3sd.log
+	echo Data/Data_Fall_2014_$i.txt | tee -a Scripts/aStar_profix_lmt_3sd.log
+	echo ================================== | tee -a Scripts/aStar_profix_lmt_3sd.log
+	python search_project1.py Data/Data_Fall_2014_$i.txt | tee -a Scripts/aStar_profix_lmt_3sd.log
+done

### 2015-02-08 search_project/Scripts/temp.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+
+cd ..
+echo | tee -a Scripts/profix_lmt_3sd.log
+echo ================================== | tee -a Scripts/profix_lmt_3sd.log
+echo Data/Data_Fall_2014_62.txt | tee -a Scripts/profix_lmt_3sd.log
+echo ================================== | tee -a Scripts/profix_lmt_3sd.log
+python search_project1.py Data/Data_Fall_2014_62.txt | tee -a Scripts/profix_lmt_3sd.log

### 2015-02-08 search_project/Tile1.py

@@ -1,0 +1,138 @@
+#!/usr/bin/python
+
+import math
+from weka.core.dataset import Instance
+from weka.classifiers import Classifier
+
+
+"""
+A Tile contains the NMR data for a single amino acid or a list of amino acids
+"""
+
+class Tile(object):
+
+    """
+    To generate a tile provide (a,b,c,d) or (tile_list)
+    a: carbon alpha value for residue i
+    b: carbon beta value for residue i
+    c: carbon alpha value for residue i-1
+    d: carbon beta value for residue i-1
+    tile_list: A list of tiles that have been grouped together
+    """
+    def __init__(self,a=0 ,b=0 ,c=0 ,d=0, model=None, tile_list=[], pro=False):
+        if (not tile_list): # not given a tile list
+            self.a = float(a)
+            self.b = float(b)
+            self.c = float(c)
+            self.d = float(d)
+            self.tile_list = []
+            self.char_weight = .1
+            self.order_weight = 1
+            self.tile_list_cost = 0
+            self.amino_type = self.calculate_amino_type(model,pro)
+        else: # create a tile form the tile_list
+            self.tile_list = tile_list
+            self.amino_type = 0
+            self.char_weight = .1
+            self.order_weight = 1
+            
+            #assigns a and b of the last tile to the a and b value of combined tile
+            self.a = float(tile_list[-1].a)
+            self.b = float(tile_list[-1].b)
+
+            #assigns c and d of the fist tile to the c and d value of the combined tiles
+            self.c = float(tile_list[0].c)
+            self.d = float(tile_list[0].d)
+
+            # calculate the cost of the tile
+            self.tile_list_cost = self.calculate_tile_list_cost()
+
+
+    """
+    Group tiles by expected amino acid type 
+    """
+    def calculate_amino_type(self, model, pro):
+        if pro:
+            return [0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 2.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0]
+        i = Instance.create_instance(values=[1.0, self.a, self.b])
+        if (self.a==-1 and self.b==-1 ):
[…]

### 2015-02-08 search_project/Tile_aStar.py

@@ -1,0 +1,139 @@
+#!/usr/bin/python
+
+import math
+from weka.core.dataset import Instance
+from weka.classifiers import Classifier
+
+
+"""
+A Tile contains the NMR data for a single amino acid or a list of amino acids
+"""
+
+class Tile(object):
+
+    """
+    To generate a tile provide (a,b,c,d) or (tile_list)
+    a: carbon alpha value for residue i
+    b: carbon beta value for residue i
+    c: carbon alpha value for residue i-1
+    d: carbon beta value for residue i-1
+    tile_list: A list of tiles that have been grouped together
+    """
+    def __init__(self,a=0 ,b=0 ,c=0 ,d=0, model=None, tile_list=[], pro=False, heuristic=0.0):
+        if (not tile_list): # not given a tile list
+            self.a = float(a)
+            self.b = float(b)
+            self.c = float(c)
+            self.d = float(d)
+            self.tile_list = []
+            self.char_weight = .1
+            self.order_weight = 1
+            self.tile_list_cost = 0
+            self.heuristic_cost = heuristic
+            self.amino_type = self.calculate_amino_type(model,pro)
+        else: # create a tile form the tile_list
+            self.tile_list = tile_list
+            self.amino_type = 0
+            self.char_weight = .1
+            self.order_weight = 1
+            
+            #assigns a and b of the last tile to the a and b value of combined tile
+            self.a = float(tile_list[-1].a)
+            self.b = float(tile_list[-1].b)
+
+            #assigns c and d of the fist tile to the c and d value of the combined tiles
+            self.c = float(tile_list[0].c)
+            self.d = float(tile_list[0].d)
+
+            # calculate the cost of the tile
+            self.tile_list_cost = self.calculate_tile_list_cost()
+
+
+    """
+    Group tiles by expected amino acid type 
+    """
+    def calculate_amino_type(self, model, pro):
+        if pro:
+            return [0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 2.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0]
+        i = Instance.create_instance(values=[1.0, self.a, self.b])
+        if (self.a==-1 and self.b==-1 ):
[…]

### 2015-02-08 search_project/search_project1.py

@@ -1,0 +1,32 @@
+"""
+Name: Joel Venzke, Katie Roth, Paxten Johnson, Rachel Davis, Leah Robison, John Emmons, Tim Urness, Adina Kilpatrick
+Date created: October 12th, 2013
+Description: This program automates the assignment of NMR data. 
+				The data is read in from a file and then the search will begin.
+				A uniform cost search is used if a 0 is given in the run command
+				A "puzzle building" search is completed if a 1 is given in the run command
+				
+				For further infromation on the project please see our paper:
+				http://www.micsymposium.org/mics2014/ProceedingsMICS_2014/mics2014_submission_35.pdf
+				or email joel.venzke@drake.edu
+
+				To run the code use the following command:
+				shell$ python search_project.py Path/To/Data/File.txt NumberOfSearchType
+"""
+
+
+import search_strategies2
+import time
+import sys
+
+# Error if not enough data is provided
+if len(sys.argv) < 2:
+	exit("NO INPUT DATA FILE OR MISSING SEARCH TYPE NUMBER\n\nPlease type: \nshell$ python search_project.py Path/To/Data/File.txt NumberOfSearchType\
+		\n\nSearch Type Numbers:\nUniform Cost: 0\nPuzzle Building: 1")
+
+# time and run search
+start = time.clock()
+search_strategies2.start_search(sys.argv[1],0)
+end = time.clock()
+
+print "Run Time:  " + str(end-start)

### 2015-02-08 search_project/search_project_aStar.py

@@ -1,0 +1,32 @@
+"""
+Name: Joel Venzke, Katie Roth, Paxten Johnson, Rachel Davis, Leah Robison, John Emmons, Tim Urness, Adina Kilpatrick
+Date created: October 12th, 2013
+Description: This program automates the assignment of NMR data. 
+				The data is read in from a file and then the search will begin.
+				A uniform cost search is used if a 0 is given in the run command
+				A "puzzle building" search is completed if a 1 is given in the run command
+				
+				For further infromation on the project please see our paper:
+				http://www.micsymposium.org/mics2014/ProceedingsMICS_2014/mics2014_submission_35.pdf
+				or email joel.venzke@drake.edu
+
+				To run the code use the following command:
+				shell$ python search_project.py Path/To/Data/File.txt NumberOfSearchType
+"""
+
+
+import search_strategies_aStar
+import time
+import sys
+
+# Error if not enough data is provided
+if len(sys.argv) < 2:
+	exit("NO INPUT DATA FILE OR MISSING SEARCH TYPE NUMBER\n\nPlease type: \nshell$ python search_project.py Path/To/Data/File.txt NumberOfSearchType\
+		\n\nSearch Type Numbers:\nUniform Cost: 0\nPuzzle Building: 1")
+
+# time and run search
+start = time.clock()
+search_strategies_aStar.start_search(sys.argv[1],0)
+end = time.clock()
+
+print "Run Time:  " + str(end-start)

### 2015-02-08 search_project/search_strategies1.py

@@ -1,0 +1,280 @@
+from Tile2 import Tile
+from Node2 import Node
+import sys
+import re
+import random
+from weka.core.converters import Loader
+from weka.classifiers import Classifier
+import weka.core.jvm as jvm
+import weka.core.serialization as serialization
+
+"""
+groups tiles together if there error is low enough
+takes in a list of assigned tiles
+returns a list of tiles and grouped tiles
+"""
+def find_matches(tiles):
+	outputNode = tiles
+	# lots of work needed =================================================================================
+	# lots of work needed =================================================================================
+	# lots of work needed =================================================================================
+	# lots of work needed =================================================================================
+	return outputNode
+
+
+"""
+Creates enough place holder tiles to do a full search
+takes in the tile set and characteristic lists
+returns tile list with place holder tiles
+"""
+def generate_placeholders(tile_set, characteristic, nmrClass):
+	pro_count = 0
+	for i in characteristic:
+		if (i[2] ==12):
+			pro_count +=1
+			tile_set.append(Tile(-1,-1,-1,-1,nmrClass,pro=True))
+			# print tile_set[-1].amino_type[12]
+	gap = len(characteristic) - len(tile_set) # number of place holder tiles needed
+	if gap > 0:
+		for n in range(gap):
+			# print "making"
+			tile_set.append(Tile(-1, -1, -1, -1, nmrClass)) # add place holder tiles to tile set
+	return tile_set
+
+
+"""
+Converts protein sequence strings into expected chemical shift values
+takes in a list of strings
+returns a list of lists that hold a carbon alpha and carbon beta value
+"""
+def letters_to_numbers(characteristic):
+	temp = []
+	new_characteristic = []
+	for ch in characteristic: # loop through the whole list
+		ch = ch.lower().strip() # deal with case problems
+		temp = []
+		# finds amino acid type and gets expected chemical shift data
+		# Values come from BRMB data. The exact values are the average
+		# Ca and Cb values as recorded on 01-22-2015
+		# Here is the link: http://www.bmrb.wisc.edu/ref_info/statsel.htm
[…]

### 2015-02-08 search_project/search_strategies_aStar.py

@@ -1,0 +1,302 @@
+from Tile_aStar import Tile
+from Node_aStar import Node
+import sys
+import re
+import random
+from weka.core.converters import Loader
+from weka.classifiers import Classifier
+import weka.core.jvm as jvm
+import weka.core.serialization as serialization
+import time
+
+"""
+calculates and stores heuristic values for 
+all tiles with data
+"""
+def calculate_heuristic(tile_set, characteristic):
+	temp = 0
+	greatest = 0
+	for tile in tile_set:
+		for char in characteristic:
+			temp = tile.get_error(char)
+			if (temp>greatest):
+				greatest = temp
+		tile.heuristic_cost = temp
+
+"""
+groups tiles together if there error is low enough
+takes in a list of assigned tiles
+returns a list of tiles and grouped tiles
+"""
+def find_matches(tiles):
+	outputNode = tiles
+	# lots of work needed =================================================================================
+	# lots of work needed =================================================================================
+	# lots of work needed =================================================================================
+	# lots of work needed =================================================================================
+	return outputNode
+
+
+"""
+Creates enough place holder tiles to do a full search
+takes in the tile set and characteristic lists
+returns tile list with place holder tiles
+"""
+def generate_placeholders(tile_set, characteristic, nmrClass):
+	pro_count = 0
+	for i in characteristic:
+		if (i[2] ==12):
+			pro_count +=1
+			tile_set.append(Tile(-1,-1,-1,-1,nmrClass,pro=True))
+			# print tile_set[-1].amino_type[12]
+	gap = len(characteristic) - len(tile_set) # number of place holder tiles needed
+	if gap > 0:
+		for n in range(gap):
+			# print "making"
+			tile_set.append(Tile(-1, -1, -1, -1, nmrClass, heuristic=1.9)) # add place holder tiles to tile set
+	return tile_set
+
+
+"""
+Converts protein sequence strings into expected chemical shift values
+takes in a list of strings
+returns a list of lists that hold a carbon alpha and carbon beta value
+"""
+def letters_to_numbers(characteristic):
+	temp = []
+	new_characteristic = []
[…]

### 2015-02-08 search_project/test_code.py

@@ -9,10 +9,10 @@ def getExpectedOutput(filename):
     return expected_output
 
 def getOutput(filename):
-    p = subprocess.Popen(["python", "search_project.py", "./Data/"+filename, "0"], stdout=subprocess.PIPE)
+    p = subprocess.Popen(["python", "search_project1.py", "./Data/"+filename, "0"], stdout=subprocess.PIPE)
     out = p.communicate()
     outputList = out[0].split("\n")
-    output = "\n".join(outputList[10 : len(outputList) - 5])
+    output = "\n".join(outputList[3 : len(outputList) - 5])
     return output
 
 class TestSequenceFunctions(unittest.TestCase):

### 2015-02-08 Papers_and_Presentations/presentation/tilePlacement/naive.tex
clean up the home directory of the repository

\documentclass[10pt, varwidth]{standalone}

%
% compile using: pdflatex -shell-escape reu_paper.tex
%

\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{shapes,arrows}

\usepackage{pgfplots}

\usepackage{caption}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{mdwlist}
\usepackage{mathtools}
\usepackage{url}
\pgfrealjobname{survey}

\date{}

\begin{document}
\beginpgfgraphicnamed{naive}
	\begin{tikzpicture} [scale=.5]

		% level 4 lines
		\draw [thick] (24,10) -- (6,8.5);
		\draw [thick] (24,10) -- (18,8.5);
		\draw [thick] (24,10) -- (30,8.5);
		\draw [thick] (24,10) -- (42,8.5);

		% level 3 lines
		\draw [thick] (6,6.5) -- (2,6);
		\draw [thick] (6,6.5) -- (6,6);
		\draw [thick] (6,6.5) -- (10,6);
		\draw [thick] (18,6.5) -- (14,6);
		\draw [thick] (18,6.5) -- (18,6);
		\draw [thick] (18,6.5) -- (22,6);
		\draw [thick] (30,6.5) -- (26,6);
		\draw [thick] (30,6.5) -- (30,6);
		\draw [thick] (30,6.5) -- (34,6);
		\draw [thick] (42,6.5) -- (38,6);
		\draw [thick] (42,6.5) -- (42,6);
		\draw [thick] (42,6.5) -- (46,6);

		% level 2 lines
		\draw [thick] (2,4) -- (1,3.5);
		\draw [thick] (2,4) -- (3,3.5);
		\draw [thick] (6,4) -- (5,3.5);
		\draw [thick] (6,4) -- (7,3.5);
		\draw [thick] (10,4) -- (9,3.5);
		\draw [thick] (10,4) -- (11,3.5);
		\draw [thick] (14,4) -- (13,3.5);
		\draw [thick] (14,4) -- (15,3.5);
		\draw [thick] (18,4) -- (17,3.5);
		\draw [thick] (18,4) -- (19,3.5);
		\draw [thick] (22,4) -- (21,3.5);
		\draw [thick] (22,4) -- (23,3.5);
		\draw [thick] (26,4) -- (25,3.5);
		\draw [thick] (26,4) -- (27,3.5);
		\draw [thick] (30,4) -- (29,3.5);
		\draw [thick] (30,4) -- (31,3.5);
		\draw [thick] (34,4) -- (33,3.5);
		\draw [thick] (34,4) -- (35,3.5);
		\draw [thick] (38,4) -- (37,3.5);
		\draw [thick] (38,4) -- (39,3.5);
		\draw [thick] (42,4) -- (41,3.5);
		\draw [thick] (42,4) -- (43,3.5);
		\draw [thick] (46,4) -- (45,3.5);
		\draw [thick] (46,4) -- (47,3.5);

		% level 1 lines
		\draw [thick] (1,1.5) -- (1,1);
		\draw [thick] (3,1.5) -- (3,1);
		\draw [thick] (5,1.5) -- (5,1);
		\draw [thick] (7,1.5) -- (7,1);
		\draw [thick] (9,1.5) -- (9,1);
		\draw [thick] (11,1.5) -- (11,1);
		\draw [thick] (13,1.5) -- (13,1);
		\draw [thick] (15,1.5) -- (15,1);
		\draw [thick] (17,1.5) -- (17,1);
		\draw [thick] (19,1.5) -- (19,1);
		\draw [thick] (21,1.5) -- (21,1);
		\draw [thick] (23,1.5) -- (23,1);
		\draw [thick] (25,1.5) -- (25,1);
		\draw [thick] (27,1.5) -- (27,1);
		\draw [thick] (29,1.5) -- (29,1);
		\draw [thick] (31,1.5) -- (31,1);
		\draw [thick] (33,1.5) -- (33,1);
		\draw [thick] (35,1.5) -- (35,1);
		\draw [thick] (37,1.5) -- (37,1);
		\draw [thick] (39,1.5) -- (39,1);
		\draw [thick] (41,1.5) -- (41,1);
		\draw [thick] (43,1.5) -- (43,1);
		\draw [thick] (45,1.5) -- (45,1);
		\draw [thick] (47,1.5) -- (47,1);

		% level 4
		\node[align=center, rounded corners, draw, fill = white] at (6,7.5) {9\\12};
		\node[align=center, rounded corners, draw, fill = green] at (18,7.5) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (30,7.5) {13\\9};
		\node[align=center, rounded corners, draw, fill = red] at (42,7.5) {12\\9.2};

		% level 3
		\node[align=center, rounded corners, draw, fill = red] at (2,5) {11\\13};
		\node[align=center, rounded corners, draw, fill = white] at (6,5) {13\\9};
		\node[align=center, rounded corners, draw, fill = white] at (10,5) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (14,5) {9\\12};
		\node[align=center, rounded corners, draw, fill = green] at (18,5) {13\\9};
		\node[align=center, rounded corners, draw, fill = white] at (22,5) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (26,5) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (30,5) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (34,5) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (38,5) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (42,5) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (46,5) {13\\9};

		% level 2
		\node[align=center, rounded corners, draw, fill = red] at (1,2.5) {13\\9};
		\node[align=center, rounded corners, draw, fill = red] at (3,2.5) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (5,2.5) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (7,2.5) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = white] at (9,2.5) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (11,2.5) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (13,2.5) {13\\9};
		\node[align=center, rounded corners, draw, fill = red] at (15,2.5) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = green] at (17,2.5) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (19,2.5) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = white] at (21,2.5) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (23,2.5) {13\\9};
		\node[align=center, rounded corners, draw, fill = red] at (25,2.5) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (27,2.5) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (29,2.5) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (31,2.5) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (33,2.5) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (35,2.5) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (37,2.5) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (39,2.5) {13\\9};
		\node[align=center, rounded corners, draw, fill = red] at (41,2.5) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (43,2.5) {13\\9};
		\node[align=center, rounded corners, draw, fill = red] at (45,2.5) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (47,2.5) {11\\13};

		% bottom row (level 1)
		\node[align=center, rounded corners, draw, fill = red] at (1,0) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (3,0) {13\\9};
		\node[align=center, rounded corners, draw, fill = red] at (5,0) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (7,0) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (9,0) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (11,0) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (13,0) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (15,0) {13\\9};
		\node[align=center, rounded corners, draw, fill = green] at (17,0) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (19,0) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (21,0) {13\\9};
		\node[align=center, rounded corners, draw, fill = red] at (23,0) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (25,0) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (27,0) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (29,0) {12\\9.2};
		\node[align=center, rounded corners, draw, fill = red] at (31,0) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (33,0) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (35,0) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (37,0) {13\\9};
		\node[align=center, rounded corners, draw, fill = red] at (39,0) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (41,0) {13\\9};
		\node[align=center, rounded corners, draw, fill = red] at (43,0) {9\\12};
		\node[align=center, rounded corners, draw, fill = red] at (45,0) {11\\13};
		\node[align=center, rounded corners, draw, fill = red] at (47,0) {9\\12};
		\node at (47.75,0) {};

	\end{tikzpicture}
\endpgfgraphicnamed
\end{document}

### 2015-02-08 Papers_and_Presentations/presentation/tilePlacement/step9.tex
clean up the home directory of the repository

--- 2014-04-24 presentation/tilePlacement/step8.tex
@@
 		\draw (14,-.5) -- (12.5,-1);
-		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = green] at (15.5,-2) {12\\9.2};
 		\node[align=center] at (17,-2) {1.8};
@@
 		\node[align=center] at (7,-2) {3.0};
-		\node[align=center, rounded corners, draw, fill = green] at (8.5,-2) {12\\9.2};
-		\node[align=center] at (10,-2) {1.8};
+		\node[align=center, rounded corners, draw] at (8.5,-2) {12\\9.2};
+		% \node[align=center] at (10,-2) {1.8};
 
@@
 		% \node[align=center] at (14,-4.5) {1.6};
+		\draw (15.5,-3) -- (15.5,-3.5);
+		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
+		\node[align=center] at (17,-4.5) {2.6};
 

### 2015-02-08 Venzke_Main.py

@@ -1,7 +1,0 @@
-from Venzke_Tile import Tile
-
-
-t = Tile(1,25,1,12)
-t1 = Tile(2,1,1,9)
-print t.compare_below(t1)
-print t1.compare_below(t)

### 2015-02-08 Venzke_Tile.py

@@ -1,27 +1,0 @@
-import math
-
-class Tile(object):
-    def __init__(self,a,b,c,d):
-        self.a = a
-        self.b = b
-        self.c = c
-        self.d = d
-    def set_a(self,i):
-        self.a = i
-    def set_b(self,i):
-        self.b = i
-    def set_c(self, i):
-        self.c = i
-    def set_d(self, i):
-        self.d = i
-    def get_a(self):
-        return self.a
-    def get_b(self):
-        return self.b
-    def get_c(self):
-        return self.c
-    def get_d(self):
-        return self.d
-    def compare_below(self, t):
-        self.compare = math.fabs((self.c+self.d)-(t.get_a()+t.get_b()))
-        return self.compare

### 2015-02-08 cuda/int_tree_builder_test.cpp

@@ -1,199 +1,0 @@
-#include <iostream>
-#include <iterator>
-#include <list>
-using namespace std;
-
-// calculates (n!)/(d!)
-int fact_over_fact(int numerator, int denominator) {
-	int total = 1;
-
-	// multiply all numbers in the set [n, n-1, ... , d]
-	while (numerator > denominator) {
-		total *= numerator;
-		numerator--;
-	}
-	return total;
-}
-
-// returns start of the next level down one
-int start_level_value(int numberOfTiles, int currentLevel){
-	int total = 0;
-
-	// sum the number of tiles on each level until you get to the current level
-	for (int j = 1; j<=currentLevel; j++) {
-		total += fact_over_fact(numberOfTiles, (numberOfTiles-j));
-	}
-	return total;
-}
-
-// returns what level of the tree the value occurs on
-int generate_level(int numberOfTiles, int currentValue) {
-	int currentLevel = numberOfTiles;
-
-	// loop until the value is no longer less than the start of the level
-	while (currentValue < start_level_value(numberOfTiles, currentLevel)) {
-		currentLevel--;
-	}
-	return currentLevel;
-}
-
-// calculates width of a "packet" on a given level of a tree
-int get_width(int numberOfTiles, int currentLevel) {
-	return numberOfTiles-currentLevel;
-}
-
-// returns the location of the parent
-// start_level_value(numberOfTiles, currentLevel-1) gives first value in the level above the current
-// currentValue-start_level_value(numberOfTiles, currentLevel) gives number in the current level
-// get_width(numberOfTiles, currentLevel) gives the number of tiles placed under each tile above (number of tiles in a "packet")
-// (currentValue-start_level_value(numberOfTiles, currentLevel))/(get_width(numberOfTiles, currentLevel)) give which "packet" the tile is in on the current level
-int up_one_level(int numberOfTiles, int currentLevel, int currentValue) {
-	return start_level_value(numberOfTiles, currentLevel-1) + (currentValue-start_level_value(numberOfTiles, currentLevel))/(get_width(numberOfTiles, currentLevel));
-}
-
-// see overloaded function
-int up_one_level(int numberOfTiles, int currentValue) {
-	int currentLevel = generate_level(numberOfTiles, currentValue);
[…]

### 2015-02-08 cuda/nmr_data.cu

@@ -1,10 +1,0 @@
-
-
-struct nmrData // old tile
-{
-	float cAlpha1; // c alpha for i
-	float cBeta1; // c beta for i
-	float cAlpha2; // c alpha for i -1
-	float cBeta2; // c beta for i - 1
-	int group;
-};

### 2015-02-08 cuda/node.cu

@@ -1,191 +1,0 @@
-#include <iostream>
-#include <iterator>
-#include <list>
-using namespace std;
-
-struct node
-{
-	int value;
-	float cost;
-};
-
-// calculates (n!)/(d!)
-__host__ __device__ int fact_over_fact(int numerator, int denominator) {
-	int total = 1;
-
-	// multiply all numbers in the set [n, n-1, ... , d]
-	while (numerator > denominator) {
-		total *= numerator;
-		numerator--;
-	}
-	return total;
-}
-
-// returns start of the next level down one
-__host__ __device__ int start_level_value(int numberOfTiles, int currentLevel){
-	int total = 0;
-
-	// sum the number of tiles on each level until you get to the current level
-	for (int j = 1; j<=currentLevel; j++) {
-		total += fact_over_fact(numberOfTiles, (numberOfTiles-j));
-	}
-	return total;
-}
-
-// returns what level of the tree the value occurs on
-__host__ __device__ int generate_level(int numberOfTiles, int currentValue) {
-	int currentLevel = numberOfTiles;
-
-	// loop until the value is no longer less than the start of the level
-	while (currentValue < start_level_value(numberOfTiles, currentLevel)) {
-		currentLevel--;
-	}
-	return currentLevel;
-}
-
-// calculates width of a "packet" on a given level of a tree
-__host__ __device__ int get_width(int numberOfTiles, int currentLevel) {
-	return numberOfTiles-currentLevel;
-}
-
-// returns the location of the parent
-// start_level_value(numberOfTiles, currentLevel-1) gives first value in the level above the current
-// currentValue-start_level_value(numberOfTiles, currentLevel) gives number in the current level
-// get_width(numberOfTiles, currentLevel) gives the number of tiles placed under each tile above (number of tiles in a "packet")
-// (currentValue-start_level_value(numberOfTiles, currentLevel))/(get_width(numberOfTiles, currentLevel)) give which "packet" the tile is in on the current level
-__host__ __device__ int up_one_level(int numberOfTiles, int currentLevel, int currentValue) {
-	return start_level_value(numberOfTiles, currentLevel-1) + (currentValue-start_level_value(numberOfTiles, currentLevel))/(get_width(numberOfTiles, currentLevel));
-}
-
-// see overloaded function
-__host__ __device__ int up_one_level(int numberOfTiles, int currentValue) {
[…]

### 2015-02-08 cuda/search_project.cu

@@ -1,14 +1,0 @@
-#include <iostream>
-#include <string>
-#include "search_strategies.cu"
-using namespace std;
-
-int main(int argc, char const *argv[])
-{
-	// TODO make comand line version
-	string file;
-	cout << "Enter a file: ";
-	cin >> file;
-	start_search(file);
-	return 0;
-}

### 2015-02-08 cuda/search_strategies.cu

@@ -1,59 +1,0 @@
-#include <iostream>
-#include <string>
-#include <list>
-#include "node.cu"
-#include "nmr_data.cu"
-using namespace std;
-
-struct protein
-{
-	float cAlpha1; // c alpha for i
-	float cBeta1; // c beta for i
-	int group;
-};
-
-
-// take in abbreviation, generates chemical shift data
-protein letters_to_numbers(char acid[4]){
-
-	// TODO: Create data base file for values
-	// TODO: Make it easer to update 
-	// TODO: python script for runtime?
-	switch (acid) {
-		case ala: 
-	}
-}
-
-// read in all data from file
-void read_In_File(string &fileName, protein &p, nmrData &n) {
-	
-	// float value = atof(myString.c_str());
-}
-
-
-void start_search(string fileName){
-	// Initialize variables
-
-	// Read in file, Store NRM Data and protein chain in array
-
-	// Generate root node
-
-	// Create frontier linked list
-
-	// Loop till solution is found
-	// while (keepRunning) {
-		// Find best node to expand
-
-		// Remove best node from list
-
-		// Check state of node
-
-		// Expand Node
-
-		// Check if the solution has been found
-	// }
-
-	// Print results
-
-	// TODO: save results to output file
-}

### 2015-03-05 Papers_and_Presentations/paper_spring_2015/paper.tex

\documentclass{article}

\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{caption}
\usepackage{chngpage}
\usepackage{achemso}
\usepackage[affil-it]{authblk}

% put in paragraph spacing
\setlength{\parskip}{0.2cm}

\title{\textbf{Utilizing Machine Learning to Accelerate Automated Assignment of Backbone NMR Data}}

\author{Joel Venzke, David Mascharka, Paxten Johnson, Rachel Davis, Katie Roth, Leah Robison, Adina Kilpatrick and Timothy Urness*}
\affil{Department of Mathematics and Computer Science and the Department of Physics and Astromony,\\Drake University, Des Moines, Iowa\\\vspace{0.5cm}*Joel Venzke: joel.venzke@drake.edu\\Timothy Urness: timothy.urness@drake.edu}

\begin{document}

\maketitle

\begin{abstract}
Nuclear magnetic resonance (NMR) spectroscopy is a powerful method for studying the three-dimensional structure of molecules, including proteins. These methods provide useful data for the sequencing of amino acids into primary protein structures. Unfortunately, current manual techniques for analyzing these NMR datasets can take months to assign and are highly susceptible to error. Many programs have been developed to sequence protein backbone structures, with various strengths and weaknesses. The algorithm detailed in this paper works to overcome the obstacles others have met by utilizing machine learning to predict amino acid type, thereby increasing assignment speed. The program also generates place-holders to accommodate missing data and recurring amino acids with problematic chemical characteristics, namely proline. This approach is able to speed up the process of assignment by almost three orders of magnitude while maintaining high accuracy when compared to a previously assigned set.
\end{abstract}

\noindent\textbf{KEYWORDS}\\
Protein Sequencing, Machine Learning, NMR, Artificial Intelligence, Proteins, Bioinformatics

\noindent \textbf{INTRODUCTION}\\
The analysis of Nuclear Magnetic Resonance (NMR) data, in particular the sequence-specific assignment of backbone and side-chain protein resonances, is an error-prone and time-consuming step during protein structure determination by NMR spectroscopy \cite{aria}. NMR spectroscopy is a powerful method for obtaining atomic-resolution three-dimensional protein structures, as well as assessing changes in protein conformations or motions due to mutations or interactions with ligands or other biomolecules. Determining a protein’s structure is essential for understanding its function and alterations in function, which often lead to disease. This paper describes a computational algorithm that utilizes machine learning in the process of automating the assignment of backbone protein NMR resonances.
\\\\
\noindent \textbf{BACKGROUND}\\
NMR spectroscopy experiments generate information on several variables that can be used in the determination of protein structures. In particular, essential information is provided by the chemical shifts determined by NMR-active nuclei present in proteins, including hydrogen and isotopes of carbon and nitrogen. The chemical shift is a quantifier for the deviation in the resonant frequency of a nucleus from its value in a structure-free environment, and therefore provides information on the local conformation. Measuring the chemical shifts of all or most of the nuclei in a biomolecule is the first step in determining its structure by NMR spectroscopy. An important set of chemical shifts in a protein are those corresponding to the nuclei in the backbone of the protein polypeptide chain, including the amide nitrogen (N), attached hydrogen (H), and the alpha and beta carbons ($C_\alpha$ and $C_\beta$) of each residue. The chemical shift values are measured using various three-dimensional NMR experiments, and then matched to the individual residues in the protein in a process called sequential assignment.

Triple resonance experiments are the method of choice for proteins and other large biomolecules, because they can greatly decrease the amount of spectral overlap in data. Typical experiments for the assignment of backbone resonances include HNCA, HN(CO)CA, HNCACB, and CBCA(CO)NH or HN(CO)CACB \cite{mars}. These experiments transfer magnetization over the protein polypeptide chain, and thus connect different spin systems through covalent bonds. A spin system essentially contains all resonances belonging to a particular amino acid. The order of elements in experiment names indicates the order in which magnetization is passed down the line of nuclei, resonances in parentheses being used only for transfer to the next nucleus. All these experiments produce spectra with common H-N resonance correlations, and provide connectivities between neighboring residues. For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_\alpha$ and $C_\beta$ nuclei of each residue in the protein chain (residue $i$) , as well as the immediately preceding residue (residue $i-1$). In this experiment, resonances corresponding to residue $i$ can usually be distinguished from the $i-1$  values due to their higher intensity. However, ambiguities can arise if the intensities are comparable or if chemical shift values overlap. Such uncertainty happens frequently and can be resolved by using additional experiments. For example, an experiment CBCA(CO)NH yields the chemical shifts of the preceding residue only, unambiguously identifying $i$ and $i-1$  values. Using all inter-residue connectivities, a chain of correlations through the protein backbone chemical shifts can be established. Sequentially-linked chemical shift values reflect the ordered linear arrangement of individual residues in the protein sequence. The pattern is then matched to the protein sequence through certain residues with characteristic $C_\alpha$ and $C_\beta$ chemical shift ranges that uniquely identify them. Thus, each measured chemical shift is assigned to a protein residue and can be used to infer structural information about the biomolecule.
\\\\
\noindent \textbf{SEQUENTIAL ASSIGNMENT STRATEGIES}\\
The sequential assignment of backbone chemical shifts can be done manually or in an automated fashion. Both approaches follow similar strategies. The process starts by identifying the chemical shifts of $i$ and $i-1$  residues from a set of three-dimensional NMR experiments. In the early days of NMR spectroscopy, these chemical shifts were measured using a ruler \cite{guntert}. Nowadays, many computer programs, such as NMRPipe \cite{nmrpipe} and SPARKY \cite{zimmerman}, can be used to process, analyze and visualize NMR data. After grouping chemical shifts into spin systems, sequential spin systems are linked into increasingly larger segments by matching $i-1$  and $i$ values. In parallel, the spin systems are classified into possible residue types, using a set of established chemical shift values for each of the 20 common amino acids found in proteins. For example, alanines have $C_\alpha$ and $C_\beta$ chemical shifts ranging from approximately 50 to 5 ppm (parts per million), and 17 to 25 ppm, respectively; glycines have unique $C_\alpha$ values in the 45 ppm region; and threonines have distinctive $C_\beta$ values in the 68-73 ppm range \cite{biomagresbank}. Using the residue type information, the linked segments from the resonance sequential walk are iteratively mapped onto the protein primary sequence.

When performed manually, the assignment process is time-consuming and prone to errors. If chemical shifts values overlap, multiple matches between $i$ and $i-1$  values are possible. The classification of spin systems into amino acid types also has a high potential for error, as the spin systems can look identical or very similar even for very different amino acids. In recent years, advances in computer technology, accompanied by the increased use of NMR spectroscopy in drug design and structural genomics initiatives, have created a push for the automation of various steps in the NMR structure determination process \cite{moseley}. These automated methods decrease the time needed to complete the assignment, and attempt to minimize the risk of human error and subjectivity. A wide variety of algorithms and software packages for the assignment of backbone chemical shifts exist. Amongst a few of the most well known are GARANT \cite{guntert}, AutoAssign \cite{zimmerman} and MARS \cite{mars}.

The GARANT program has three key elements \cite{garant}. It starts with matching measured chemical shift values to values expected from the protein sequence. It then evaluates the correctness of  these matches using a scoring function, and optimizes the score using an evolutionary algorithm in conjunction with a local optimization routine \cite{guntert}. This optimization is similar to simulated annealing which makes repeated selections until the optimal solution is reached (8). AutoAssign uses a combination of artificial intelligence techniques and statistical methods to obtain the assignment \cite{james} . This program utilizes four basic steps, generally following the overall assignment strategy described above, but providing customized and novel solutions for each step. It first ranks and sorts spin systems. Secondly, it creates lists of possible amino acid types using Bayesian statistical methods. In step 3, AutoAssign links sequential spin systems into fragments, starting from spin systems that have a unique one-to-one match. Lastly, the fragments are mapped onto the protein sequence. Steps three and four are interleaved and run iteratively, such that sequential connectivities are established in parallel with  the identification of amino acid types. The software MARS optimizes the search by simultaneously assessing the local and global quality of the assignment \cite{mars}. This program breaks the assignment into segments, linking and mapping fragments consisting of up to five residues, and using them as units in the search. The most accurate model is selected in combination with protein secondary structure prediction. The reliability of fragment mapping is tested by performing multiple runs with chemical shifts modified by the addition of artificial noise.

These and other programs have paved the way for the automation of protein backbone assignments and made significant advances toward complete automation of protein structure determination by NMR spectroscopy. However, several issues remain. Some strategies may abandon a promising assignment too early if it has a higher error than other assignments, and thus the optimal solution will not be selected in the end \cite{mars}. Occasionally, a local minimum can throw off the optimization process \cite{mars}. Further issues arise when assigning larger protein chains. Some programs need days to finish the assignment in these cases; even then, the calculations can still have very high errors.

Our algorithm utilizes elements from these existing programs, but employs novel concepts from machine learning to accelerate the assignment process.
\\\\
\noindent\textbf{Machine Learning}\\
Machine learning provides algorithms that learn from attributes in the input data to increase performance. Supervised learning, a field of machine learning, builds a model based on numerous data elements and their respective labels. The result is a mathematical model that predicts a label given a set of input attributes. By discovering patterns and trends in the data, machine learning algorithms provide excellent solutions for building models to generalize from large amounts of collected data with potentially many attributes, a task that is often difficult or impossible by other means.

Machine learning offers a natural solution to the problem of determining amino acid type from NMR chemical shifts values. The overlap between the normal range of $C_\alpha$ and $C_\beta$ values between many amino acids makes it difficult to infer the type of residue based solely on chemical shift information. Machine learning algorithms offer a unique approach to this problem and achieve excellent accuracy.

There are several supervised machine learning algorithms that can be applied to improve automated assignment strategies. The J4.8 algorithm \cite{j48_algorithm} builds a decision tree model. This means that the data is split based on a comparison to an attribute of the data, with a branch for each possible outcome of the test. At the end of the tree, the leaf, is the predicted label. In our case this is the amino acid type. To classify a new value, a datapoint begins at the root of the tree and moves through until a leaf is encountered. The encountered leaf is the predicted value for that datapoint. To construct the tree, the attribute test used at each branch is the one that partitions the set in the most useful manner.

The Logistic Model Tree, or LMT \cite{lmt_algorithm}, is another tree-based algorithm. In contrast to the J4.8 algorithm, LMT constructs a tree with logistic regression functions at each branch rather than an attribute test. Logistic regression attempts to model class probabilities with linear functions (Hall). The weights used for each function can be learned to split each class in a way somewhat analogous to the split in J4.8 described above.

The Decision Table algorithm \cite{decisiontable_algorithm} is comprised of a set of features and a set of labeled data. To classify a new datapoint, the set of labeled data is searched for a match with the new point, considering only the features in the feature set. If no matches are found, the majority class of the labeled data is used. Otherwise, the majority class of the matches is used.
\\\\
\noindent\textbf {Methods}\\
Our goal is to create an automated program for the assignment of protein backbone chemical shifts that could deliver quality results in a small amount of time without the use of a supercomputer. Our program implements group sorting, machine learning, filtered amino acid selection, and careful cost calculation. The algorithm completes resonance assignment in six steps: (1) the NMR chemical shifts and the protein sequence are used as input data that fills data structures; (2) the protein sequence is processed and empty data structures are initialized for missing data; (3) the machine learning model assigns possible amino acid types to each spin system; (4) filtering is applied to locate chemical shift data that corresponds to residue 1 in the protein sequence; (5) the search continues with the best assignments until all chemical shift data is assigned; (6) the best solution is recorded and the process is terminated.

Before the algorithm begins the assignment process, machine learning is used to build a model for predicting amino acid type. After the model is trained, the assignment process consisting of the pre-processing steps (steps 1 to 3) and the search (steps 4 to 6) begins. Pre-processing is where our research has made significant advances in order to decrease assignment time by predicting amino acid types. This allows the data to be filtered, significantly reducing the branching factor. The algorithm is then able to intelligently search the remaining possibilities for the best assignment. 
\\\\
\noindent\textit{Machine Learning Data Collection}\\
The training dataset for the machine learning algorithm was obtained from BMRB. We initially identified 9,736 datasets containing chemical shifts for the $C_\alpha$ and $C_\beta$ resonances of 689,977 residues. However, a preprocessing step was necessary in order to remove extreme values for each amino acid and improve both accuracy and generalization. Removing outliers prevents the algorithms from fitting extraneous data, improving future performance. By looking at statistics available on the BMRB site, we excluded chemical shift values outside three standard deviations of the mean for each amino acid type. This gave us 681,363 pairs of $C_\alpha$ and $C_\beta$ values to use for training.
\\\\
\noindent\textit{Pre-processing}\\
Step 1 consists of reading the chemical shift values and the protein amino acid sequence from an input file. We use the $C_\alpha$ and $C_\beta$ values for residues $i$ and $i-1$  to create an object we will refer to as a tile. A tile holds information corresponding to a single residue in the protein sequence to be assigned. In step 3, amino acid types will be assigned to each tile.

Step 2 of the algorithm converts the protein sequence from the abbreviations into $C_\alpha$ and $C_\beta$ chemical shift values, using statistics provided by the Biological Magnetic Resonance Bank \cite{biomagresbank}, a database of NMR chemical shifts hosted by the University of Wisconsin at Madison. These statistics provide average chemical shift values for each of the twenty common amino acids found in proteins, using 4944897 chemical shifts published in BMRB as of February 2, 2015. For example, we assign alanine a $C_\alpha$ chemical shift of 53.19 ppm (parts-per-million) and a $C_\beta$ chemical shift of 18.96 ppm. Then the protein sequence is analyzed. The algorithm looks for prolines in the protein sequence. Since prolines do not generate chemical shift data from these experiments, special tiles are created to handle this case. Identifiers in the proline tiles ensure that the tile is placed only when the corresponding residue in the protein sequence is a proline. This identifier limits the number of possibilities where the tile can be assigned. The length of the protein sequence is then compared to the total number of tiles created thus far. If fewer tiles exist than the overall number of residues, blank tiles are created to fill the difference. Blank tiles can fit in any location in the assignment. Large amounts of missing data will deteriorate the algorithm’s performance.

Step 3 assigns possible amino acid types to each tile.The $C_\alpha$ and $C_\beta$ values for residue $i$ in each tile are processed by our machine learning model, producing a list of probabilities that a tile represents each amino acid. The probabilities correspond to confidence levels used for filtering during the assignment process.

Preprocessing the dataset takes a minimal amount of time (less than a second on a standard laptop) and drastically reduces the time required to assign dataset without affecting accuracy. The search for the optimal assignment then begins. 
\\\\
\noindent\textit{The Search}\\
The algorithm begins an intelligent search through filtered combinations of all possible chemical shifts. The search begins by placing the first tile, which is selected based on a filtering process. Only titles that correspond to the first amino acid based on a confidence level threshold (0.4\% match or better) are placed at residue one.

At this point, the cost of assignment is generated. The cost of placing a tile consists of two parts: (1) the difference between the tile’s residue $i-1$  values and the previous tile’s residue $i$ values and (2) the difference between the residue $i$ values and the values predicted from the protein sequence. In the case of blank and proline tiles, a fixed cost is added in place of the above calculation. Since initially only one tile is placed, the cost is based solely on a comparison to the protein sequence, and the search moves on to step 5.

In step 5, the algorithm selects the assignment with the lowest cost to continue the search process. If the assignment is a solution, the algorithm moves on to step 6.  A solution is reached when all tiles have been placed in an assignment. If the assignment is not a solution, the amino acid type of the next residue in the protein sequence is retrieved. Any unplaced tile that corresponds to that amino acid type with a confidence level above the threshold is placed at the next location in the sequence. In the special case that the next amino acid type is proline, only the special proline tiles are considered for placement. The cost is then adjusted to include the newly placed tile. Step 5 is repeated until a solution has been reached.

In the final step the search records the solution. The solution assignment is formatted for easy reading and output along with the algorithm’s performance. Then the algorithm terminates. 
\\\\
\noindent\textbf {Results}\\
The chemical shift dataset used in this study consisted of $C_\alpha$ and $C_\beta$ values for the 59-residue (our data set is 62 long) long C-terminal domain of the Tfg1 subunit of the yeast transcription factor TFIIF. The chemical shifts were previously obtained by Kilpatrick et al. from HNCACB and CBCA(CO)NH experiments, and manually assigned to 99\% completeness. The previously assigned data was cut into sub-sections, randomized, and used for algorithmic analysis.

The results of assigning this dataset with different filtering methods are shown in Figure 1. For sequences of up to 62 residues a smooth trend for all filtering methods tested was seen when graphing the generated nodes (or different assignments) against the sequence lengths. Interestingly, a comparison of the methods indicates that our filtering process results in a significant decrease in number of generated nodes compared to an unfiltered generic search algorithm, as seen in Figure 1. Since the most time-consuming part of the search is node generation, there is a direct correlation between assignment time and number of nodes generated. The graph indicates that the LMT algorithm has the best performance, outperforming the method with no filter by almost two orders of magnitude, without loss of assignment accuracy. This not only accelerates assignment, but also allows for larger datasets to be assigned.

% PUT IN FIGURE 1 HERE *******************

Figure 2 shows the impact of proline identification on our algorithm’s performance. The same unfiltered and LMT data from Figure 1 is plotted for comparison. The large jump in assignment time from 32 to 33 residues shows the performance impact of missing data. In the sequence of the studied protein, residue 33 is a proline, which lacks NH (check denotation previously in paper) spin systems. As a consequence, HNCACB and CBCA(CO)NH experiments do not provide $C_\alpha$ and $C_\beta$ chemical shifts for this residue. If the algorithm identifies and deals with prolines as a special case, only one more node is generated for the 33-residue case. However, if the proline is not dealt with separately, the algorithm’s performance is significantly impacted. Without proline checking, the proline tile is placed in every position in the assignment. The result is a major increase in the branching factor that leads to the jump observed in Figure 2. With proline checking, prolines are no longer problematic to the assignment process. This indicates that our algorithm can produce accurate assignments with reliable and reasonably fast assignment times even when data is missing.

% PUT IN FIGURE 2 HERE *********************
Our algorithm using LMT filtering with proline checking can complete a 62-residue assignment in approximately 40 minutes on a 2.3 GHz Intel Core i7 processor with 8Gb of RAM. In less than 1 second the LMT model can complete an assignment of 43 residues, compared to 27, 29 and 30 for the no filter, decision table and J4.8 models, respectively.

The use of proline checking and utilizing machine learning to filter data has shown to be extremely effective in accelerating the assignment. The reduction of nearly 3 orders of magnitude in assignment time allows for approximately twice as many residues to be assigned in the same time period. Our algorithm has completed assignments of up to 62 amino acids in less than an hour. The solution matched the manually assigned sequence, ensuring the accuracy of our algorithm. Given more time, our algorithm can complete longer assignments. However, with the overall exponential trend, the length of time required to complete assignments overcomes the usefulness of the automated assignment process for long protein sequences.
\\\\
\noindent\textbf {Conclusions and Future Directions}\\
Our algorithm has made significant advances in the field of automated assignment for protein backbone chemical shifts. We implemented machine learning to filter NMR data in order to reduce the branching factor in a search-based algorithm. This increased our assignment rate by approximately three orders of magnitude while still maintaining the accuracy of a comparative manually assigned solution.

In the future, we will improve the overall performance of our algorithm by optimizing cost calculations, handling missing data better, and sequencing chunks of data at a time (puzzle building). (Tim, should we even talk about this?)(Tim help us)

One of our main focuses for the future is handling missing data in a more efficient manner. By examining characteristics of the amino acids in the sequence, we hope to predict where missing data will end up in the final assignment. This would reduce the number of assignments attempted.

We are currently acquiring backbone chemical shifts for a new protein.This new data will include additional chemical shifts that can be used in the assignment process, such as the backbone carbonyl and H-alpha values. This data will be used to further validate and improve our algorithm. Since the cost calculation is crucial to the effectiveness of our algorithm, additional chemical shifts may prove invaluable to the success of the algorithm for longer protein sequences or incomplete datasets. We are also investigating methods of predicting the final cost of an assignment in order to remove unrealistic assignments early on. Having this information available will help optimize our cost calculation, resulting in a further decreased assignment times.

In order to accommodate longer protein sequences while still producing accurate assignments, we will also look at assigning separate sections of the protein sequence at one time. By chunking the amino acids into smaller sections and incorpo, we hope to decrease current assignment times. 
\\\\
\textbf{ACKNOWLEDGEMENTS}\\
The authors of this paper would like to thank Drake University for being a conductive space to research, Iowa State University for their use of their NMR spectroscopy machine, John Emmons for kicking off this research, and our ever supportive mentors Tim Urness and Adina Kilpatrick.

\noindent\textbf {}
\clearpage
\nocite{*}
\bibliographystyle{achemso}
%\bibliographystyle{biochem}
\bibliography{citations}

\vspace{1cm}
\noindent\textbf{ABOUT THE STUDENT AUTHORS}\\
\indent Joel Venzke (say some things) is not at this meeting, so his biography will be vandalized by other people while he cannot defend himself. His biography is going to be written in comic sans, since it fits him so well and he can’t choose his own font. Joel was born on January 6th 1994. It was a cold winter day in Minnesota when he was brought into this world. His love for science started at a young age as he liked to take apart Easy Bake Ovens in order to put them back together. Ironically that sparked his love for petit fors, especially with blackberry jam. Yum-o! After his toaster phase, Joel started experimenting with cooking. He honed his skills and currently is making jerky, of the beef variety. Literally, he is right now. We hope he can put his love for jerky aside in the near future so he can continue his research. He better damn bring us some jerky. Also possibly take some photos along the way.

David Mascharka is a sophomore pursuing a B.S. in Computer Science and Mathematics and B.A. in Philosophy. David also pursues his love for mathematics as the president of the math club in which is he able to hone his leadership skills.Plus he is a pretty cool guy. David is a really special guy and is going to do great things in the future. Just watch. He actually will. He really has no idea what to put here, and so will change this later. Sure, sure it will.

Paxten Johnson is on track to graduate in the Spring of 2016 with a B.S. in Physics, Computer Science, and Mathematics. Aside from conducting this research for the past two years, she has been involved with Air Force ROTC, Delta Gamma Fraternity, and the Drake Honor’s Program. She hopes to use the knowledge and experience gained from this research to help her advance into the military intelligence branch of the Air Force.

Rachel Davis is a mere semester away from her B.S. in both Computer Science and Mathematics. This is the second year conducting this sequencing research. Her research includes not only this primary structuring of proteins, but also a collaborative tertiary structuring algorithm. Currently she is applying to summer internships closely relating to her interests and expertise.

Katie Roth is currently pursuing a B.A. in Mathematics and Computer Science. She has been working on this research for two years, and enjoys it immensely. Katie is the treasurer of the Women in Mathematics and Computer Science and an active member of Math Club. She is currently applying for summer research experiences, as well as internships.

Leah Robison is on her way to graduate with a B.S. in Environment Science and a minor in Computer Science. Apart from studying abroad in Denmark for a semester, she has been involved with this research group for the past two years. She hopes to apply the knowledge gained from this research to future studies in the field of Environmental Science.
\\\\
\noindent\textbf{PRESS SUMMARY}\\
Manually assigning nuclear magnetic resonance data to a backbone protein sequence is time consuming and error prone. Although current algorithms have made advances in this area, a student research group at Drake University is improving the process by utilizing machine learning to identify amino acids before assignment. Using both old and new methods has resulted in an algorithm that is fast and accurate. 
\end{document}

### 2015-03-12 Papers_and_Presentations/paper_spring_2015/paper.tex
Updated paper

@@
 \usepackage{setspace}
+\usepackage{float}
 \usepackage{caption}
@@
 \usepackage{achemso}
+\setkeys{acs}{usetitle=true}
 \usepackage[affil-it]{authblk}
@@
 \begin{abstract}
-Nuclear magnetic resonance (NMR) spectroscopy is a powerful method for studying the three-dimensional structure of molecules, including proteins.
-These methods provide useful data for the sequencing of amino acids into primary protein structures.
-Unfortunately, current manual techniques for analyzing these NMR datasets can take months to assign and are highly susceptible to error.
-Many programs have been developed to sequence protein backbone structures, with various strengths and weaknesses.
-The algorithm detailed in this paper works to overcome the obstacles others have met by utilizing machine learning to predict amino acid type, thereby increasing assignment speed.
-The program also generates place-holders to accommodate missing data and recurring amino acids with problematic chemical characteristics, namely proline.
+Nuclear magnetic resonance (NMR) spectroscopy is a powerful method for determining three-dimensional structures of biomolecules, including proteins.
+In a critical step of the structure determination process for proteins, measured NMR values are assigned to specific amino acids in the protein primary sequence.
+Unfortunately, current manual techniques for the assignment of NMR data are time-consuming and susceptible to error.
+Many algorithms have been developed to automate the process, with various strengths and weaknesses.
+The algorithm described in this paper works to overcome the obstacles others have met by utilizing machine learning to predict amino acid type, thereby increasing assignment speed.
+The program also generates place-holders to accommodate missing data and recurring amino acids with unique chemical characteristics, namely proline.
 This approach is able to speed up the process of assignment by almost three orders of magnitude while maintaining high accuracy when compared to a previously assigned set.
@@
 \noindent \textbf{INTRODUCTION}\\
+NMR spectroscopy is a powerful method for obtaining atomic-resolution three-dimensional protein structures, as well as assessing changes in protein conformations or motions due to mutations or interactions with ligands or other biomolecules.
+Determining a protein's structure is essential for understanding its function and alterations in function, which often lead to disease.
 The analysis of Nuclear Magnetic Resonance (NMR) data, in particular the sequence-specific assignment of backbone and side-chain protein resonances, is an error-prone and time-consuming step during protein structure determination by NMR spectroscopy \cite{aria}.
-NMR spectroscopy is a powerful method for obtaining atomic-resolution three-dimensional protein structures, as well as assessing changes in protein conformations or motions due to mutations or interactions with ligands or other biomolecules.
-Determining a protein’s structure is essential for understanding its function and alterations in function, which often lead to disease.
 This paper describes a computational algorithm that utilizes machine learning in the process of automating the assignment of backbone protein NMR resonances.
@@
 NMR spectroscopy experiments generate information on several variables that can be used in the determination of protein structures.
-In particular, essential information is provided by the chemical shifts determined by NMR-active nuclei present in proteins, including hydrogen and isotopes of carbon and nitrogen.
+In particular, essential information is provided by the chemical shifts of NMR-active nuclei present in proteins, including hydrogen and isotopes of carbon and nitrogen.
 The chemical shift is a quantifier for the deviation in the resonant frequency of a nucleus from its value in a structure-free environment, and therefore provides information on the local conformation.
-Measuring the chemical shifts of all or most of the nuclei in a biomolecule is the first step in determining its structure by NMR spectroscopy.
-An important set of chemical shifts in a protein are those corresponding to the nuclei in the backbone of the protein polypeptide chain, including the amide nitrogen (N), attached hydrogen (H), and the alpha and beta carbons ($C_\alpha$ and $C_\beta$) of each residue.
-The chemical shift values are measured using various three-dimensional NMR experiments, and then matched to the individual residues in the protein in a process called sequential assignment.
+Measuring the chemical shifts of all or most of the nuclei in a protein is the first step in determining its structure by NMR spectroscopy.
+An important set of protein chemical shifts are those corresponding to the nuclei in the backbone of the protein polypeptide chain, including the amide nitrogen (N), attached hydrogen (H), and the alpha and beta carbons ($C_{\alpha}$ and $C_{\beta}$) of each residue.
+Chemical shift values are measured using various three-dimensional NMR experiments, and then matched to the individual residues in the protein in a process called sequential assignment.
 
-Triple resonance experiments are the method of choice for proteins and other large biomolecules, because they can greatly decrease the amount of spectral overlap in data.
-Typical experiments for the assignment of backbone resonances include HNCA, HN(CO)CA, HNCACB, and CBCA(CO)NH or HN(CO)CACB \cite{mars}.
+Triple resonance experiments on hydrogen, nitrogen and carbon nuclei are the method of choice for proteins and other large biomolecules, because they can greatly decrease the amount of spectral overlap in data.
+Typical experiments for the assignment of backbone resonances include HNCA, HN(CO)CA, HNCACB, and CBCA(CO)NH or HN(CO)CACB2.
 These experiments transfer magnetization over the protein polypeptide chain, and thus connect different spin systems through covalent bonds.
-A spin system essentially contains all resonances belonging to a particular amino acid.
+A spin system essentially contains all resonances belonging to a particular residue in the protein sequence.
 The order of elements in experiment names indicates the order in which magnetization is passed down the line of nuclei, resonances in parentheses being used only for transfer to the next nucleus.
-All these experiments produce spectra with common H-N resonance correlations, and provide connectivities between neighboring residues.
-For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_\alpha$ and $C_\beta$ nuclei of each residue in the protein chain (residue $i$) , as well as the immediately preceding residue (residue $i-1$).
+All these experiments produce NMR spectra with common H-N resonance correlations, and provide connectivities between neighboring residues.
+For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_{\alpha}$ and $C_{\beta}$ nuclei of each residue in the protein chain (residue i), as well as the immediately preceding residue (residue $i-1$).
 In this experiment, resonances corresponding to residue $i$ can usually be distinguished from the $i-1$ values due to their higher intensity.
 However, ambiguities can arise if the intensities are comparable or if chemical shift values overlap.
-Such uncertainty happens frequently and can be resolved by using additional experiments.
-For example, an experiment CBCA(CO)NH yields the chemical shifts of the preceding residue only, unambiguously identifying $i$ and $i-1$  values.
+These ambiguities can be resolved by using additional experiments.
+For example, the CBCA(CO)NH experiment yields the chemical shifts of the preceding residue only, unambiguously identifying $i$ and $i-1$ values.
 Using all inter-residue connectivities, a chain of correlations through the protein backbone chemical shifts can be established.
-Sequentially-linked chemical shift values reflect the ordered linear arrangement of individual residues in the protein sequence.
-The pattern is then matched to the protein sequence through certain residues with characteristic $C_\alpha$ and $C_\beta$ chemical shift ranges that uniquely identify them.
-Thus, each measured chemical shift is assigned to a protein residue and can be used to infer structural information about the biomolecule.
+The pattern of sequentially-linked chemical shift values reflects the linear arrangement of individual residues in the protein sequence.
+This pattern is then matched to the protein sequence through certain residues with characteristic $C_{\alpha}$ and $C_{\beta}$ chemical shift values that uniquely identify them.
+Thus, each measured chemical shift is assigned to a protein residue and can then be used to infer structural information about the biomolecule.
 \\\\
-\noindent \textbf{SEQUENTIAL ASSIGNMENT STRATEGIES}\\
+\noindent \textbf{SEQUENTIAL ASSIGNMENT STRATEGIES}
+\begin{figure}[b]
+	\caption{A sequence can be placed in order by matching $C_{\alpha}$ and $C_{\beta}$ values}
+	\label{fig:joel_figure}
+	\begin{center}
+		\includegraphics[keepaspectratio=true, width=0.7\textwidth]{residue_thingy}
+	\end{center}
+\end{figure}
+
 The sequential assignment of backbone chemical shifts can be done manually or in an automated fashion.
@@
 In the early days of NMR spectroscopy, these chemical shifts were measured using a ruler \cite{guntert}.
-Nowadays, many computer programs, such as NMRPipe \cite{nmrpipe} and SPARKY \cite{zimmerman}, can be used to process, analyze and visualize NMR data.
+Nowadays, many computer programs, such as NMRPipe \cite{nmrpipe} and SPARKY \cite{goddard}, can be used to process, analyze and visualize NMR data.
 After grouping chemical shifts into spin systems, sequential spin systems are linked into increasingly larger segments by matching $i-1$ and $i$ values.
+This process can be seen in Figure~\ref{fig:joel_figure}.
 In parallel, the spin systems are classified into possible residue types, using a set of established chemical shift values for each of the 20 common amino acids found in proteins.
-For example, alanines have $C_\alpha$ and $C_\beta$ chemical shifts ranging from approximately 50 to 5 ppm (parts per million), and 17 to 25 ppm, respectively; glycines have unique $C_\alpha$ values in the 45 ppm region; and threonines have distinctive $C_\beta$ values in the 68-73 ppm range \cite{biomagresbank}.
+For example, alanines have $C_{\alpha}$ and $C_{\beta}$ chemical shifts ranging from approximately 50 to 56 ppm (parts-per-million), and 17 to 25 ppm, respectively; glycines have unique $C_{\alpha}$ values in the 45 ppm region, and threonines have distinctive $C_{\beta}$ values in the 68-73 ppm range\cite{wishart, wang}.
 Using the residue type information, the linked segments from the resonance sequential walk are iteratively mapped onto the protein primary sequence.
@@
 These automated methods decrease the time needed to complete the assignment, and attempt to minimize the risk of human error and subjectivity.
-A wide variety of algorithms and software packages for the assignment of backbone chemical shifts exist.
-Amongst a few of the most well known are GARANT \cite{guntert}, AutoAssign \cite{zimmerman} and MARS \cite{mars}.
+A wide variety of algorithms and software packages for the assignment of backbone chemical shifts exist \cite{guntert}, including GARANT \cite{garant}, AutoAssign \cite{moseley,zimmerman} and MARS \cite{mars}.
 
-The GARANT program has three key elements \cite{garant}.
-It starts with matching measured chemical shift values to values expected from the protein sequence.
-It then evaluates the correctness of  these matches using a scoring function, and optimizes the score using an evolutionary algorithm in conjunction with a local optimization routine \cite{guntert}.
-This optimization is similar to simulated annealing which makes repeated selections until the optimal solution is reached (8).
-AutoAssign uses a combination of artificial intelligence techniques and statistical methods to obtain the assignment \cite{james} .
-This program utilizes four basic steps, generally following the overall assignment strategy described above, but providing customized and novel solutions for each step.
-It first ranks and sorts spin systems.
-Secondly, it creates lists of possible amino acid types using Bayesian statistical methods.
-In step 3, AutoAssign links sequential spin systems into fragments, starting from spin systems that have a unique one-to-one match.
-Lastly, the fragments are mapped onto the protein sequence.
-Steps three and four are interleaved and run iteratively, such that sequential connectivities are established in parallel with  the identification of amino acid types.
-The software MARS optimizes the search by simultaneously assessing the local and global quality of the assignment \cite{mars}.
-This program breaks the assignment into segments, linking and mapping fragments consisting of up to five residues, and using them as units in the search.
-The most accurate model is selected in combination with protein secondary structure prediction.
-The reliability of fragment mapping is tested by performing multiple runs with chemical shifts modified by the addition of artificial noise.
-
-These and other programs have paved the way for the automation of protein backbone assignments and made significant advances toward complete automation of protein structure determination by NMR spectroscopy.
-However, several issues remain.
-Some strategies may abandon a promising assignment too early if it has a higher error than other assignments, and thus the optimal solution will not be selected in the end \cite{mars}.
-Occasionally, a local minimum can throw off the optimization process \cite{mars}.
-Further issues arise when assigning larger protein chains.
-Some programs need days to finish the assignment in these cases; even then, the calculations can still have very high errors.
-
-Our algorithm utilizes elements from these existing programs, but employs novel concepts from machine learning to accelerate the assignment process.
+Our algorithm utilizes elements from these existing programs, such as cost analysis, sorting amino acids into groups.
+Our algorithm employs novel concepts from machine learning to accelerate the assignment process.
 \\\\
-\noindent\textbf{Machine Learning}\\
+\noindent\textbf{MACHINE LEARNING}\\
 Machine learning provides algorithms that learn from attributes in the input data to increase performance.
@@
 
-Machine learning offers a natural solution to the problem of determining amino acid type from NMR chemical shifts values.
-The overlap between the normal range of $C_\alpha$ and $C_\beta$ values between many amino acids makes it difficult to infer the type of residue based solely on chemical shift information.
+Machine learning offers a natural solution to the problem of determining amino acid type from NMR chemical shift values.
+The overlap between the normal range of $C_{\alpha}$ and $C_{\beta}$ values between many amino acids makes it difficult to infer the type of residue based solely on chemical shift information.
 Machine learning algorithms offer a unique approach to this problem and achieve excellent accuracy.
@@
 \\\\
-\noindent\textbf {Methods}\\
-Our goal is to create an automated program for the assignment of protein backbone chemical shifts that could deliver quality results in a small amount of time without the use of a supercomputer.
-Our program implements group sorting, machine learning, filtered amino acid selection, and careful cost calculation.
-The algorithm completes resonance assignment in six steps: (1) the NMR chemical shifts and the protein sequence are used as input data that fills data structures; (2) the protein sequence is processed and empty data structures are initialized for missing data; (3) the machine learning model assigns possible amino acid types to each spin system; (4) filtering is applied to locate chemical shift data that corresponds to residue 1 in the protein sequence; (5) the search continues with the best assignments until all chemical shift data is assigned; (6) the best solution is recorded and the process is terminated.
+\noindent\textbf{PROGRAM DEVELOPMENT}\\
+Our goal is to create an automated program for the assignment of protein backbone chemical shifts that can deliver quality results in a small amount of time without the use of a supercomputer.
+Our program implements group sorting, machine learning, filtered amino acid selection, and careful cost calculations.
+The algorithm completes resonance assignment in six steps: (1) the NMR chemical shifts and the protein sequence are used to fill data structures; (2) the protein sequence is processed and empty data structures are initialized for missing data; (3) the machine learning model assigns possible amino acid types to each spin system; (4) filtering is applied to locate chemical shift values that could potentially be assigned to residue 1 in the protein sequence; (5) the search continues with the best assignments until all chemical shift data is assigned; (6) the best solution is recorded and the process is terminated.
 
 Before the algorithm begins the assignment process, machine learning is used to build a model for predicting amino acid type.
-After the model is trained, the assignment process consisting of the pre-processing steps (steps 1 to 3) and the search (steps 4 to 6) begins.
-Pre-processing is where our research has made significant advances in order to decrease assignment time by predicting amino acid types.
-This allows the data to be filtered, significantly reducing the branching factor.
-The algorithm is then able to intelligently search the remaining possibilities for the best assignment.
+After the model is trained, the pre-processing component of the algorithm (steps 1 to 3) begins.
+Pre-processing is where our research has made significant advances: by predicting amino acid types with machine learning algorithms, the assignment time is decreased significantly.
+Machine learning allows the data to be filtered, significantly reducing the branching factor.
+The algorithm is then able to intelligently search the remaining possibilities for the best assignment (steps 4 to 6).
 \\\\
-\noindent\textit{Machine Learning Data Collection}\\
-The training dataset for the machine learning algorithm was obtained from BMRB.
-We initially identified 9,736 datasets containing chemical shifts for the $C_\alpha$ and $C_\beta$ resonances of 689,977 residues.
-However, a preprocessing step was necessary in order to remove extreme values for each amino acid and improve both accuracy and generalization.
-Removing outliers prevents the algorithms from fitting extraneous data, improving future performance.
-By looking at statistics available on the BMRB site, we excluded chemical shift values outside three standard deviations of the mean for each amino acid type.
-This gave us 681,363 pairs of $C_\alpha$ and $C_\beta$ values to use for training.
+\noindent\textbf{METHODS}\\
+\noindent\textit{MACHINE LEARNING DATA COLLECTION}\\
+The training dataset for the machine learning algorithm was obtained from the Biological Magnetic Resonance Bank (BMRB), a database of NMR chemical shifts hosted by the University of Wisconsin at Madison \cite{biomagresbank}.
+We initially identified 9,736 datasets containing chemical shifts for the $C_{\alpha}$ and $C_{\beta}$ resonances of 689,977 residues.
+In order to improve both accuracy and generalization, and to prevent the algorithm from fitting extraneous data, it was necessary to remove outliers from the published datasets.
+By inspecting statistics available on the BMRB site, we excluded chemical shift values outside three standard deviations of the mean for each amino acid type.
+This gave us 681,363 pairs of $C_{\alpha}$ and $C_{\beta}$ values to use for training.
 \\\\
-\noindent\textit{Pre-processing}\\
-Step 1 consists of reading the chemical shift values and the protein amino acid sequence from an input file.
-We use the $C_\alpha$ and $C_\beta$ values for residues $i$ and $i-1$  to create an object we will refer to as a tile.
-A tile holds information corresponding to a single residue in the protein sequence to be assigned.
+\noindent\textit{PRE-PROCESSING}\\
+Step 1 of our algorithm consists of reading the chemical shift values and the protein amino acid sequence from an input file.
+We use the $C_{\alpha}$ and $C_{\beta}$ values for each pair of $i$ and $i-1$ residues to create an object we will refer to as a tile.
+A tile holds all the available chemical shift information corresponding to a single residue in the protein sequence to be assigned.
 In step 3, amino acid types will be assigned to each tile.
 
-Step 2 of the algorithm converts the protein sequence from the abbreviations into $C_\alpha$ and $C_\beta$ chemical shift values, using statistics provided by the Biological Magnetic Resonance Bank \cite{biomagresbank}, a database of NMR chemical shifts hosted by the University of Wisconsin at Madison.
-These statistics provide average chemical shift values for each of the twenty common amino acids found in proteins, using 4944897 chemical shifts published in BMRB as of February 2, 2015.
-For example, we assign alanine a $C_\alpha$ chemical shift of 53.19 ppm (parts-per-million) and a $C_\beta$ chemical shift of 18.96 ppm.
-Then the protein sequence is analyzed.
-The algorithm looks for prolines in the protein sequence.
-Since prolines do not generate chemical shift data from these experiments, special tiles are created to handle this case.
-Identifiers in the proline tiles ensure that the tile is placed only when the corresponding residue in the protein sequence is a proline.
-This identifier limits the number of possibilities where the tile can be assigned.
+Step 2 of the algorithm converts the protein primary sequence into $C_{\alpha}$ and $C_{\beta}$ chemical shift values, using statistics available in BMRB.
+These statistics provide average chemical shift values for each of the twenty common amino acids found in proteins.
+For example, we assign alanine a $C_{\alpha}$ chemical shift of 53.19 ppm and a $C_{\beta}$ chemical shift of 18.96 ppm.
+Next, the algorithm searches the protein sequence for prolines, as prolines lack H-N spin systems.
+As a consequence, HNCACB and CBCA(CO)NH experiments do not provide $C_{\alpha}$ and $C_{\beta}$ chemical shifts for this residue.
+Special tiles, designed to specifically identify the proline residue, are created to handle this case.
+Identifiers in the proline tiles ensure that these tiles are placed only when the corresponding residue in the protein sequence is a proline.
+The identifier limits the number of possibilities where the tile can be assigned.
 The length of the protein sequence is then compared to the total number of tiles created thus far.
@@
 Blank tiles can fit in any location in the assignment.
-Large amounts of missing data will deteriorate the algorithm’s performance.
+However, large amounts of missing data will deteriorate the algorithm's performance as every blank tile would need to be checked for the best fit in every position in the assignment.
 
-Step 3 assigns possible amino acid types to each tile.The $C_\alpha$ and $C_\beta$ values for residue $i$ in each tile are processed by our machine learning model, producing a list of probabilities that a tile represents each amino acid.
+Step 3 assigns possible amino acid types to each tile.The $C_{\alpha}$ and $C_{\beta}$ values for residue $i$ in each tile are processed by our machine learning model, producing a list of probabilities that a tile represents a certain amino acid.
 The probabilities correspond to confidence levels used for filtering during the assignment process.
 
-Preprocessing the dataset takes a minimal amount of time (less than a second on a standard laptop) and drastically reduces the time required to assign dataset without affecting accuracy.
+Preprocessing the dataset takes a minimal amount of time (less than a second on a standard laptop) and drastically reduces the time required to assign the chemical shifts without affecting accuracy.
 The search for the optimal assignment then begins.
 \\\\
-\noindent\textit{The Search}\\
-The algorithm begins an intelligent search through filtered combinations of all possible chemical shifts.
+\noindent\textit{THE SEARCH}\\
+The algorithm initiates an intelligent search through filtered combinations of all possible chemical shifts.
 The search begins by placing the first tile, which is selected based on a filtering process.
-Only titles that correspond to the first amino acid based on a confidence level threshold (0.4\% match or better) are placed at residue one.
+Only tiles that could correspond to the first amino acid based on a confidence level threshold (0.4\% match or better) are placed at residue one.
+The threshold was chosen by determining the lowest probability for a correct amino acid classification.
 
-At this point, the cost of assignment is generated.
-The cost of placing a tile consists of two parts: (1) the difference between the tile’s residue $i-1$  values and the previous tile’s residue $i$ values and (2) the difference between the residue $i$ values and the values predicted from the protein sequence.
-In the case of blank and proline tiles, a fixed cost is added in place of the above calculation.
+At this point, a “cost” of assignment is generated.
+The cost of placing a tile consists of two parts: (1) the difference between the tile's residue $i-1$ values and the previous tile's residue $i$ values, and (2) the difference between the residue $i$ values and the values predicted from the protein sequence.
+In the case of blank and proline tiles, a fixed cost is added instead of  the above calculation.
 Since initially only one tile is placed, the cost is based solely on a comparison to the protein sequence, and the search moves on to step 5.
@@
 In step 5, the algorithm selects the assignment with the lowest cost to continue the search process.
-If the assignment is a solution, the algorithm moves on to step 6.
 A solution is reached when all tiles have been placed in an assignment.
@@
 
-In the final step the search records the solution. The solution assignment is formatted for easy reading and output along with the algorithm’s performance. Then the algorithm terminates. 
+In the final step the search records the solution. The solution assignment along with the performance (the number of possible assignments searched) is output. Then the algorithm terminates. 
 \\\\
-\noindent\textbf {Results}\\
-The chemical shift dataset used in this study consisted of $C_\alpha$ and $C_\beta$ values for the 59-residue (our data set is 62 long) long C-terminal domain of the Tfg1 subunit of the yeast transcription factor TFIIF.
+\noindent\textbf{RESULTS}\\
+The chemical shift dataset used in this study consisted of $C_{\alpha}$ and $C_{\beta}$ values for the 62-residue long C-terminal domain of the Tfg1 subunit of the yeast transcription factor TFIIF.
 The chemical shifts were previously obtained by Kilpatrick et al.
-from HNCACB and CBCA(CO)NH experiments, and manually assigned to 99\% completeness.
-The previously assigned data was cut into sub-sections, randomized, and used for algorithmic analysis.
+from HNCACB and CBCA(CO)NH experiments, and manually assigned to 99\% completeness\cite{kilpatrick}.
+The chemical shift dataset was cut into sub-sections, randomized, and used for algorithmic analysis.
 
-The results of assigning this dataset with different filtering methods are shown in Figure 1.
-For sequences of up to 62 residues a smooth trend for all filtering methods tested was seen when graphing the generated nodes (or different assignments) against the sequence lengths.
-Interestingly, a comparison of the methods indicates that our filtering process results in a significant decrease in number of generated nodes compared to an unfiltered generic search algorithm, as seen in Figure 1.
-Since the most time-consuming part of the search is node generation, there is a direct correlation between assignment time and number of nodes generated.
-The graph indicates that the LMT algorithm has the best performance, outperforming the method with no filter by almost two orders of magnitude, without loss of assignment accuracy.
-This not only accelerates assignment, but also allows for larger datasets to be assigned.
+The results of assigning this dataset with different filtering methods are shown in Figure~\ref{fig:figure1}.
+Each of the tests described in Figure~\ref{fig:figure1} follow a smooth trend, as opposed to a highly irregular trend which would indicate an impediment in the processing and sequencing of data.
+A comparison of the methods indicates that our filtering process results in a significant decrease in number of generated nodes compared to an unfiltered generic search algorithm.
+Since the most time-consuming part of the search is node generation, there is a direct correlation between assignment time and the number of nodes generated.
+The graph indicates that the LMT machine learning algorithm has the best performance, outperforming the unfiltered method by almost two orders of magnitude, without loss of assignment accuracy.
+LMT established itself as best because it was able to assign all 62 residues within forty-five minutes, whereas the other filters were unable to complete the full assignment within a 12 hour time limit.
+The LMT model not only accelerates assignment, but also allows for larger datasets to be assigned in the same amount of time.
 
-% PUT IN FIGURE 1 HERE *******************
+\begin{figure}[H]
+	\caption{Impact of filtering methods on assignment time.
+Number of nodes (y-axis) are plotted as a function of number of residues (protein sequence length) used in the assignment (x-axis).
+The search without machine learning filtering is depicted in blue.
+The other three groups (DecisionTable, J4.8 and LMT) are the machine learning algorithms that were used for filtering, e.g.
+DecisionTable used a Decision Table for the filtering process.}
+	\label{fig:figure1}
+	\begin{center}
+		\resizebox{!}{0.6\textwidth}{\input{ProFix_full.tex}}
+	\end{center}
+\end{figure}
 
-Figure 2 shows the impact of proline identification on our algorithm’s performance.
-The same unfiltered and LMT data from Figure 1 is plotted for comparison.
-The large jump in assignment time from 32 to 33 residues shows the performance impact of missing data.
-In the sequence of the studied protein, residue 33 is a proline, which lacks NH (check denotation previously in paper) spin systems.
-As a consequence, HNCACB and CBCA(CO)NH experiments do not provide $C_\alpha$ and $C_\beta$ chemical shifts for this residue.
-If the algorithm identifies and deals with prolines as a special case, only one more node is generated for the 33-residue case.
-However, if the proline is not dealt with separately, the algorithm’s performance is significantly impacted.
+The impact of proline identification on our algorithm's performance is shown in Figure~\ref{fig:figure2}.
+The same unfiltered and LMT data from Figure~\ref{fig:figure1} is plotted for comparison.
+The large jump in assignment time between 32 and 33 residue long sequences shows the performance impact of missing data on performance without filtering and using the LMT model for filtering.
+In the sequence of the studied protein, residue 33 is a proline, for which chemical shifts are missing.
+If the algorithm identifies and handles prolines as a special case, only one more node is generated for the 33-residue long sequence.
+However, if the proline is not dealt with separately, the algorithm's performance is significantly impacted.
 Without proline checking, the proline tile is placed in every position in the assignment.
-The result is a major increase in the branching factor that leads to the jump observed in Figure 2.
+The result is a major increase in the branching factor that leads to the jump observed in Figure~\ref{fig:figure2}.
 With proline checking, prolines are no longer problematic to the assignment process.
-This indicates that our algorithm can produce accurate assignments with reliable and reasonably fast assignment times even when data is missing.
+This indicates that our algorithm can accurately reproduce assignments with reasonably fast assignment times even when chemical shift data is missing.
 
-% PUT IN FIGURE 2 HERE *********************
-Our algorithm using LMT filtering with proline checking can complete a 62-residue assignment in approximately 40 minutes on a 2.3 GHz Intel Core i7 processor with 8Gb of RAM.
-In less than 1 second the LMT model can complete an assignment of 43 residues, compared to 27, 29 and 30 for the no filter, decision table and J4.8 models, respectively.
+\begin{figure}[H]
+	\caption{Impact of proline identification on assignment time.
+Number of nodes (y-axis) as a function of number of residues used in the assignment (x-axis).
+Blue shows the search with proline checking and without machine learning filtering.
+Similarly, the search without either proline checking or machine learning filtering is depicted in purple.
+The search with proline checking and LMT machine learning filtering is depicted in red.
+Not utilizing proline checking, but using LMT machine learning filtering is depicted in green.}
+	\label{fig:figure2}
+	\begin{center}
+		\resizebox{!}{0.6\textwidth}{\input{pro_compare.tex}}
+	\end{center}
+\end{figure}
 
-The use of proline checking and utilizing machine learning to filter data has shown to be extremely effective in accelerating the assignment.
-The reduction of nearly 3 orders of magnitude in assignment time allows for approximately twice as many residues to be assigned in the same time period.
-Our algorithm has completed assignments of up to 62 amino acids in less than an hour.
-The solution matched the manually assigned sequence, ensuring the accuracy of our algorithm.
-Given more time, our algorithm can complete longer assignments.
-However, with the overall exponential trend, the length of time required to complete assignments overcomes the usefulness of the automated assignment process for long protein sequences.
+Our algorithm with LMT filtering and proline identification can complete the 62-residue assignment in approximately 40 minutes on a 2.3 GHz Intel Core i7 processor with 8Gb of RAM.
+The LMT model with proline checking can complete the assignment of a 43-residue long sub-sequence in less than 1 second, compared to 27, 29 and 30 seconds without filtering, using a Decision Table for filtering and using the J4.8 model for filtering, respectively.
+In all cases, the solution from the automated algorithm is identical to the manual assignment, indicating that our algorithm is both fast and accurate.
 \\\\
-\noindent\textbf {Conclusions and Future Directions}\\
-Our algorithm has made significant advances in the field of automated assignment for protein backbone chemical shifts.
+\noindent\textbf {CONCLUSIONS AND FUTURE DIRECTIONS}\\
+Our algorithm has made significant advances in the field of automated assignment of protein backbone chemical shifts.
 We implemented machine learning to filter NMR data in order to reduce the branching factor in a search-based algorithm.
-This increased our assignment rate by approximately three orders of magnitude while still maintaining the accuracy of a comparative manually assigned solution.
+This increased our assignment rate by approximately three orders of magnitude while still maintaining the accuracy of a manually assigned solution.
 
-In the future, we will improve the overall performance of our algorithm by optimizing cost calculations, handling missing data better, and sequencing chunks of data at a time (puzzle building).
-(Tim, should we even talk about this?)(Tim help us)
+The use of proline checking and the utilization of machine learning to filter data has shown to be extremely effective in accelerating the assignment.
+Constrained within the same period of time, reducing the assignment time by 3 orders of magnitude allows for twice as many residues to be assigned.
+Our algorithm has successfully completed assignments of up to 62 amino acids in a short amount of time and if allotted more time, more residues could be assigned.
 
@@
 This would reduce the number of assignments attempted.
+Furthermore, we will look to improve the overall performance of our algorithm by optimizing cost calculations and investigate sequencing via parallel processing.
 
-We are currently acquiring backbone chemical shifts for a new protein.This new data will include additional chemical shifts that can be used in the assignment process, such as the backbone carbonyl and H-alpha values.
+We are currently measuring the backbone chemical shifts of a protein previously uncharacterized by NMR spectroscopy.
+This new dataset will include additional chemical shifts that can be used in the assignment process, such as the backbone carbonyl and H-alpha values.
 This data will be used to further validate and improve our algorithm.
@@
 We are also investigating methods of predicting the final cost of an assignment in order to remove unrealistic assignments early on.
-Having this information available will help optimize our cost calculation, resulting in a further decreased assignment times.
+Having this information available will help optimize our cost calculation, resulting in a further decrease in assignment times.
+\\\\
+\textbf{ACKNOWLEDGEMENTS}
+\\
+The authors of this paper would like to thank Drake University for being a conducive space to research, John Emmons for initiating this research.
 
-In order to accommodate longer protein sequences while still producing accurate assignments, we will also look at assigning separate sections of the protein sequence at one time.
-By chunking the amino acids into smaller sections and incorpo, we hope to decrease current assignment times.
-\\\\
-\textbf{ACKNOWLEDGEMENTS}\\
-The authors of this paper would like to thank Drake University for being a conductive space to research, Iowa State University for their use of their NMR spectroscopy machine, John Emmons for kicking off this research, and our ever supportive mentors Tim Urness and Adina Kilpatrick.
-
-\noindent\textbf {}
+\noindent\textbf {REFERENCES}
 \clearpage
-\nocite{*}
+%\nocite{*}
 \bibliographystyle{achemso}
-%\bibliographystyle{biochem}
 \bibliography{citations}
@@
 \noindent\textbf{ABOUT THE STUDENT AUTHORS}\\
-\indent Joel Venzke (say some things) is not at this meeting, so his biography will be vandalized by other people while he cannot defend himself.
-His biography is going to be written in comic sans, since it fits him so well and he can’t choose his own font.
-Joel was born on January 6th 1994.
-It was a cold winter day in Minnesota when he was brought into this world.
-His love for science started at a young age as he liked to take apart Easy Bake Ovens in order to put them back together.
-Ironically that sparked his love for petit fors, especially with blackberry jam.
-Yum-o!
-After his toaster phase, Joel started experimenting with cooking.
-He honed his skills and currently is making jerky, of the beef variety.
-Literally, he is right now.
-We hope he can put his love for jerky aside in the near future so he can continue his research.
-He better damn bring us some jerky.
-Also possibly take some photos along the way.
+\indent Joel Venzke is a junior pursuing a B.S.
+in Physics, Computer Science, and  Mathematics.
+Outside of conducting research, Joel is president of the Drake University chapter of the Society of Physics Students and vice president of the math club.
+He also works as an award winning photojournalist for Drake University Communications and The Times-Delphic.
+Joel will be conducting research at Oak Ridge National Lab this summer, and he plans to pursue a PhD in computational science.
 
-David Mascharka is a sophomore pursuing a B.S.
+David Mascharka is a sophomore seeking a B.S.
 in Computer Science and Mathematics and B.A.
 in Philosophy.
-David also pursues his love for mathematics as the president of the math club in which is he able to hone his leadership skills.Plus he is a pretty cool guy.
-David is a really special guy and is going to do great things in the future.
-Just watch.
-He actually will.
-He really has no idea what to put here, and so will change this later.
-Sure, sure it will.
+David also pursues his love for mathematics as the president of the math club at Drake University, where is he able to hone his leadership skills.
+His research interests include machine learning and mobile computation.
+David will be spending this summer conducting reasearch at the MIT Haystack Observatory.
 
@@
 in Physics, Computer Science, and Mathematics.
-Aside from conducting this research for the past two years, she has been involved with Air Force ROTC, Delta Gamma Fraternity, and the Drake Honor’s Program.
+Aside from conducting this research for the past two years, she has been involved with Air Force ROTC, Delta Gamma Fraternity, and the Drake Honor's Program.
 She hopes to use the knowledge and experience gained from this research to help her advance into the military intelligence branch of the Air Force.
 
-Rachel Davis is a mere semester away from her B.S.
+Rachel Davis is currently on the path to obtaining a B.S.
 in both Computer Science and Mathematics.
@@
 Her research includes not only this primary structuring of proteins, but also a collaborative tertiary structuring algorithm.
-Currently she is applying to summer internships closely relating to her interests and expertise.
+Currently she is applying to summer internships closely relating to both her interests and expertise.
 
-Katie Roth is currently pursuing a B.A.
+Katie Roth is pursuing a B.A.
 in Mathematics and Computer Science.
@@
 \noindent\textbf{PRESS SUMMARY}\\
-Manually assigning nuclear magnetic resonance data to a backbone protein sequence is time consuming and error prone.
+Manually assigning nuclear magnetic resonance data to a protein sequence is time consuming and error prone.
 Although current algorithms have made advances in this area, a student research group at Drake University is improving the process by utilizing machine learning to identify amino acids before assignment.

### 2015-04-03 search_project/Node.py
adding files to test script and cleaning up extra code files from runs

@@ -51,7 +51,16 @@ class Node(object):
 				# check to see if current tile can be placed in this location
 				amino_type_list = self.unplaced_tiles[i].get_amino_type()
 				amino_Idx = self.characteristic[char_num][2]
-				if(amino_type_list[amino_Idx] > 0.004):
+				if(amino_type_list[amino_Idx]==2.0):
+					temp_ut = list(self.unplaced_tiles) 
+					placed_tile = temp_ut.pop(i) 
+					temp_pt = list(self.placed_tiles) 
+					temp_pt.append(placed_tile)
+
+					# add child node to list of new_nodes
+					new_nodes.append(Node(temp_ut, temp_pt, self.cost, self.characteristic, self.char_cost, self.order_cost))
+
+				elif(amino_type_list[amino_Idx] > 0.004):
 
 					# copy unplaced and placed tile lists, remove tile from list and add it to the placed tile list
 					temp_ut = list(self.unplaced_tiles) 

### 2015-04-03 search_project/Node1.py

@@ -1,130 +1,0 @@
-#!/usr/bin/python
-
-"""
-A node contains a state in the search tree
-It contains the list of placed and unplaced tiles 
-It also holds the characteristic protein sequence if we have one
-It also has the cost of the search state
-"""
-
-class Node(object):
-
-	""" 
-	Initializes a node
-	ut: list of unplaced tiles in this node
-	pt: list of placed tiles in this node
-	cost: current cost associated with this node 
-	characteristic: list containing the characteristic backbone protein chain
-	char_cost: cost from comparing with the characteristic
-	order_cost: cost from comparing tiles with the one before it
-	"""
-	def __init__(self, ut, pt, cost, characteristic, char_cost, order_cost):
-		self.unplaced_tiles = ut
-		self.placed_tiles = pt
-		self.cost = cost
-		self.characteristic = characteristic
-		self.char_cost = char_cost
-		self.order_cost = order_cost
-
-	"""
-	prints the node to the console
-	"""
-	def __str__(self):
-		for tile in self.placed_tiles:
-			print tile.get_tile()
-		return ""
-
-	"""
-	Creates children nodes of the current node
-	returns a list of child nodes
-	"""
-	def expand(self):
-		new_nodes = []
-		char_num = len(self.placed_tiles) # location in the protein sequence
-
-		# If this Node contains a characteristic protein sequence we will use it
-		if(self.characteristic):
-
-			# loop through all tiles that have not been placed
-			for i in range(len(self.unplaced_tiles)):
-
-				# check to see if current tile can be placed in this location
-				amino_type_list = self.unplaced_tiles[i].get_amino_type()
-				amino_Idx = self.characteristic[char_num][2]
-				if(amino_type_list[amino_Idx]==2.0):
-					temp_ut = list(self.unplaced_tiles) 
-					placed_tile = temp_ut.pop(i) 
-					temp_pt = list(self.placed_tiles) 
-					temp_pt.append(placed_tile)
-
-					# add child node to list of new_nodes
-					new_nodes.append(Node(temp_ut, temp_pt, self.cost, self.characteristic, self.char_cost, self.order_cost))
-
-				elif(amino_type_list[amino_Idx] > 0.001):
-
-					# copy unplaced and placed tile lists, remove tile from list and add it to the placed tile list
-					temp_ut = list(self.unplaced_tiles) 
-					placed_tile = temp_ut.pop(i) 
-					temp_pt = list(self.placed_tiles) 
[…]

### 2015-04-03 search_project/Node2.py

@@ -1,130 +1,0 @@
-#!/usr/bin/python
-
-"""
-A node contains a state in the search tree
-It contains the list of placed and unplaced tiles 
-It also holds the characteristic protein sequence if we have one
-It also has the cost of the search state
-"""
-
-class Node(object):
-
-	""" 
-	Initializes a node
-	ut: list of unplaced tiles in this node
-	pt: list of placed tiles in this node
-	cost: current cost associated with this node 
-	characteristic: list containing the characteristic backbone protein chain
-	char_cost: cost from comparing with the characteristic
-	order_cost: cost from comparing tiles with the one before it
-	"""
-	def __init__(self, ut, pt, cost, characteristic, char_cost, order_cost):
-		self.unplaced_tiles = ut
-		self.placed_tiles = pt
-		self.cost = cost
-		self.characteristic = characteristic
-		self.char_cost = char_cost
-		self.order_cost = order_cost
-
-	"""
-	prints the node to the console
-	"""
-	def __str__(self):
-		for tile in self.placed_tiles:
-			print tile.get_tile()
-		return ""
-
-	"""
-	Creates children nodes of the current node
-	returns a list of child nodes
-	"""
-	def expand(self):
-		new_nodes = []
-		char_num = len(self.placed_tiles) # location in the protein sequence
-
-		# If this Node contains a characteristic protein sequence we will use it
-		if(self.characteristic):
-
-			# loop through all tiles that have not been placed
-			for i in range(len(self.unplaced_tiles)):
-
-				# check to see if current tile can be placed in this location
-				amino_type_list = self.unplaced_tiles[i].get_amino_type()
-				amino_Idx = self.characteristic[char_num][2]
-				if(amino_type_list[amino_Idx]==2.0):
-					temp_ut = list(self.unplaced_tiles) 
-					placed_tile = temp_ut.pop(i) 
-					temp_pt = list(self.placed_tiles) 
-					temp_pt.append(placed_tile)
-
-					# add child node to list of new_nodes
-					new_nodes.append(Node(temp_ut, temp_pt, self.cost, self.characteristic, self.char_cost, self.order_cost))
-
-				elif(amino_type_list[amino_Idx] > -2.0):
-
-					# copy unplaced and placed tile lists, remove tile from list and add it to the placed tile list
-					temp_ut = list(self.unplaced_tiles) 
-					placed_tile = temp_ut.pop(i) 
-					temp_pt = list(self.placed_tiles) 
[…]

### 2015-04-03 search_project/Scripts/get_data.sh

@@ -2,7 +2,7 @@
 
 cd ..
 
-for i  in $(seq 1 50); 
+for i  in $(seq 44 70); 
 do 
 	echo Data/Spring_2015_$i.txt
 	echo >> Scripts/aStar_spring2015_data.log

### 2015-04-03 search_project/Tile.py

@@ -19,7 +19,7 @@ class Tile(object):
     d: carbon beta value for residue i-1
     tile_list: A list of tiles that have been grouped together
     """
-    def __init__(self,a=0 ,b=0 ,c=0 ,d=0, model=None, tile_list=[]):
+    def __init__(self,a=0 ,b=0 ,c=0 ,d=0, model=None, tile_list=[], pro=False):
         if (not tile_list): # not given a tile list
             self.a = float(a)
             self.b = float(b)
@@ -29,7 +29,7 @@ class Tile(object):
             self.char_weight = .1
             self.order_weight = 1
             self.tile_list_cost = 0
-            self.amino_type = self.calculate_amino_type(model)
+            self.amino_type = self.calculate_amino_type(model,pro)
         else: # create a tile form the tile_list
             self.tile_list = tile_list
             self.amino_type = 0
@@ -51,7 +51,9 @@ class Tile(object):
     """
     Group tiles by expected amino acid type 
     """
-    def calculate_amino_type(self, model):
+    def calculate_amino_type(self, model, pro):
+        if pro:
+            return [0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 2.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0]
         i = Instance.create_instance(values=[1.0, self.a, self.b])
         if (self.a==-1 and self.b==-1 ):
             return [1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0, 1.0]

### 2015-04-03 search_project/Tile1.py

@@ -1,138 +1,0 @@
-#!/usr/bin/python
-
-import math
-from weka.core.dataset import Instance
-from weka.classifiers import Classifier
-
-
-"""
-A Tile contains the NMR data for a single amino acid or a list of amino acids
-"""
-
-class Tile(object):
-
-    """
-    To generate a tile provide (a,b,c,d) or (tile_list)
-    a: carbon alpha value for residue i
-    b: carbon beta value for residue i
-    c: carbon alpha value for residue i-1
-    d: carbon beta value for residue i-1
-    tile_list: A list of tiles that have been grouped together
-    """
-    def __init__(self,a=0 ,b=0 ,c=0 ,d=0, model=None, tile_list=[], pro=False):
-        if (not tile_list): # not given a tile list
-            self.a = float(a)
-            self.b = float(b)
-            self.c = float(c)
-            self.d = float(d)
-            self.tile_list = []
-            self.char_weight = .1
-            self.order_weight = 1
-            self.tile_list_cost = 0
-            self.amino_type = self.calculate_amino_type(model,pro)
-        else: # create a tile form the tile_list
-            self.tile_list = tile_list
-            self.amino_type = 0
-            self.char_weight = .1
-            self.order_weight = 1
-            
-            #assigns a and b of the last tile to the a and b value of combined tile
-            self.a = float(tile_list[-1].a)
-            self.b = float(tile_list[-1].b)
-
-            #assigns c and d of the fist tile to the c and d value of the combined tiles
-            self.c = float(tile_list[0].c)
-            self.d = float(tile_list[0].d)
-
-            # calculate the cost of the tile
-            self.tile_list_cost = self.calculate_tile_list_cost()
-
-
-    """
-    Group tiles by expected amino acid type 
-    """
-    def calculate_amino_type(self, model, pro):
-        if pro:
-            return [0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 2.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0]
-        i = Instance.create_instance(values=[1.0, self.a, self.b])
-        if (self.a==-1 and self.b==-1 ):
[…]

### 2015-04-03 search_project/Tile2.py

@@ -1,138 +1,0 @@
-#!/usr/bin/python
-
-import math
-from weka.core.dataset import Instance
-from weka.classifiers import Classifier
-
-
-"""
-A Tile contains the NMR data for a single amino acid or a list of amino acids
-"""
-
-class Tile(object):
-
-    """
-    To generate a tile provide (a,b,c,d) or (tile_list)
-    a: carbon alpha value for residue i
-    b: carbon beta value for residue i
-    c: carbon alpha value for residue i-1
-    d: carbon beta value for residue i-1
-    tile_list: A list of tiles that have been grouped together
-    """
-    def __init__(self,a=0 ,b=0 ,c=0 ,d=0, model=None, tile_list=[], pro=False):
-        if (not tile_list): # not given a tile list
-            self.a = float(a)
-            self.b = float(b)
-            self.c = float(c)
-            self.d = float(d)
-            self.tile_list = []
-            self.char_weight = .1
-            self.order_weight = 1
-            self.tile_list_cost = 0
-            self.amino_type = self.calculate_amino_type(model,pro)
-        else: # create a tile form the tile_list
-            self.tile_list = tile_list
-            self.amino_type = 0
-            self.char_weight = .1
-            self.order_weight = 1
-            
-            #assigns a and b of the last tile to the a and b value of combined tile
-            self.a = float(tile_list[-1].a)
-            self.b = float(tile_list[-1].b)
-
-            #assigns c and d of the fist tile to the c and d value of the combined tiles
-            self.c = float(tile_list[0].c)
-            self.d = float(tile_list[0].d)
-
-            # calculate the cost of the tile
-            self.tile_list_cost = self.calculate_tile_list_cost()
-
-
-    """
-    Group tiles by expected amino acid type 
-    """
-    def calculate_amino_type(self, model, pro):
-        if pro:
-            return [-3.0, -3.0, -3.0, -3.0, -3.0, -3.0, -3.0, -3.0, -3.0, -3.0, -3.0, -3.0, 2.0, -3.0, -3.0, -3.0, -3.0, -3.0, -3.0, -3.0]
-        i = Instance.create_instance(values=[1.0, self.a, self.b])
-        if (self.a==-1 and self.b==-1 ):
[…]

### 2015-04-03 search_project/search_project1.py

@@ -1,32 +1,0 @@
-"""
-Name: Joel Venzke, Katie Roth, Paxten Johnson, Rachel Davis, Leah Robison, John Emmons, Tim Urness, Adina Kilpatrick
-Date created: October 12th, 2013
-Description: This program automates the assignment of NMR data. 
-				The data is read in from a file and then the search will begin.
-				A uniform cost search is used if a 0 is given in the run command
-				A "puzzle building" search is completed if a 1 is given in the run command
-				
-				For further infromation on the project please see our paper:
-				http://www.micsymposium.org/mics2014/ProceedingsMICS_2014/mics2014_submission_35.pdf
-				or email joel.venzke@drake.edu
-
-				To run the code use the following command:
-				shell$ python search_project.py Path/To/Data/File.txt NumberOfSearchType
-"""
-
-
-import search_strategies1
-import time
-import sys
-
-# Error if not enough data is provided
-if len(sys.argv) < 2:
-	exit("NO INPUT DATA FILE OR MISSING SEARCH TYPE NUMBER\n\nPlease type: \nshell$ python search_project.py Path/To/Data/File.txt NumberOfSearchType\
-		\n\nSearch Type Numbers:\nUniform Cost: 0\nPuzzle Building: 1")
-
-# time and run search
-start = time.clock()
-search_strategies1.start_search(sys.argv[1],0)
-end = time.clock()
-
-print "Run Time:  " + str(end-start)

### 2015-04-03 search_project/search_project2.py

@@ -1,32 +1,0 @@
-"""
-Name: Joel Venzke, Katie Roth, Paxten Johnson, Rachel Davis, Leah Robison, John Emmons, Tim Urness, Adina Kilpatrick
-Date created: October 12th, 2013
-Description: This program automates the assignment of NMR data. 
-				The data is read in from a file and then the search will begin.
-				A uniform cost search is used if a 0 is given in the run command
-				A "puzzle building" search is completed if a 1 is given in the run command
-				
-				For further infromation on the project please see our paper:
-				http://www.micsymposium.org/mics2014/ProceedingsMICS_2014/mics2014_submission_35.pdf
-				or email joel.venzke@drake.edu
-
-				To run the code use the following command:
-				shell$ python search_project.py Path/To/Data/File.txt NumberOfSearchType
-"""
-
-
-import search_strategies2
-import time
-import sys
-
-# Error if not enough data is provided
-if len(sys.argv) < 2:
-	exit("NO INPUT DATA FILE OR MISSING SEARCH TYPE NUMBER\n\nPlease type: \nshell$ python search_project.py Path/To/Data/File.txt NumberOfSearchType\
-		\n\nSearch Type Numbers:\nUniform Cost: 0\nPuzzle Building: 1")
-
-# time and run search
-start = time.clock()
-search_strategies2.start_search(sys.argv[1],0)
-end = time.clock()
-
-print "Run Time:  " + str(end-start)

### 2015-04-03 search_project/search_strategies.py

@@ -28,10 +28,16 @@ takes in the tile set and characteristic lists
 returns tile list with place holder tiles
 """
 def generate_placeholders(tile_set, characteristic, nmrClass):
+	pro_count = 0
+	for i in characteristic:
+		if (i[2] ==12):
+			pro_count +=1
+			tile_set.append(Tile(-1,-1,-1,-1,nmrClass,pro=True))
+			# print tile_set[-1].amino_type[12]
 	gap = len(characteristic) - len(tile_set) # number of place holder tiles needed
 	if gap > 0:
 		for n in range(gap):
-			print "making"
+			# print "making"
 			tile_set.append(Tile(-1, -1, -1, -1, nmrClass)) # add place holder tiles to tile set
 	return tile_set
 
@@ -109,9 +115,12 @@ prints results to console
 take in a solution node and the number of nodes generated
 """
 def output_soultion(finalNode, nodeCount):
-	#prints best solution to console
-	# with open("../Results_Winter_2014-15/lmt_3sd.dat", "a") as dataFile:
+	# Uncomment to record results to data file for scripted runs
+	
+	# with open("../Results_Winter_2014-15/lmt_spring2015_data.dat", "a") as dataFile:
 	# 	dataFile.write(str(len(finalNode.characteristic)) + "\t" + str(nodeCount) + "\n")
+
+	#prints best solution to console
 	print "HERE IS THE BEST"
 	print "Cost: " + str(finalNode.get_cost())
 	print ""
@@ -171,7 +180,7 @@ def read_file(file_name):
 	tile_set_list = []
 	characteristic = []
 	jvm.start()
-	nmrClass = Classifier(jobject=serialization.read("models/decisiontable_3sd.model"))
+	nmrClass = Classifier(jobject=serialization.read("models/lmt_3sd.model"))
 	with open(file_name) as f: # opens file
 
 		# reads in characteristic protein sequence and coverts it to expected chemical shift values
@@ -193,7 +202,8 @@ def read_file(file_name):
 			if (d == "na"):
 				d = -1
 			# adds a new Tile to tile_set_list
-			tile_set_list.append(Tile(a, b, c, d, nmrClass)) 
+			if (not (a==-1 and b==-1 and c==-1 and d==-1)):
+				tile_set_list.append(Tile(a, b, c, d, nmrClass)) 
 	return tile_set_list, characteristic, nmrClass
 
 

### 2015-04-03 search_project/search_strategies1.py

@@ -1,280 +1,0 @@
-from Tile1 import Tile
-from Node1 import Node
-import sys
-import re
-import random
-from weka.core.converters import Loader
-from weka.classifiers import Classifier
-import weka.core.jvm as jvm
-import weka.core.serialization as serialization
-
-"""
-groups tiles together if there error is low enough
-takes in a list of assigned tiles
-returns a list of tiles and grouped tiles
-"""
-def find_matches(tiles):
-	outputNode = tiles
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	return outputNode
-
-
-"""
-Creates enough place holder tiles to do a full search
-takes in the tile set and characteristic lists
-returns tile list with place holder tiles
-"""
-def generate_placeholders(tile_set, characteristic, nmrClass):
-	pro_count = 0
-	for i in characteristic:
-		if (i[2] ==12):
-			pro_count +=1
-			tile_set.append(Tile(-1,-1,-1,-1,nmrClass,pro=True))
-			# print tile_set[-1].amino_type[12]
-	gap = len(characteristic) - len(tile_set) # number of place holder tiles needed
-	if gap > 0:
-		for n in range(gap):
-			# print "making"
-			tile_set.append(Tile(-1, -1, -1, -1, nmrClass)) # add place holder tiles to tile set
-	return tile_set
-
-
-"""
-Converts protein sequence strings into expected chemical shift values
-takes in a list of strings
-returns a list of lists that hold a carbon alpha and carbon beta value
-"""
-def letters_to_numbers(characteristic):
-	temp = []
-	new_characteristic = []
-	for ch in characteristic: # loop through the whole list
-		ch = ch.lower().strip() # deal with case problems
-		temp = []
-		# finds amino acid type and gets expected chemical shift data
-		# Values come from BRMB data. The exact values are the average
-		# Ca and Cb values as recorded on 01-22-2015
-		# Here is the link: http://www.bmrb.wisc.edu/ref_info/statsel.htm
[…]

### 2015-04-03 search_project/search_strategies2.py

@@ -1,280 +1,0 @@
-from Tile2 import Tile
-from Node2 import Node
-import sys
-import re
-import random
-from weka.core.converters import Loader
-from weka.classifiers import Classifier
-import weka.core.jvm as jvm
-import weka.core.serialization as serialization
-
-"""
-groups tiles together if there error is low enough
-takes in a list of assigned tiles
-returns a list of tiles and grouped tiles
-"""
-def find_matches(tiles):
-	outputNode = tiles
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	return outputNode
-
-
-"""
-Creates enough place holder tiles to do a full search
-takes in the tile set and characteristic lists
-returns tile list with place holder tiles
-"""
-def generate_placeholders(tile_set, characteristic, nmrClass):
-	pro_count = 0
-	for i in characteristic:
-		if (i[2] ==12):
-			pro_count +=1
-			tile_set.append(Tile(-1,-1,-1,-1,nmrClass,pro=True))
-			# print tile_set[-1].amino_type[12]
-	gap = len(characteristic) - len(tile_set) # number of place holder tiles needed
-	if gap > 0:
-		for n in range(gap):
-			# print "making"
-			tile_set.append(Tile(-1, -1, -1, -1, nmrClass)) # add place holder tiles to tile set
-	return tile_set
-
-
-"""
-Converts protein sequence strings into expected chemical shift values
-takes in a list of strings
-returns a list of lists that hold a carbon alpha and carbon beta value
-"""
-def letters_to_numbers(characteristic):
-	temp = []
-	new_characteristic = []
-	for ch in characteristic: # loop through the whole list
-		ch = ch.lower().strip() # deal with case problems
-		temp = []
-		# finds amino acid type and gets expected chemical shift data
-		# Values come from BRMB data. The exact values are the average
-		# Ca and Cb values as recorded on 01-22-2015
-		# Here is the link: http://www.bmrb.wisc.edu/ref_info/statsel.htm
[…]

### 2015-04-03 search_project/search_strategies_aStar.py

@@ -54,7 +54,7 @@ def generate_placeholders(tile_set, characteristic, nmrClass):
 	if gap > 0:
 		for n in range(gap):
 			# print "making"
-			tile_set.append(Tile(-1, -1, -1, -1, nmrClass, heuristic=1.9)) # add place holder tiles to tile set
+			tile_set.append(Tile(-1, -1, -1, -1, nmrClass, heuristic=0)) # add place holder tiles to tile set
 	return tile_set
 
 

### 2015-04-03 search_project/test_code.py

@@ -9,10 +9,10 @@ def getExpectedOutput(filename):
     return expected_output
 
 def getOutput(filename):
-    p = subprocess.Popen(["python", "search_project_aStar.py", "./Data/"+filename, "0"], stdout=subprocess.PIPE)
+    p = subprocess.Popen(["python", "search_project.py", "./Data/"+filename, "0"], stdout=subprocess.PIPE)
     out = p.communicate()
     outputList = out[0].split("\n")
-    output = "\n".join(outputList[7 : len(outputList) - 5])
+    output = "\n".join(outputList[4 : len(outputList) - 5])
     return output
 
 class TestSequenceFunctions(unittest.TestCase):
@@ -170,11 +170,11 @@ class TestSequenceFunctions(unittest.TestCase):
     def test_data35_txt(self):
         self.assertTrue(getOutput("data35.txt") == getExpectedOutput("data35.txt"))
 
-    # def test_data36_txt(self):
-    #     self.assertTrue(getOutput("data36.txt") == getExpectedOutput("data36.txt"))
+    def test_data36_txt(self):
+        self.assertTrue(getOutput("data36.txt") == getExpectedOutput("data36.txt"))
 
-    # def test_data37_txt(self):
-    #     self.assertTrue(getOutput("data37.txt") == getExpectedOutput("data37.txt"))
+    def test_data37_txt(self):
+        self.assertTrue(getOutput("data37.txt") == getExpectedOutput("data37.txt"))
 
     # def test_data38_txt(self):
     #     self.assertTrue(getOutput("data38.txt") == getExpectedOutput("data38.txt"))
@@ -187,6 +187,145 @@ class TestSequenceFunctions(unittest.TestCase):
 
     # def test_data41_txt(self):
     #     self.assertTrue(getOutput("data41.txt") == getExpectedOutput("data41.txt"))
+    
+    def test_Data_Fall_2014_1_txt(self):
+        self.assertTrue(getOutput("Data_Fall_2014_1.txt") == getExpectedOutput("Data_Fall_2014_1.txt"))
+
+    def test_Data_Fall_2014_2_txt(self):
[…]

### 2015-04-03 search_project/Node.py
removed old code from non aStar and left nodes for puzzle building

@@ -42,66 +42,41 @@ class Node(object):
 		new_nodes = []
 		char_num = len(self.placed_tiles) # location in the protein sequence
 
-		# If this Node contains a characteristic protein sequence we will use it
-		if(self.characteristic):
+		# loop through all tiles that have not been placed
+		for i in range(len(self.unplaced_tiles)):
 
-			# loop through all tiles that have not been placed
-			for i in range(len(self.unplaced_tiles)):
-
-				# check to see if current tile can be placed in this location
-				amino_type_list = self.unplaced_tiles[i].get_amino_type()
-				amino_Idx = self.characteristic[char_num][2]
-				if(amino_type_list[amino_Idx]==2.0):
-					temp_ut = list(self.unplaced_tiles) 
-					placed_tile = temp_ut.pop(i) 
-					temp_pt = list(self.placed_tiles) 
-					temp_pt.append(placed_tile)
-
-					# add child node to list of new_nodes
-					new_nodes.append(Node(temp_ut, temp_pt, self.cost, self.characteristic, self.char_cost, self.order_cost))
-
-				elif(amino_type_list[amino_Idx] > 0.004):
-
-					# copy unplaced and placed tile lists, remove tile from list and add it to the placed tile list
-					temp_ut = list(self.unplaced_tiles) 
-					placed_tile = temp_ut.pop(i) 
-					temp_pt = list(self.placed_tiles) 
-					temp_pt.append(placed_tile)
-
-					# Calculated cost 
-					if(self.placed_tiles): # not the first tile
-						temp_char_cost = placed_tile.get_error(self.characteristic[char_num])
-						temp_order_cost = self.placed_tiles[-1].compare_below(placed_tile)
-					else: # first tile being placed 
-						temp_char_cost = placed_tile.get_error(self.characteristic[char_num])
-						temp_order_cost = 0 # no before it to compare to
-					c = temp_order_cost + temp_char_cost
-
-					# add child node to list of new_nodes
-					new_nodes.append(Node(temp_ut, temp_pt, self.cost + c, self.characteristic,self.char_cost+temp_char_cost, self.order_cost+temp_order_cost))
-			return new_nodes
-
-		# Account for nodes that do not have a characteristic protein sequence
-		else:
-			for i in range(len(self.unplaced_tiles)):
[…]

### 2015-04-03 search_project/Tile.py

@@ -19,33 +19,15 @@ class Tile(object):
     d: carbon beta value for residue i-1
     tile_list: A list of tiles that have been grouped together
     """
-    def __init__(self,a=0 ,b=0 ,c=0 ,d=0, model=None, tile_list=[], pro=False):
-        if (not tile_list): # not given a tile list
-            self.a = float(a)
-            self.b = float(b)
-            self.c = float(c)
-            self.d = float(d)
-            self.tile_list = []
-            self.char_weight = .1
-            self.order_weight = 1
-            self.tile_list_cost = 0
-            self.amino_type = self.calculate_amino_type(model,pro)
-        else: # create a tile form the tile_list
-            self.tile_list = tile_list
-            self.amino_type = 0
-            self.char_weight = .1
-            self.order_weight = 1
-            
-            #assigns a and b of the last tile to the a and b value of combined tile
-            self.a = float(tile_list[-1].a)
-            self.b = float(tile_list[-1].b)
-
-            #assigns c and d of the fist tile to the c and d value of the combined tiles
-            self.c = float(tile_list[0].c)
-            self.d = float(tile_list[0].d)
-
-            # calculate the cost of the tile
-            self.tile_list_cost = self.calculate_tile_list_cost()
+    def __init__(self,a=0 ,b=0 ,c=0 ,d=0, model=None, pro=False):
+        self.a = float(a)
+        self.b = float(b)
+        self.c = float(c)
+        self.d = float(d)
+        self.tile_list = []
+        self.char_weight = .1
+        self.order_weight = 1
+        self.amino_type = self.calculate_amino_type(model,pro)
 
 
     """
@@ -66,21 +48,7 @@ class Tile(object):
         myDataset = loader.load_file("weka/testingthisthingout.arff")
         myDataset.set_class_index(0)
         i.set_dataset(myDataset)
-        # print model.distribution_for_instance(i)
         return model.distribution_for_instance(i)
-
-
-    """
-    calculate the cost inside the list of tiles
-    """
-    def calculate_tile_list_cost(self):
-        last = len(self.tile_list)
-        cost = 0
-        for i in xrange(last): # loop though tiles
-            if (i==last-1): # if last tile return cost
-                return cost
-            else: # calculated cost of 
-                cost += self.tile_list[i].compare_below(self.tile_list[i+1])
 
     """
     Calculates order cost

### 2015-04-03 search_project/search_strategies.py

@@ -8,19 +8,6 @@ from weka.classifiers import Classifier
 import weka.core.jvm as jvm
 import weka.core.serialization as serialization
 
-"""
-groups tiles together if there error is low enough
-takes in a list of assigned tiles
-returns a list of tiles and grouped tiles
-"""
-def find_matches(tiles):
-	outputNode = tiles
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	return outputNode
-
 
 """
 Creates enough place holder tiles to do a full search
@@ -129,36 +116,13 @@ def output_soultion(finalNode, nodeCount):
 	print "Order Cost:  " + str(finalNode.get_order_cost())
 	print "Nodes: " + str(nodeCount)
 
-
-"""
-This search will select 20 random tiles to assign, run a uniform cost search and then group tiles until a final state is found
-Takes in a list of tiles 
-Returns a single tile that contains a lits of tiles
-"""
-def puzzle_building_search(allTiles):
-	while len(allTiles) > 1: # while we have more than one tile
-
-		# get up to 20 random tiles from the list
-		tempTileArray = []
-		if (len(allTiles)>20):
-			for i in xrange(20):
-				randomNum = random.ranint(0,len(allTiles)-1)
-				tempTileArray.append(allTiles.pop(randomNum))
-		else: 
-			tempTileArray = allTiles
-
-		# preform a uniform cost search
-		tempNode = Node(tempTileArray,[],0,[],0,0) # make a starting node for a uniform cost search
-		outputNode, count = uniform_cost(tempNode) # preform search
-
-		# group tiles together 
-		newList = find_matches(outputNode.placed_tiles)
-
-		# add tiles back onto the list of tiles
-		for i in len(newList):
-			allTiles.append(newList[i])
-	return allTiles[0]
-
+def puzzle_building_search(root):
+	#make this maintain the list of nodes being used to start and end the uniform cost search
+	# uniform cost search may want to have 3 variables: 
+	# one for the frontier (some changes will need to make this happen)
+	# one for the depth needed for termination of that layer of the search (the number I talked about in the meeting)
+	# one for the number of nodes to return at the completion of the search
+	return root
 
 """
 Reads in the data from the provided file

### 2015-04-03 search_project/Node_aStar.py
cleaned up puzzle building in aStar search

@@ -43,66 +43,41 @@ class Node(object):
 		new_nodes = []
 		char_num = len(self.placed_tiles) # location in the protein sequence
 
-		# If this Node contains a characteristic protein sequence we will use it
-		if(self.characteristic):
+		# loop through all tiles that have not been placed
+		for i in range(len(self.unplaced_tiles)):
 
-			# loop through all tiles that have not been placed
-			for i in range(len(self.unplaced_tiles)):
-
-				# check to see if current tile can be placed in this location
-				amino_type_list = self.unplaced_tiles[i].get_amino_type()
-				amino_Idx = self.characteristic[char_num][2]
-				if(amino_type_list[amino_Idx]==2.0):
-					temp_ut = list(self.unplaced_tiles) 
-					placed_tile = temp_ut.pop(i) 
-					temp_pt = list(self.placed_tiles) 
-					temp_pt.append(placed_tile)
-
-					# add child node to list of new_nodes
-					new_nodes.append(Node(temp_ut, temp_pt, self.cost, self.characteristic, self.char_cost, self.order_cost, heuristic=self.heuristic_cost))
-
-				elif(amino_type_list[amino_Idx] > 0.004):
-					# copy unplaced and placed tile lists, remove tile from list and add it to the placed tile list
-					temp_ut = list(self.unplaced_tiles) 
-					placed_tile = temp_ut.pop(i) 
-					temp_pt = list(self.placed_tiles) 
-					temp_pt.append(placed_tile)
-
-					# Calculated cost 
-					if(self.placed_tiles): # not the first tile
-						temp_char_cost = placed_tile.get_error(self.characteristic[char_num])
-						temp_order_cost = self.placed_tiles[-1].compare_below(placed_tile)
-					else: # first tile being placed 
-						temp_char_cost = placed_tile.get_error(self.characteristic[char_num])
-						temp_order_cost = 0 # no before it to compare to
-					c = temp_order_cost + temp_char_cost - placed_tile.heuristic_cost
-
-					# add child node to list of new_nodes
-					new_nodes.append(Node(temp_ut, temp_pt, self.cost + c, self.characteristic,self.char_cost+temp_char_cost, self.order_cost+temp_order_cost,heuristic=self.heuristic_cost-placed_tile.heuristic_cost))
-			return new_nodes
-
-		# Account for nodes that do not have a characteristic protein sequence
-		else:
[…]

### 2015-04-03 search_project/Tile_aStar.py

@@ -19,34 +19,16 @@ class Tile(object):
     d: carbon beta value for residue i-1
     tile_list: A list of tiles that have been grouped together
     """
-    def __init__(self,a=0 ,b=0 ,c=0 ,d=0, model=None, tile_list=[], pro=False, heuristic=0.0):
-        if (not tile_list): # not given a tile list
-            self.a = float(a)
-            self.b = float(b)
-            self.c = float(c)
-            self.d = float(d)
-            self.tile_list = []
-            self.char_weight = .1
-            self.order_weight = 1
-            self.tile_list_cost = 0
-            self.heuristic_cost = heuristic
-            self.amino_type = self.calculate_amino_type(model,pro)
-        else: # create a tile form the tile_list
-            self.tile_list = tile_list
-            self.amino_type = 0
-            self.char_weight = .1
-            self.order_weight = 1
-            
-            #assigns a and b of the last tile to the a and b value of combined tile
-            self.a = float(tile_list[-1].a)
-            self.b = float(tile_list[-1].b)
-
-            #assigns c and d of the fist tile to the c and d value of the combined tiles
-            self.c = float(tile_list[0].c)
-            self.d = float(tile_list[0].d)
-
-            # calculate the cost of the tile
-            self.tile_list_cost = self.calculate_tile_list_cost()
+    def __init__(self,a=0 ,b=0 ,c=0 ,d=0, model=None, pro=False, heuristic=0.0):
+        self.a = float(a)
+        self.b = float(b)
+        self.c = float(c)
+        self.d = float(d)
+        self.tile_list = []
+        self.char_weight = .1
+        self.order_weight = 1
+        self.heuristic_cost = heuristic
+        self.amino_type = self.calculate_amino_type(model,pro)
 
 
     """
@@ -70,18 +52,6 @@ class Tile(object):
         # print model.distribution_for_instance(i)
         return model.distribution_for_instance(i)
 
-
-    """
-    calculate the cost inside the list of tiles
-    """
-    def calculate_tile_list_cost(self):
-        last = len(self.tile_list)
-        cost = 0
-        for i in xrange(last): # loop though tiles
-            if (i==last-1): # if last tile return cost
-                return cost
-            else: # calculated cost of 
-                cost += self.tile_list[i].compare_below(self.tile_list[i+1])
 
     """
     Calculates order cost

### 2015-04-03 search_project/search_strategies_aStar.py

@@ -23,19 +23,6 @@ def calculate_heuristic(tile_set, characteristic):
 				greatest = temp
 		tile.heuristic_cost = temp
 
-"""
-groups tiles together if there error is low enough
-takes in a list of assigned tiles
-returns a list of tiles and grouped tiles
-"""
-def find_matches(tiles):
-	outputNode = tiles
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	# lots of work needed =================================================================================
-	return outputNode
-
 
 """
 Creates enough place holder tiles to do a full search
@@ -152,27 +139,11 @@ Takes in a list of tiles
 Returns a single tile that contains a lits of tiles
 """
 def puzzle_building_search(allTiles):
-	while len(allTiles) > 1: # while we have more than one tile
-
-		# get up to 20 random tiles from the list
-		tempTileArray = []
-		if (len(allTiles)>20):
-			for i in xrange(20):
-				randomNum = random.ranint(0,len(allTiles)-1)
-				tempTileArray.append(allTiles.pop(randomNum))
-		else: 
-			tempTileArray = allTiles
-
-		# preform a uniform cost search
-		tempNode = Node(tempTileArray,[],0,[],0,0) # make a starting node for a uniform cost search
-		outputNode, count = uniform_cost(tempNode) # preform search
-
-		# group tiles together 
-		newList = find_matches(outputNode.placed_tiles)
-
-		# add tiles back onto the list of tiles
-		for i in len(newList):
-			allTiles.append(newList[i])
+	#make this maintain the list of nodes being used to start and end the uniform cost search
+	# uniform cost search may want to have 3 variables: 
+	# one for the frontier (some changes will need to make this happen)
+	# one for the depth needed for termination of that layer of the search (the number I talked about in the meeting)
+	# one for the number of nodes to return at the completion of the search
 	return allTiles[0]
 
 

### 2015-04-03 search_project/test_code.py

@@ -9,10 +9,10 @@ def getExpectedOutput(filename):
     return expected_output
 
 def getOutput(filename):
-    p = subprocess.Popen(["python", "search_project.py", "./Data/"+filename, "0"], stdout=subprocess.PIPE)
+    p = subprocess.Popen(["python", "search_project_aStar.py", "./Data/"+filename, "0"], stdout=subprocess.PIPE)
     out = p.communicate()
     outputList = out[0].split("\n")
-    output = "\n".join(outputList[4 : len(outputList) - 5])
+    output = "\n".join(outputList[7 : len(outputList) - 5])
     return output
 
 class TestSequenceFunctions(unittest.TestCase):

### 2015-04-03 search_project/test_code.py
changed test code to run for non aStar

@@ -9,10 +9,10 @@ def getExpectedOutput(filename):
     return expected_output
 
 def getOutput(filename):
-    p = subprocess.Popen(["python", "search_project_aStar.py", "./Data/"+filename, "0"], stdout=subprocess.PIPE)
+    p = subprocess.Popen(["python", "search_project.py", "./Data/"+filename, "0"], stdout=subprocess.PIPE)
     out = p.communicate()
     outputList = out[0].split("\n")
-    output = "\n".join(outputList[7 : len(outputList) - 5])
+    output = "\n".join(outputList[4 : len(outputList) - 5])
     return output
 
 class TestSequenceFunctions(unittest.TestCase):

### 2015-04-04 Papers_and_Presentations/paper_spring_2015/paper.tex
Paper changes

@@
 \usepackage{setspace}
+\usepackage{times}
 \usepackage{float}
@@
 
-\title{\textbf{Utilizing Machine Learning to Accelerate Automated Assignment of Backbone NMR Data}}
+\title{Utilizing Machine Learning to Accelerate Automated Assignment of Backbone NMR Data}
 
-\author{Joel Venzke, David Mascharka, Paxten Johnson, Rachel Davis, Katie Roth, Leah Robison, Adina Kilpatrick and Timothy Urness*}
-\affil{Department of Mathematics and Computer Science and the Department of Physics and Astromony,\\Drake University, Des Moines, Iowa\\\vspace{0.5cm}*Joel Venzke: joel.venzke@drake.edu\\Timothy Urness: timothy.urness@drake.edu}
+\author{\textit{Joel Venzke, David Mascharka, Paxten Johnson, Rachel Davis, Katie Roth, Leah Robison, Adina Kilpatrick and Timothy Urness*}}
+\affil{Department of Mathematics and Computer Science, Department of Physics and Astromony,\\Drake University, Des Moines, Iowa\\\vspace{0.5cm}*Joel Venzke: joel.venzke@drake.edu\\Timothy Urness: timothy.urness@drake.edu}
+
+\makeatletter
+\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
+\begin{flushleft}
+\huge{\@title}
+
+\normalsize\textit{\@author}
+\end{flushleft}\egroup
+}
+\makeatother
 
@@
 
-\begin{abstract}
+\noindent\textbf{ABSTRACT}\\
 Nuclear magnetic resonance (NMR) spectroscopy is a powerful method for determining three-dimensional structures of biomolecules, including proteins.
-In a critical step of the structure determination process for proteins, measured NMR values are assigned to specific amino acids in the protein primary sequence.
+The protein structure determination process requires measured NMR values to be assigned to specific amino acids in the protein primary sequence.
 Unfortunately, current manual techniques for the assignment of NMR data are time-consuming and susceptible to error.
 Many algorithms have been developed to automate the process, with various strengths and weaknesses.
-The algorithm described in this paper works to overcome the obstacles others have met by utilizing machine learning to predict amino acid type, thereby increasing assignment speed.
-The program also generates place-holders to accommodate missing data and recurring amino acids with unique chemical characteristics, namely proline.
-This approach is able to speed up the process of assignment by almost three orders of magnitude while maintaining high accuracy when compared to a previously assigned set.
-\end{abstract}
+The algorithm described in this paper addresses the challenges of previous programs by utilizing machine learning to predict amino acid type, thereby increasing assignment speed.
+The program also generates place-holders to accommodate missing data and amino acids with unique chemical characteristics, namely proline through machine learning and residue-type tagging.
+This approach is able to greatly speed up the process of assignment, while maintaining high accuracy.
 
 \noindent\textbf{KEYWORDS}\\
-Protein Sequencing, Machine Learning, NMR, Artificial Intelligence, Proteins, Bioinformatics
+Chemical Shift, Machine Learning, NMR, Artificial Intelligence, Proteins, Bioinformatics
 
 \noindent \textbf{INTRODUCTION}\\
-NMR spectroscopy is a powerful method for obtaining atomic-resolution three-dimensional protein structures, as well as assessing changes in protein conformations or motions due to mutations or interactions with ligands or other biomolecules.
+\indent NMR spectroscopy is a powerful method for obtaining atomic-resolution three-dimensional protein structures, as well as assessing changes in protein conformations or motions due to mutations or interactions with ligands or other biomolecules.
 Determining a protein's structure is essential for understanding its function and alterations in function, which often lead to disease.
@@
 \noindent \textbf{BACKGROUND}\\
-NMR spectroscopy experiments generate information on several variables that can be used in the determination of protein structures.
+\indent NMR experiments generate information on several variables that can be used in the determination of protein structures.
 In particular, essential information is provided by the chemical shifts of NMR-active nuclei present in proteins, including hydrogen and isotopes of carbon and nitrogen.
@@
 
-Triple resonance experiments on hydrogen, nitrogen and carbon nuclei are the method of choice for proteins and other large biomolecules, because they can greatly decrease the amount of spectral overlap in data.
-Typical experiments for the assignment of backbone resonances include HNCA, HN(CO)CA, HNCACB, and CBCA(CO)NH or HN(CO)CACB2.
+\indent Triple resonance experiments on hydrogen, nitrogen and carbon nuclei are the method of choice for proteins and other large biomolecules, because they can greatly decrease the amount of spectral overlap in data.
+Typical experiments for the assignment of backbone resonances include HNCA, HN(CO)CA, HNCACB, and CBCA(CO)NH or HN(CO)CACB \cite{cavanagh}.
 These experiments transfer magnetization over the protein polypeptide chain, and thus connect different spin systems through covalent bonds.
@@
 All these experiments produce NMR spectra with common H-N resonance correlations, and provide connectivities between neighboring residues.
-For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_{\alpha}$ and $C_{\beta}$ nuclei of each residue in the protein chain (residue i), as well as the immediately preceding residue (residue $i-1$).
+For example, the HNCACB experiment identifies the chemical shifts corresponding to the $C_{\alpha}$ and $C_{\beta}$ nuclei of each residue in the protein chain (residue $i$), as well as the immediately preceding residue (residue $i-1$).
 In this experiment, resonances corresponding to residue $i$ can usually be distinguished from the $i-1$ values due to their higher intensity.
@@
 \\\\
-\noindent \textbf{SEQUENTIAL ASSIGNMENT STRATEGIES}
-\begin{figure}[b]
-	\caption{A sequence can be placed in order by matching $C_{\alpha}$ and $C_{\beta}$ values}
-	\label{fig:joel_figure}
-	\begin{center}
-		\includegraphics[keepaspectratio=true, width=0.7\textwidth]{residue_thingy}
-	\end{center}
-\end{figure}
-
-The sequential assignment of backbone chemical shifts can be done manually or in an automated fashion.
+\noindent \textbf{SEQUENTIAL ASSIGNMENT STRATEGIES}\\
+\indent The sequential assignment of backbone chemical shifts can be done manually or in an automated fashion.
 Both approaches follow similar strategies.
 The process starts by identifying the chemical shifts of $i$ and $i-1$ residues from a set of three-dimensional NMR experiments.
-In the early days of NMR spectroscopy, these chemical shifts were measured using a ruler \cite{guntert}.
-Nowadays, many computer programs, such as NMRPipe \cite{nmrpipe} and SPARKY \cite{goddard}, can be used to process, analyze and visualize NMR data.
+Many computer programs, such as NMRPipe \cite{nmrpipe} and SPARKY \cite{goddard}, can be used to process, analyze and visualize NMR data.
 After grouping chemical shifts into spin systems, sequential spin systems are linked into increasingly larger segments by matching $i-1$ and $i$ values.
@@
 
-When performed manually, the assignment process is time-consuming and prone to errors.
+\begin{figure}[!h]
+	\begin{center}
+		\includegraphics[keepaspectratio=true, width=0.7\textwidth]{residue_thingy}
+	\caption{Sequential residues are linked by matching $i$ and $i-1$ chemical shifts}
+	\label{fig:joel_figure}
+	\end{center}
+\end{figure}
+
+\indent When performed manually, the assignment process is time-consuming and prone to errors.
 If chemical shifts values overlap, multiple matches between $i$ and $i-1$ values are possible.
@@
 
-Our algorithm utilizes elements from these existing programs, such as cost analysis, sorting amino acids into groups.
-Our algorithm employs novel concepts from machine learning to accelerate the assignment process.
+\indent Our algorithm utilizes elements from these existing programs, such as cost analysis and sorting amino acids into groups but employs novel concepts from machine learning to accelerate the assignment process.
 \\\\
 \noindent\textbf{MACHINE LEARNING}\\
-Machine learning provides algorithms that learn from attributes in the input data to increase performance.
+\indent Machine learning provides algorithms that learn from attributes in the input data to increase performance.
 Supervised learning, a field of machine learning, builds a model based on numerous data elements and their respective labels.
@@
 
-Machine learning offers a natural solution to the problem of determining amino acid type from NMR chemical shift values.
-The overlap between the normal range of $C_{\alpha}$ and $C_{\beta}$ values between many amino acids makes it difficult to infer the type of residue based solely on chemical shift information.
+\indent Machine learning offers a natural solution to the problem of determining amino acid type from NMR chemical shift values.
+The overlap in the normal range of $C_{\alpha}$ and $C_{\beta}$ values among many amino acids makes it difficult to infer the type of residue based solely on chemical shift information.
 Machine learning algorithms offer a unique approach to this problem and achieve excellent accuracy.
 
-There are several supervised machine learning algorithms that can be applied to improve automated assignment strategies.
+\indent There are several supervised machine learning algorithms that can be applied to improve automated assignment strategies.
 The J4.8 algorithm \cite{j48_algorithm} builds a decision tree model.
@@
 
-The Logistic Model Tree, or LMT \cite{lmt_algorithm}, is another tree-based algorithm.
+\indent The Logistic Model Tree, or LMT \cite{lmt_algorithm}, is another tree-based algorithm.
 In contrast to the J4.8 algorithm, LMT constructs a tree with logistic regression functions at each branch rather than an attribute test.
-Logistic regression attempts to model class probabilities with linear functions (Hall).
+Logistic regression attempts to model class probabilities with linear functions.
 The weights used for each function can be learned to split each class in a way somewhat analogous to the split in J4.8 described above.
 
-The Decision Table algorithm \cite{decisiontable_algorithm} is comprised of a set of features and a set of labeled data.
+\indent The Decision Table algorithm \cite{decisiontable_algorithm} is comprised of a set of features and a set of labeled data.
 To classify a new datapoint, the set of labeled data is searched for a match with the new point, considering only the features in the feature set.
@@
 \noindent\textbf{PROGRAM DEVELOPMENT}\\
-Our goal is to create an automated program for the assignment of protein backbone chemical shifts that can deliver quality results in a small amount of time without the use of a supercomputer.
+\indent Our goal is to create an automated program for the assignment of protein backbone chemical shifts that can deliver quality results in a small amount of time without the use of a supercomputer.
 Our program implements group sorting, machine learning, filtered amino acid selection, and careful cost calculations.
@@
 
-Before the algorithm begins the assignment process, machine learning is used to build a model for predicting amino acid type.
+\indent Before the algorithm begins the assignment process, machine learning is used to build a model for predicting amino acid type.
 After the model is trained, the pre-processing component of the algorithm (steps 1 to 3) begins.
@@
 \noindent\textit{MACHINE LEARNING DATA COLLECTION}\\
-The training dataset for the machine learning algorithm was obtained from the Biological Magnetic Resonance Bank (BMRB), a database of NMR chemical shifts hosted by the University of Wisconsin at Madison \cite{biomagresbank}.
+\indent The training dataset for the machine learning algorithm was obtained from the Biological Magnetic Resonance Bank (BMRB), a database of NMR chemical shifts hosted by the University of Wisconsin at Madison \cite{biomagresbank}.
 We initially identified 9,736 datasets containing chemical shifts for the $C_{\alpha}$ and $C_{\beta}$ resonances of 689,977 residues.
@@
 \noindent\textit{PRE-PROCESSING}\\
-Step 1 of our algorithm consists of reading the chemical shift values and the protein amino acid sequence from an input file.
-We use the $C_{\alpha}$ and $C_{\beta}$ values for each pair of $i$ and $i-1$ residues to create an object we will refer to as a tile.
+\indent Step 1 of our algorithm consists of reading the chemical shift values and the protein amino acid sequence from an input file.
+We use the $C_{\alpha}$ and $C_{\beta}$ values for each pair of $i$ and $i-1$ residues to create an object we will refer to as a \textit{tile}.
 A tile holds all the available chemical shift information corresponding to a single residue in the protein sequence to be assigned.
@@
 
-Step 2 of the algorithm converts the protein primary sequence into $C_{\alpha}$ and $C_{\beta}$ chemical shift values, using statistics available in BMRB.
+\indent Step 2 of the algorithm converts the protein primary sequence into $C_{\alpha}$ and $C_{\beta}$ chemical shift values, using statistics available in BMRB.
 These statistics provide average chemical shift values for each of the twenty common amino acids found in proteins.
 For example, we assign alanine a $C_{\alpha}$ chemical shift of 53.19 ppm and a $C_{\beta}$ chemical shift of 18.96 ppm.
-Next, the algorithm searches the protein sequence for prolines, as prolines lack H-N spin systems.
-As a consequence, HNCACB and CBCA(CO)NH experiments do not provide $C_{\alpha}$ and $C_{\beta}$ chemical shifts for this residue.
+Next, the algorithm searches the protein sequence for prolines.
+As prolines lack H-N spin systems, HNCACB and CBCA(CO)NH experiments do not provide $C_{\alpha}$ and $C_{\beta}$ chemical shifts for this residue.
 Special tiles, designed to specifically identify the proline residue, are created to handle this case.
@@
 
-Step 3 assigns possible amino acid types to each tile.The $C_{\alpha}$ and $C_{\beta}$ values for residue $i$ in each tile are processed by our machine learning model, producing a list of probabilities that a tile represents a certain amino acid.
+\indent Step 3 assigns possible amino acid types to each tile.The $C_{\alpha}$ and $C_{\beta}$ values for residue $i$ in each tile are processed by our machine learning model, producing a list of probabilities that a tile represents a certain amino acid.
 The probabilities correspond to confidence levels used for filtering during the assignment process.
 
-Preprocessing the dataset takes a minimal amount of time (less than a second on a standard laptop) and drastically reduces the time required to assign the chemical shifts without affecting accuracy.
+\indent Preprocessing the dataset takes a minimal amount of time (less than a second on a standard laptop) and drastically reduces the time required to assign the chemical shifts without affecting accuracy.
 The search for the optimal assignment then begins.
@@
 \noindent\textit{THE SEARCH}\\
-The algorithm initiates an intelligent search through filtered combinations of all possible chemical shifts.
-The search begins by placing the first tile, which is selected based on a filtering process.
+\indent The algorithm initiates an intelligent search through filtered combinations of all possible chemical shifts.
+The search begins by placing the first tile, which is selected based on the filtering process.
 Only tiles that could correspond to the first amino acid based on a confidence level threshold (0.4\% match or better) are placed at residue one.
@@
 
-At this point, a “cost” of assignment is generated.
+\indent At this point, a “cost” of assignment is generated.
 The cost of placing a tile consists of two parts: (1) the difference between the tile's residue $i-1$ values and the previous tile's residue $i$ values, and (2) the difference between the residue $i$ values and the values predicted from the protein sequence.
 In the case of blank and proline tiles, a fixed cost is added instead of  the above calculation.
-Since initially only one tile is placed, the cost is based solely on a comparison to the protein sequence, and the search moves on to step 5.
+When the first tile is placed, the cost is based solely on a comparison to the protein sequence, and the search moves on to step 5.
 
-In step 5, the algorithm selects the assignment with the lowest cost to continue the search process.
+\indent In step 5, the algorithm selects the assignment with the lowest cost to continue the search process.
 A solution is reached when all tiles have been placed in an assignment.
@@
 
-In the final step the search records the solution. The solution assignment along with the performance (the number of possible assignments searched) is output. Then the algorithm terminates. 
+\indent In the final step the search records the solution. The solution assignment along with the performance (the number of possible assignments searched) is output. Then the algorithm terminates. 
 \\\\
 \noindent\textbf{RESULTS}\\
-The chemical shift dataset used in this study consisted of $C_{\alpha}$ and $C_{\beta}$ values for the 62-residue long C-terminal domain of the Tfg1 subunit of the yeast transcription factor TFIIF.
+\indent The chemical shift dataset used in this study consisted of $C_{\alpha}$ and $C_{\beta}$ values for the 62-residue long C-terminal domain of the Tfg1 subunit of the yeast transcription factor TFIIF.
 The chemical shifts were previously obtained by Kilpatrick et al.
 from HNCACB and CBCA(CO)NH experiments, and manually assigned to 99\% completeness\cite{kilpatrick}.
-The chemical shift dataset was cut into sub-sections, randomized, and used for algorithmic analysis.
+The chemical shift dataset was divided into sub-sections, randomized, and used for algorithmic analysis.
 
-The results of assigning this dataset with different filtering methods are shown in Figure~\ref{fig:figure1}.
-Each of the tests described in Figure~\ref{fig:figure1} follow a smooth trend, as opposed to a highly irregular trend which would indicate an impediment in the processing and sequencing of data.
+\indent The results of assigning this dataset with different filtering methods are shown in Figure~\ref{fig:figure1}.
+Each of the tests described in Figure~\ref{fig:figure1} follows a smooth trend, as opposed to a highly irregular trend which would indicate an impediment in the processing and assignment of data.
 A comparison of the methods indicates that our filtering process results in a significant decrease in number of generated nodes compared to an unfiltered generic search algorithm.
@@
 The graph indicates that the LMT machine learning algorithm has the best performance, outperforming the unfiltered method by almost two orders of magnitude, without loss of assignment accuracy.
-LMT established itself as best because it was able to assign all 62 residues within forty-five minutes, whereas the other filters were unable to complete the full assignment within a 12 hour time limit.
+LMT was able to assign all 62 residues within forty-five minutes, whereas the other filters were unable to complete the full assignment within a 12 hour time limit.
 The LMT model not only accelerates assignment, but also allows for larger datasets to be assigned in the same amount of time.
@@
 \begin{figure}[H]
+	\begin{center}
+		\resizebox{!}{0.6\textwidth}{\input{ProFix_full.tex}}
 	\caption{Impact of filtering methods on assignment time.
-Number of nodes (y-axis) are plotted as a function of number of residues (protein sequence length) used in the assignment (x-axis).
+Number of nodes (y-axis) is plotted as a function of number of residues (protein sequence length) used in the assignment (x-axis).
 The search without machine learning filtering is depicted in blue.
@@
 	\label{fig:figure1}
-	\begin{center}
-		\resizebox{!}{0.6\textwidth}{\input{ProFix_full.tex}}
 	\end{center}
@@
 
-The impact of proline identification on our algorithm's performance is shown in Figure~\ref{fig:figure2}.
+\indent The impact of proline identification on our algorithm's performance is shown in Figure~\ref{fig:figure2}.
+In the sequence of the studied protein, residue 33 is a proline, for which chemical shifts are missing.
 The same unfiltered and LMT data from Figure~\ref{fig:figure1} is plotted for comparison.
-The large jump in assignment time between 32 and 33 residue long sequences shows the performance impact of missing data on performance without filtering and using the LMT model for filtering.
-In the sequence of the studied protein, residue 33 is a proline, for which chemical shifts are missing.
+The large jump in assignment time between residues 32 and 33 shows the performance impact of missing data on performance without filtering and using the LMT model for filtering.
 If the algorithm identifies and handles prolines as a special case, only one more node is generated for the 33-residue long sequence.
@@
 With proline checking, prolines are no longer problematic to the assignment process.
-This indicates that our algorithm can accurately reproduce assignments with reasonably fast assignment times even when chemical shift data is missing.
+This indicates that our algorithm can accurately obtain assignments with reasonably fast assignment times even when chemical shift data is missing.
 
 \begin{figure}[H]
-	\caption{Impact of proline identification on assignment time.
-Number of nodes (y-axis) as a function of number of residues used in the assignment (x-axis).
-Blue shows the search with proline checking and without machine learning filtering.
-Similarly, the search without either proline checking or machine learning filtering is depicted in purple.
-The search with proline checking and LMT machine learning filtering is depicted in red.
-Not utilizing proline checking, but using LMT machine learning filtering is depicted in green.}
-	\label{fig:figure2}
 	\begin{center}
 		\resizebox{!}{0.6\textwidth}{\input{pro_compare.tex}}
+	\caption{Impact of proline identification on assignment time.
+Number of nodes (y-axis) is plotted as a function of number of residues used in the assignment (x-axis).
+Green shows the search with proline checking and without machine learning filtering.
+Similarly, the search without either proline checking or machine learning filtering is depicted in red.
+The search with proline checking and LMT machine learning filtering is depicted in pink.
+Not utilizing proline checking, but using LMT machine learning filtering is depicted in blue.}
+	\label{fig:figure2}
 	\end{center}
@@
 
-Our algorithm with LMT filtering and proline identification can complete the 62-residue assignment in approximately 40 minutes on a 2.3 GHz Intel Core i7 processor with 8Gb of RAM.
+\indent Our algorithm with LMT filtering and proline checking can complete the 62-residue assignment in approximately 40 minutes on a 2.3 GHz Intel Core i7 processor with 8Gb of RAM.
 The LMT model with proline checking can complete the assignment of a 43-residue long sub-sequence in less than 1 second, compared to 27, 29 and 30 seconds without filtering, using a Decision Table for filtering and using the J4.8 model for filtering, respectively.
@@
 \noindent\textbf {CONCLUSIONS AND FUTURE DIRECTIONS}\\
-Our algorithm has made significant advances in the field of automated assignment of protein backbone chemical shifts.
+\indent Our algorithm has made significant advances in the field of automated assignment of protein backbone chemical shifts.
 We implemented machine learning to filter NMR data in order to reduce the branching factor in a search-based algorithm.
-This increased our assignment rate by approximately three orders of magnitude while still maintaining the accuracy of a manually assigned solution.
+This increased our assignment rate by approximately three orders of magnitude while still maintaining the accuracy of the solution.
 
-The use of proline checking and the utilization of machine learning to filter data has shown to be extremely effective in accelerating the assignment.
+\indent The use of proline checking and the utilization of machine learning to filter data has shown to be extremely effective in accelerating the assignment.
 Constrained within the same period of time, reducing the assignment time by 3 orders of magnitude allows for twice as many residues to be assigned.
@@
 
-One of our main focuses for the future is handling missing data in a more efficient manner.
+\indent One of our main focuses for the future is handling missing data in a more efficient manner.
 By examining characteristics of the amino acids in the sequence, we hope to predict where missing data will end up in the final assignment.
 This would reduce the number of assignments attempted.
-Furthermore, we will look to improve the overall performance of our algorithm by optimizing cost calculations and investigate sequencing via parallel processing.
+Furthermore, we will work to improve the overall performance of our algorithm by optimizing cost calculations and investigate assignment via parallel processing.
 
-We are currently measuring the backbone chemical shifts of a protein previously uncharacterized by NMR spectroscopy.
+\indent We are currently measuring the backbone chemical shifts of a protein previously uncharacterized by NMR spectroscopy.
 This new dataset will include additional chemical shifts that can be used in the assignment process, such as the backbone carbonyl and H-alpha values.
@@
 \\
-The authors of this paper would like to thank Drake University for being a conducive space to research, John Emmons for initiating this research.
-
-\noindent\textbf {REFERENCES}
-\clearpage
-%\nocite{*}
+\indent The authors of this paper would like to thank Drake University for being a conducive space to research, and John Emmons for initiating this research.
+\renewcommand{\refname}{\normalfont\selectfont\large \textbf{REFERENCES}}
 \bibliographystyle{achemso}
@@
 \noindent\textbf{ABOUT THE STUDENT AUTHORS}\\
-\indent Joel Venzke is a junior pursuing a B.S.
+\noindent Joel Venzke is a junior pursuing a B.S.
 in Physics, Computer Science, and  Mathematics.
@@
 
-David Mascharka is a sophomore seeking a B.S.
+\noindent David Mascharka is a sophomore seeking a B.S.
 in Computer Science and Mathematics and B.A.
@@
 
-Paxten Johnson is on track to graduate in the Spring of 2016 with a B.S.
+\noindent Paxten Johnson is on track to graduate in the Spring of 2016 with a B.S.
 in Physics, Computer Science, and Mathematics.
@@
 
-Rachel Davis is currently on the path to obtaining a B.S.
+\noindent Rachel Davis is currently on the path to obtaining a B.S.
 in both Computer Science and Mathematics.
@@
 
-Katie Roth is pursuing a B.A.
+\noindent Katie Roth is pursuing a B.A.
 in Mathematics and Computer Science.
@@
 
-Leah Robison is on her way to graduate with a B.S.
+\noindent Leah Robison is on her way to graduate with a B.S.
 in Environment Science and a minor in Computer Science.

### 2015-04-04 Papers_and_Presentations/paper_spring_2015/paper.tex
Another update
Yet another paper update

@@
 \indent In step 5, the algorithm selects the assignment with the lowest cost to continue the search process.
-A solution is reached when all tiles have been placed in an assignment.
+The solution is reached when all tiles have been placed in an assignment and the solution has the lowest cost.
 If the assignment is not a solution, the amino acid type of the next residue in the protein sequence is retrieved.
@@
 \noindent Rachel Davis is currently on the path to obtaining a B.S.
-in both Computer Science and Mathematics.
+in both Computer Science and Mathematics, with a minor in Data Analytics.
 This is the second year conducting this sequencing research.
 Her research includes not only this primary structuring of proteins, but also a collaborative tertiary structuring algorithm.
-Currently she is applying to summer internships closely relating to both her interests and expertise.
+For this coming summer, she is researching at East Carolina University working on Software Testing.
 
@@
 Katie is the treasurer of the Women in Mathematics and Computer Science and an active member of Math Club.
-She is currently applying for summer research experiences, as well as internships.
+She will be gracing the University of Michigan with her researching talents working on a Big Data learning cooperative.
 

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step10.tex
Made the aStart code use a heap and push the rest of the presentation

--- 2015-02-08 Papers_and_Presentations/presentation/tilePlacement/step9.tex
@@
 
-		% Tile groups 
-		\draw [thick] (6,6) -- (10,6) -- (10,3.5) -- (6,3.5) -- (6,6);
-		\draw [thick] (14.5,6) -- (10.5,6) -- (10.5,3.5) -- (14.5,3.5) -- (14.5,6);
-		\node[align=center] at (0,4.75) {\textbf{Tiles to assign:}};
-		\node[align=center] at (4.25,4.75) {$i-1$\\$i$};
-		\draw [thick] (5.5,6) -- (3,6) -- (3,3.5) -- (5.5,3.5) -- (5.5,6);
-		\node[align=center, above] at (8,6) {Group 1};
-		\node[align=center, above] at (12.5,6) {Group 2};
+		% \draw [thick] (6,6) -- (10,6) -- (10,3.5) -- (6,3.5) -- (6,6);
+				% \draw [thick] (14.5,6) -- (10.5,6) -- (10.5,3.5) -- (14.5,3.5) -- (14.5,6);
+				\node[align=center] at (-1,6.25) {\textbf{Tiles to assign:}};
+				\node[align=center, rounded corners, draw] at (3.25,6.25) {$i-1$\\$i$\\$P_1$\\$P_2$\\Proline};
+				% \draw [thick] (5.5,6) -- (3,6) -- (3,3.5) -- (5.5,3.5) -- (5.5,6);
+				% \node[align=center, above] at (8,6) {Group 1};
+				% \node[align=center, above] at (12.5,6) {Group 2};
 
 				% tiles
-		\node[align=center, rounded corners, draw] at (7,4.75) {9\\12};
-		\node[align=center, rounded corners, draw] at (9,4.75) {11\\13};
-		\node[align=center, rounded corners, draw] at (11.5,4.75) {13\\9};
-		\node[align=center, rounded corners, draw] at (13.5,4.75) {12\\9.2};		
+				\node[align=center, rounded corners, draw] at (6.25,6.25) {9\\12\\0.935\\ 0.002\\No};
+				\node[align=center, rounded corners, draw] at (9,6.25) {11\\13\\0.013\\ 0.001\\No};
+				\node[align=center, rounded corners, draw] at (11.75,6.25) {13\\9\\0.003\\ 0.04\\No};
+				\node[align=center, rounded corners, draw] at (14.5,6.25) {12\\9.2\\0.000\\ 0.403\\No};	
+				\node[align=center, rounded corners, draw] at (17.25,6.25) {--\\--\\0.000\\ 0.000\\Yes};		
 				\draw [thick] (-4,2) -- (18,2);
@@
 		\draw (12.5,-5.5) -- (12.5,-6);
-		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {12\\9.2};
-		\node[align=center] at (14,-7) {2.0};
+		\node[align=center, rounded corners, draw] at (12.5,-7) {---\\---};
+		% \node[align=center] at (14,-7) {2.0};
+
+		% right side row 5
+		\draw (12.5,-8) -- (12.5,-8.5);
+		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
+		\node[align=center] at (14,-9.5) {2.0};
 
 		% grid
-		\draw [thick] (2,3.5) -- (2,-8);
-		\draw  (-.75,1.75) -- (-.75,-8);
-		\draw  (-4,1.125) -- (1.25,1.125);
+		\draw [thick] (2,3.5) -- (2,-10.5);
+		\draw  (-.75,1.75) -- (-.75,-10.5);
+		\draw  (-4,1.125) -- (1.5,1.125);
 
@@
 		\node[align=right] at (-2.5,1.5) {\tiny Chemical Shift};
-		\node[align=right] at (.25,1.5) {\tiny Group};
+		\node[align=right] at (.5,1.5) {\tiny $P_n$};
 		\node[align=right] at (-2.5,.5) {13.5};
@@
 		\node[align=right] at (-2.5,-4.5) {11.4};
-		\node[align=right] at (-2.5,-7) {8.8};
-		\node[align=right] at (.25,.5) {1};
-		\node[align=right] at (.25,-2) {2};
-		\node[align=right] at (.25,-4.5) {1};
-		\node[align=right] at (.25,-7) {2};
+		\node[align=right] at (-2.5,-7) {-};
+		\node[align=right] at (-2.5,-9.5) {8.8};
+		\node[align=right] at (.5,.5) {1};
+		\node[align=right] at (.5,-2) {2};
+		\node[align=right] at (.5,-4.5) {1};
+		\node[align=right] at (.5,-7) {Proline};
+		\node[align=right] at (.5,-9.5) {2};
 

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step11.tex
Made the aStart code use a heap and push the rest of the presentation

--- 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step10.tex
@@
 		% \node[align=center] at (8.5,.5) {1.5};
-		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
+		\node[align=center, rounded corners, draw, fill = green] at (14,.5) {11\\13};
 		% \node[align=center] at (15.5,.5) {0.5};
@@
 		%right side row 2
-		\node[align=center, rounded corners, draw] at (12.5,-2) {13\\9};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-2) {13\\9};
 		% \node[align=center] at (14,-2) {1.0};
 		\draw (14,-.5) -- (12.5,-1);
-		\node[align=center, rounded corners, draw, fill = green] at (15.5,-2) {12\\9.2};
-		\node[align=center] at (17,-2) {1.8};
+		\node[align=center, rounded corners, draw] at (15.5,-2) {12\\9.2};
+		% \node[align=center] at (17,-2) {1.8};
 		\draw (14,-.5) -- (15.5,-1);
@@
 		\draw (12.5,-3) -- (12.5,-3.5);
-		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-4.5) {9\\12};
 		% \node[align=center] at (14,-4.5) {1.6};
@@
 		\draw (12.5,-5.5) -- (12.5,-6);
-		\node[align=center, rounded corners, draw] at (12.5,-7) {---\\---};
-		% \node[align=center] at (14,-7) {2.0};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-7) {---\\---};
 
@@
 		\draw (12.5,-8) -- (12.5,-8.5);
-		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-9.5) {12\\9.2};
 		\node[align=center] at (14,-9.5) {2.0};

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step6.tex
Made the aStart code use a heap and push the rest of the presentation

--- 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step10.tex
@@
 		%first 
-		\node[align=center, rounded corners, draw] at (7,.5) {9\\12};
-		% \node[align=center] at (8.5,.5) {1.5};
+		\node[align=center, rounded corners, draw, fill = green] at (7,.5) {9\\12};
+		\node[align=center] at (8.5,.5) {1.5};
 		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
@@
 		\draw (14,-.5) -- (12.5,-1);
-		\node[align=center, rounded corners, draw, fill = green] at (15.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-2) {12\\9.2};
 		\node[align=center] at (17,-2) {1.8};
@@
 		\node[align=center] at (7,-2) {3.0};
-		\node[align=center, rounded corners, draw] at (8.5,-2) {12\\9.2};
-		% \node[align=center] at (10,-2) {1.8};
+		\node[align=center, rounded corners, draw, fill=orange] at (8.5,-2) {12\\9.2};
+		\node[align=center] at (10,-2) {1.8};
 
 		% left side row 3
-		\node[align=center, rounded corners, draw, fill = orange] at (8.5,-4.5) {11\\13};
-		\node[align=center] at (10,-4.5) {5.2};
-		\draw (8.5,-3) -- (8.5,-3.5);
+		% \node[align=center, rounded corners, draw, fill = orange] at (8.5,-4.5) {11\\13};
+		% \node[align=center] at (10,-4.5) {5.2};
+		% \draw (8.5,-3) -- (8.5,-3.5);
 
@@
 		\draw (12.5,-3) -- (12.5,-3.5);
-		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
-		% \node[align=center] at (14,-4.5) {1.6};
-		\draw (15.5,-3) -- (15.5,-3.5);
-		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
-		\node[align=center] at (17,-4.5) {2.6};
+		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-4.5) {9\\12};
+		\node[align=center] at (14,-4.5) {1.6};
+		% \draw (15.5,-3) -- (15.5,-3.5);
+		% \node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
+		% \node[align=center] at (17,-4.5) {2.6};
 
 		% right side row 4
-		\draw (12.5,-5.5) -- (12.5,-6);
-		\node[align=center, rounded corners, draw] at (12.5,-7) {---\\---};
+		% \draw (12.5,-5.5) -- (12.5,-6);
+		% \node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {---\\---};
 		% \node[align=center] at (14,-7) {2.0};
 
-		% right side row 5
-		\draw (12.5,-8) -- (12.5,-8.5);
-		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
-		\node[align=center] at (14,-9.5) {2.0};
+		% % right side row 5
+		% \draw (12.5,-8) -- (12.5,-8.5);
+		% \node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
+		% \node[align=center] at (14,-9.5) {2.0};
 

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step7.tex
Made the aStart code use a heap and push the rest of the presentation

--- 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step6.tex
@@
 		%first 
-		\node[align=center, rounded corners, draw, fill = green] at (7,.5) {9\\12};
-		\node[align=center] at (8.5,.5) {1.5};
+		\node[align=center, rounded corners, draw] at (7,.5) {9\\12};
+		% \node[align=center] at (8.5,.5) {1.5};
 		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
@@
 		\draw (12.5,-3) -- (12.5,-3.5);
-		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-4.5) {9\\12};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-4.5) {9\\12};
 		\node[align=center] at (14,-4.5) {1.6};
@@
 		% right side row 4
-		% \draw (12.5,-5.5) -- (12.5,-6);
-		% \node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {---\\---};
-		% \node[align=center] at (14,-7) {2.0};
+		\draw (12.5,-5.5) -- (12.5,-6);
+		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {---\\---};
+		\node[align=center] at (14,-7) {1.6};
 

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step8.tex
Made the aStart code use a heap and push the rest of the presentation

--- 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step7.tex
@@
 		\draw (12.5,-3) -- (12.5,-3.5);
-		\node[align=center, rounded corners, draw, fill = green] at (12.5,-4.5) {9\\12};
-		\node[align=center] at (14,-4.5) {1.6};
+		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
+		% \node[align=center] at (14,-4.5) {1.6};
 		% \draw (15.5,-3) -- (15.5,-3.5);
@@
 		\draw (12.5,-5.5) -- (12.5,-6);
-		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {---\\---};
+		\node[align=center, rounded corners, draw, fill = green] at (12.5,-7) {---\\---};
 		\node[align=center] at (14,-7) {1.6};
 
-		% % right side row 5
-		% \draw (12.5,-8) -- (12.5,-8.5);
-		% \node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
-		% \node[align=center] at (14,-9.5) {2.0};
+		% right side row 5
+		\draw (12.5,-8) -- (12.5,-8.5);
+		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
+		\node[align=center] at (14,-9.5) {2.0};
 

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step9.tex
Made the aStart code use a heap and push the rest of the presentation

--- 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step8.tex
@@
 		\node[align=center] at (7,-2) {3.0};
-		\node[align=center, rounded corners, draw, fill=orange] at (8.5,-2) {12\\9.2};
+		\node[align=center, rounded corners, draw, fill = green] at (8.5,-2) {12\\9.2};
 		\node[align=center] at (10,-2) {1.8};
@@
 		% left side row 3
-		% \node[align=center, rounded corners, draw, fill = orange] at (8.5,-4.5) {11\\13};
-		% \node[align=center] at (10,-4.5) {5.2};
-		% \draw (8.5,-3) -- (8.5,-3.5);
+		\node[align=center, rounded corners, draw, fill = orange] at (8.5,-4.5) {11\\13};
+		\node[align=center] at (10,-4.5) {5.2};
+		\draw (8.5,-3) -- (8.5,-3.5);
 
@@
 		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
+		% \node[align=center] at (14,-4.5) {2.0};
+
 		% \node[align=center] at (14,-4.5) {1.6};
@@
 		\draw (12.5,-5.5) -- (12.5,-6);
-		\node[align=center, rounded corners, draw, fill = green] at (12.5,-7) {---\\---};
-		\node[align=center] at (14,-7) {1.6};
+		\node[align=center, rounded corners, draw] at (12.5,-7) {---\\---};
+		% \node[align=center] at (14,-7) {2.0};
 

### 2015-04-30 search_project/Node_aStar.py

@@ -71,7 +71,10 @@ class Node(object):
 					temp_order_cost = self.placed_tiles[-1].compare_below(placed_tile)
 				else: # first tile being placed 
 					temp_char_cost = placed_tile.get_error(self.characteristic[char_num])
-					temp_order_cost = 0 # no before it to compare to
+
+					# makes sure the heuristic cost for placing a tile in front of the first tile is not considered 
+					temp_order_cost = -1*placed_tile.heuristic_order_cost 
+					
 				c = temp_order_cost + temp_char_cost - placed_tile.heuristic_cost
 
 				# add child node to list of new_nodes

### 2015-04-30 search_project/Scripts/get_data.sh

@@ -2,12 +2,12 @@
 
 cd ..
 
-for i  in $(seq 44 70); 
+for i  in $(seq 36 70); 
 do 
 	echo Data/Spring_2015_$i.txt
-	echo >> Scripts/aStar_spring2015_data.log
-	echo ================================== >> Scripts/aStar_spring2015_data.log
-	echo Data/Spring_2015_$i.txt >> Scripts/aStar_spring2015_data.log
-	echo ================================== >> Scripts/aStar_spring2015_data.log
-	python search_project_aStar.py Data/Spring_2015_$i.txt >> Scripts/aStar_spring2015_data.log
+	echo >> Scripts/spring2015_data_missing.log
+	echo ================================== >> Scripts/spring2015_data_missing.log
+	echo Data/Spring_2015_$i.txt >> Scripts/spring2015_data_missing.log
+	echo ================================== >> Scripts/spring2015_data_missing.log
+	python search_project_aStar.py Data/Spring_2015_$i.txt >> Scripts/spring2015_data_missing.log
 done

### 2015-04-30 search_project/Scripts/get_data1.sh

@@ -2,11 +2,11 @@
 
 cd ..
 
-for i  in $(seq 50 62); 
+for i  in $(seq 1 62); 
 do 
-	echo | tee -a Scripts/profix_j48_3sd.log
-	echo ================================== | tee -a Scripts/profix_j48_3sd.log
-	echo Data/Data_Fall_2014_$i.txt | tee -a Scripts/profix_j48_3sd.log
-	echo ================================== | tee -a Scripts/profix_j48_3sd.log
-	python search_project1.py Data/Data_Fall_2014_$i.txt | tee -a Scripts/profix_j48_3sd.log
+	echo | tee -a Scripts/test2.log
+	echo ================================== | tee -a Scripts/test2.log
+	echo Data/Data_Fall_2014_$i.txt | tee -a Scripts/test2.log
+	echo ================================== | tee -a Scripts/test2.log
+	python search_project_aStar.py Data/Data_Fall_2014_$i.txt | tee -a Scripts/test2.log
 done

### 2015-04-30 search_project/Scripts/get_data2.sh

@@ -5,9 +5,9 @@ cd ..
 for i  in $(seq 1 50); 
 do 
 	echo Data/Spring_2015_$i.txt
-	echo | tee -a Scripts/lmt_spring2015_data.log
-	echo ================================== | tee -a Scripts/lmt_spring2015_data.log
-	echo Data/Spring_2015_$i.txt | tee -a Scripts/lmt_spring2015_data.log
-	echo ================================== | tee -a Scripts/lmt_spring2015_data.log
-	python search_project1.py Data/Spring_2015_$i.txt | tee -a Scripts/lmt_spring2015_data.log
+	echo | tee -a Scripts/spring_2k15_no_aStar.log
+	echo ================================== | tee -a Scripts/spring_2k15_no_aStar.log
+	echo Data/Spring_2015_$i.txt | tee -a Scripts/spring_2k15_no_aStar.log
+	echo ================================== | tee -a Scripts/spring_2k15_no_aStar.log
+	python search_project.py Data/Spring_2015_$i.txt | tee -a Scripts/spring_2k15_no_aStar.log
 done

### 2015-04-30 search_project/Tile_aStar.py

@@ -28,6 +28,7 @@ class Tile(object):
         self.char_weight = .1
         self.order_weight = 1
         self.heuristic_cost = heuristic
+        self.heuristic_order_cost = 0
         self.amino_type = self.calculate_amino_type(model,pro)
 
 

### 2015-04-30 search_project/search_strategies.py

@@ -104,8 +104,8 @@ take in a solution node and the number of nodes generated
 def output_soultion(finalNode, nodeCount):
 	# Uncomment to record results to data file for scripted runs
 	
-	# with open("../Results_Winter_2014-15/lmt_spring2015_data.dat", "a") as dataFile:
-	# 	dataFile.write(str(len(finalNode.characteristic)) + "\t" + str(nodeCount) + "\n")
+	with open("../Results_Winter_2014-15/spring_2k15_no_aStar.dat", "a") as dataFile:
+		dataFile.write(str(len(finalNode.characteristic)) + "\t" + str(nodeCount) + "\n")
 
 	#prints best solution to console
 	print "HERE IS THE BEST"
@@ -116,7 +116,7 @@ def output_soultion(finalNode, nodeCount):
 	print "Order Cost:  " + str(finalNode.get_order_cost())
 	print "Nodes: " + str(nodeCount)
 
-def puzzle_building_search(root):
+def puzzle_building_search(frontier, numSolutions, depthVal):
 	#make this maintain the list of nodes being used to start and end the uniform cost search
 	# uniform cost search may want to have 3 variables: 
 	# one for the frontier (some changes will need to make this happen)
@@ -184,10 +184,10 @@ def start_search(file_name, type):
 
 	# picks algorithm
 	if (int(type) == 0): # uniform cost search
-		best_solution, node_count = uniform_cost(root)
+		best_solution, node_count = uniform_cost([root])
 		output_soultion(best_solution, node_count)
 	elif (int(type) == 1): # puzzle building
-		best_solution = puzzle_building_search(root)
+		best_solution = puzzle_building_search([root])
 
 
 """
@@ -195,13 +195,13 @@ preforms a uniform cost search on a node
 takes in a starting node for the search 
 returns the best solution
 """
-def uniform_cost(root):
-	frontier = [root] # holds list of node that need exploring
-	lowest = 1.0
-	for i in range(len(root.unplaced_tiles)):
-		if (root.unplaced_tiles[i].amino_type[root.characteristic[i][2]] < lowest):
-			lowest = root.unplaced_tiles[i].amino_type[root.characteristic[i][2]]
-	print lowest
+def uniform_cost(frontier):
+	# frontier = [root] # holds list of node that need exploring
+	# lowest = 1.0
+	# for i in range(len(root.unplaced_tiles)):
[…]

### 2015-04-30 search_project/search_strategies_aStar.py

@@ -8,21 +8,39 @@ from weka.classifiers import Classifier
 import weka.core.jvm as jvm
 import weka.core.serialization as serialization
 import time
+from heapq import *
 
 """
 calculates and stores heuristic values for 
-all tiles with data
+all tiles with data compared with the characteristic 
+protein sequence
 """
-def calculate_heuristic(tile_set, characteristic):
+def calculate_char_heuristic(tile_set, characteristic):
 	temp = 0
-	greatest = 0
+	lowest = float("inf")
 	for tile in tile_set:
 		for char in characteristic:
 			temp = tile.get_error(char)
-			if (temp>greatest):
-				greatest = temp
-		tile.heuristic_cost = temp
+			if (temp<lowest):
+				lowest = temp
+		tile.heuristic_cost = lowest
 
+"""
+calculates and stores heuristic values for 
+all tiles with data compared with all other 
+tiles
+"""
+def calculate_order_heuristic(tile_set):
+	temp = 0
+	for tile in tile_set:
+		lowest = float("inf")
+		for tile_comp in tile_set:
+			temp = tile_comp.compare_below(tile)
+			if (temp<lowest):
+				lowest = temp
+		tile.heuristic_cost = lowest
+		# print lowest
+		tile.heuristic_order_cost = lowest #save to remove when the first tile is placed
 
 """
 Creates enough place holder tiles to do a full search
@@ -41,7 +59,7 @@ def generate_placeholders(tile_set, characteristic, nmrClass):
 	if gap > 0:
 		for n in range(gap):
 			# print "making"
-			tile_set.append(Tile(-1, -1, -1, -1, nmrClass, heuristic=0)) # add place holder tiles to tile set
+			tile_set.append(Tile(-1, -1, -1, -1, nmrClass, heuristic=1.9)) # add place holder tiles to tile set
 	return tile_set
 
 
@@ -113,6 +131,10 @@ def letters_to_numbers(characteristic):
 	return new_characteristic
 
 
+def listToHeap(data):
+	for i in xrange(len(data)):
+		data[i] = (data[i].get_cost(), data[i])
+	heapify(data)
 """
 prints results to console
 take in a solution node and the number of nodes generated
@@ -120,8 +142,8 @@ take in a solution node and the number of nodes generated
 def output_soultion(finalNode, nodeCount):
 	# Uncomment to record results to data file for scripted runs
 	
[…]

### 2015-04-30 search_project/test_code.py

@@ -9,10 +9,10 @@ def getExpectedOutput(filename):
     return expected_output
 
 def getOutput(filename):
-    p = subprocess.Popen(["python", "search_project.py", "./Data/"+filename, "0"], stdout=subprocess.PIPE)
+    p = subprocess.Popen(["python", "search_project_aStar.py", "./Data/"+filename, "0"], stdout=subprocess.PIPE)
     out = p.communicate()
     outputList = out[0].split("\n")
-    output = "\n".join(outputList[4 : len(outputList) - 5])
+    output = "\n".join(outputList[6 : len(outputList) - 5])
     return output
 
 class TestSequenceFunctions(unittest.TestCase):
